### 2024-04-05 paper/paper.qmd
Add files via upload

---
title: "Predicting the Outcome of the 2025 Election in Canada by a Regression Analysis"
title-block-banner: true
abstract: "ojjojojojljk,mkmk."
thanks: "Code and data supporting this analysis are available at: https://github.com/CSCmaster/Final-Project"
author: "Jingyi Shen"
date: today
date-format: long
format: pdf
toc: true
toc-depth: 2
number-sections: true
bibliography: references.bib
link-citations: true
---

```{r setup, include=FALSE, message=FALSE}
## Import necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(here)
library(readr)
library(knitr)
library(kableExtra)
library(rstanarm)
library(arrow)
```

# Introduction

## Background

The Canadian electoral process, epitomizing democratic principles, empowers citizens to elect parliamentarians who shape Parliament's composition and, consequently, the government formation. In the recent 2021 federal election, Justin Trudeau's Liberal Party secured a majority in the 44th Parliament. Voters' primary concerns include the cost of living, healthcare, climate change, post-pandemic recovery, and immigration, with dissatisfaction towards Trudeau's government prevalent. Trudeau's popularity lags behind UK's Poilievre. The government's ambitious immigration plan aims to admit 500,000 migrants annually by 2025, albeit facing a backlog. The Conservative Party, with a focus on economic prosperity, emphasizes attracting highly skilled immigrants while addressing concerns like living costs and housing issues[@Canada].

## Hypothesis

Based on our analysis of historical trends, governmental policies, and electoral procedures, our hypothesis aligns with the prevailing expectation that the Conservatives will emerge as the likely winners in the 2025 election. **We anticipate that the Conservatives will likely secure the highest number of votes, with the Liberals expected to closely follow in second place.** Our research indicates that the vote-counting process in Canada significantly influences the outcome, as voters do not directly elect a specific prime minister candidate. Initially, all votes are tallied based on first preferences. If a candidate obtains 50% of the vote, they win. If not, the candidate with the fewest votes is eliminated[@Canada]. Then, votes from supporters of the eliminated candidate are redistributed to their second-choice candidate. This iterative redistribution continues until one candidate achieves 50% of the vote. Hence, our objective is to forecast the election probabilities for the Conservative and Liberal parties and compare which is higher[@Elections].

## Terminology

In this paper, I used binary logistic regression models to forecast the likelihood of individuals affiliating with the Conservative or Liberal parties. Binary logistic regression is a statistical technique tailored for predicting binary outcomes, where the variable under consideration has two possible results. In our study, these outcomes represent the probability of individuals aligning with each of the two parties. Each party's likelihood will be predicted through separate logistic regression models, with the response variables indicating whether individuals vote for the corresponding party or not. The predictors used in these models include age, province, education, religion, and income before tax. The variable "sex" will be initially included but later removed after AIC model testing, as further elaborated in the model selection section. This regression approach is particularly advantageous when there's a nonlinear relationship between independent and dependent variables, especially in scenarios with categorical dependent variables like ours. Additionally, we will incorporate post-stratification in our analysis to enhance accuracy. Post-stratification helps refine precision estimates by ensuring that the sample is more representative of the entire population.

# Data

## Raw Data

In both datasets, we've focused on standardizing variables such as age, sex, province, education, religion, and pre-tax income. Conducting a census typically involves higher expenses and more time since it requires reaching out to every individual in the population. Surveys, however, offer a more cost-effective and quicker alternative, especially for large populations, by collecting data from a select group that represents the larger whole.

**Census Data**: Census data refer to information systematically gathered from the entire population of a defined area at a specific point in time. The census data we have comes from the General Social Survey (GSS), conducted on August 12, 2022. We've made necessary adjustments to ensure it matches our survey data. Data collection aims to provide a detailed snapshot of demographic, economic, and social characteristics.The GSS is a nationwide survey program designed to collect data on societal trends, behaviors, and attributes across the entire population, offering insights into the changing dynamics of communities.

**Survey Data**: Survey data, are collected from a sample of the population rather than every individual. This method is often used when it's impractical or unnecessary to include everyone. Survey data aim to infer the characteristics of the larger population based on the responses of the sample. The survey data, obtained from the Canada Election Study (CES) in 2023, includes responses from over 37,000 participants. The CES focuses specifically on voter behavior, attitudes, and the electoral process within the Canadian context. Unlike the GSS, which aims for a comprehensive overview, the CES targets specific topics of interest to derive insights from a segment of the population.

## Data analysis Tools

In this research,the arrow[@arrow]package significantly impacts the way large datasets are handled and processed. It provides high-performance reading and writing of data in the Arrow file format, including support for Parquet files, which are highly efficient for storing and querying large datasets. Tidyr[@tidyr] helps in tidying data, meaning it makes it easier to structure datasets so that they are straightforward to work with. It provides functions to transform data into a tidy format, where each variable forms a column, each observation forms a row, and each type of observational unit forms a table. The mass package[@MASS], It provides a wide range of statistical techniques including linear and nonlinear modeling, statistical tests, time series analysis, classification, and clustering. The package is known for its functions to fit generalized linear models, among many other tools. With summarytools[@summarytools], users can easily generate frequency tables, descriptive statistics summaries, cross-tabulations, and more. It makes exploratory data analysis more efficient and is particularly useful for preliminary data analysis, ensuring that researchers and analysts can understand their data before moving on to more complex analyses. Data analysis was conducted using the R programming language [@r], renowned for its open-source nature and robust statistical analysis capabilities. Visualization complexities were addressed with the ggplot2 package [@rGgplot2], which supports the creation of intricate graphics. For data manipulation, dplyr[@rDplyr] was employed, providing a streamlined grammar that simplifies dataset filtering, summarization, and reorganization. Fast and efficient data importing was achieved through the use of the readr package[@rReadr]. The process of generating this report was seamlessly managed by knitr[@rKnitr], facilitating the embedding of R code directly within the text.

## Variable Description

### Survey Data Variable

**Age**: The cps21_age field from the survey data denotes participants' ages at the time they completed the General Social Survey. This variable requires no alterations but should be renamed to "age" to ensure consistency with the census data's corresponding variable.

**sex**: In the survey dataset, cps21_genderid identifies 9474 respondents as male, 11370 as female, 90 as non-binary, and 34 as other. Given the relatively small number of non-binary and other responses, distribute these respondents between male and female categories based on existing proportions, with females at 54.22% and males at 45.18%.

**province**: The survey data's cps21_province includes three additional provinces not present in the census data, creating discrepancies. To align the datasets, remove Northwest Territories, Nunavut, and Yukon from the survey data. Moreover, convert the numeric province labels in the survey data into their corresponding categorical names for analytical compatibility.

**Education:** The survey data's cps21_education, featuring twelve education levels, should be consolidated into three categories for analysis. Group No schooling through "Don't know/ Prefer not to answer" as "Limited Education"; "Some secondary/ high school" through "Some university as Some Education"; and degrees from "Bachelor's degree" onwards as "Highly Educated".

**Religion**: The cps21_religion variable indicates a respondent's religious affiliation. A response of '1' denotes atheism (categorized as 'NO'), whereas any other response signifies a religious affiliation (categorized as 'YES').

**Income_before_tax**: Convert the numerical cps21_income_numbe, indicating total household income before taxes, into categories for logistic regression analysis. Define "Lower Middle Class to Poor" as incomes \< \$50,000, "Middle Class" as incomes between \$50,000 and \$124,999 and "Upper Middle Class to Wealthy" as incomes ≥ \$125,000.

**vote_liberal**: The cps21_votechoice variable records intended voting behavior. For logistic regression, recode responses to a binary format, where selecting '1' indicates an intention to vote for the Liberal Party ('1'), and any other selection is recoded as '0'.

**vote_conservative**: for the Conservative Party, recode cps21_votechoice to '1' for respondents who choose '2', indicating a preference for this party, and '0' for all other selections.

### Census Data Variable

**Age Adjustment**: In the census data, age is presented as a decimal number. For consistency with the survey data, round this value to the nearest whole number.

**Gender Representation**: The gender classification in the census data, listed as either 'Male' or 'Female', aligns perfectly with the survey data, requiring no modifications.

**Provincial Data**: The listing of provinces in the census data, including "Newfoundland" and "Labrador", "Nova Scotia", "Quebec", "Saskatchewan", "Ontario", "Alberta", "British Columbia", "Prince Edward Island", "New Brunswick", and "Manitoba", matches that of the survey data, making no further adjustments necessary.

**Educational Levels**: The census data sorts educational attainment into eight categories, with one category for missing information. Align these with the survey data's education classifications by grouping "Less than high school diploma or its equivalent" and missing data as "Limited Education"; "High school diploma or a high school equivalency certificate", "Trade certificate or diploma", "College, CEGEP, or other non-university certificate or diploma", "University certificate or diploma below the bachelor's level" as "Some Education"; and both "Bachelor's degree", and any university certification above a bachelor's degree as "Highly Educated".

**Religious Affiliation**: The "religion_has_affiliation" variable in the census data identifies if an individual has a religious affiliation, is uncertain, claims no religious affiliation, or if the response is missing. For alignment with the survey data, consolidate into two groups: categorize as `YES` for those with a religious affiliation, uncertain, or missing responses (assuming missing responses indicate reluctance to disclose religious affiliation), and `NO` for those without any religious affiliation.

**Income Categories**: The Income_respondent field in the census dataset uses 7 income brackets to classify respondents' earnings. To harmonize with the survey data's "income_before_tax" categories, reclassify these into three broader groups. Designate incomes of "\$125,000 and more" to the "Upper Middle Class to Wealthy" group. Categorize incomes of "\$50,000 to \$74,999", "\$75,000 to \$99,999", and "\$100,000 to \$124,999" as "Middle Class". Assign "Less than \$25,000" and "\$25,000 to \$49,999" incomes to the "Lower Middle Class to Poor" group.

## Sample of cleaned Data

### Data Summary Measures 
Table 1: Summary varibales in Census and Survey Data
```{r echo=FALSE}
numeric_summary_df <- data.frame(
  Variable = c("Age in Census Data", "Age in Survey Data", 
               "Liberal Votes in Survey", "Conservative Votes in Survey"),
  Minimum = c(15.0, 18.0, 0.000, 0.000),
  Q1 = c(37.0, 36.0, 0.000, 0.000),
  Median = c(54.0, 53.0, 0.000, 0.000),
  Average = c(52.18, 51.3, 0.267, 0.249),
  Q3 = c(67.0, 66.0, 1.000, 0.000),
  Maximum = c(80.0, 97.0, 1.000, 1.000)
)

knitr::kable(numeric_summary_df, caption = "Summary of Numerical Variables Across Census and Survey Data")

```

The statistical summary of the census and survey data reveals age distributions with the census data capturing a narrower age range (15 to 80 years, with a median of 54) compared to the broader age span in the survey data (18 to 97 years, with a median of 53). The average ages for the census and survey populations are 52.18 and 51.3 years, respectively. Voting data from the survey indicate that a quarter of the respondents are inclined towards the Liberal Party, as shown by an average of 0.267, while a slightly lower average of 0.249 suggests Conservative support; both parties have 50% of the population not voting for them, with a median of 0. The upper bounds for Liberal and Conservative votes are 1, meaning some respondents indicated a vote for these parties, while the third quartile for Conservative votes indicates less overall support compared to the Liberal Party.

### Data Visualization

```{r, echo=FALSE, message=FALSE, warning=FALSE}
cleaned_survey_data <- read_parquet(here("data", "analysis_data","cleaned_survey_data.parquet"))
cleaned_census_data <- read_parquet(here("data", "analysis_data","cleaned_census_data.parquet"))
combined_data <- rbind(
  data.frame(Age = cleaned_survey_data$age, Dataset = "Survey"),
  data.frame(Age = cleaned_census_data$age, Dataset = "Census")
)
ggplot(combined_data, aes(x = Age, fill = Dataset)) +
  geom_histogram(position = "identity", alpha = 0.5, binwidth = 4) +
  scale_fill_manual(values = c("Survey" = "blue", "Census" = "red")) +
  labs(
    title = "Plot.1 Age Distribution Comparison",
    x = "Age",
    y = "Frequency"
  ) +
  xlim(min(combined_data$Age, na.rm = TRUE), max(combined_data$Age, na.rm = TRUE)) +
  theme_minimal()

```

The overlapping histogram illustrates the age distributions from census and survey datasets, with the census data in red displaying a more concentrated and unimodal age distribution peaking between 50 and 60 years and tapering off sharply at 80. In contrast, the survey data, shown in blue, reveals a broader spread of ages with a right-skewed tail extending to 97 years, indicating the inclusion of older respondents. Both distributions share a common median age range, highlighted by the combined purple hue in the overlap, but the census data consistently show higher frequencies across most age bins. This visual comparison underscores the differing age profiles captured by the two datasets and a significant density of middle-aged respondents in both populations.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
combined_provinces <- rbind(
  data.frame(province = cleaned_survey_data$province, dataset = "Survey Dataset"),
  data.frame(province = cleaned_census_data$province, dataset = "Census Dataset")
)
ggplot(combined_provinces, aes(x = province, fill = dataset)) +
  geom_bar(position = "dodge") +
  labs(title = "Plot.2 Comparison of Province Variable", x = "Province", y = "Count") +  
  scale_fill_manual(values = c("Survey Dataset" = "red", "Census Dataset" = "blue")) +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

The bar chart depicts the frequency distribution of respondents across different provinces as collected in two datasets: the census and survey data. Each province is represented on the x-axis, and the corresponding count of respondents is displayed on the y-axis. The bars are color-coded, with blue indicating the survey dataset and red representing the census dataset. The bars are placed side by side, or 'dodged', allowing for a direct visual comparison between the two datasets within each provincial category.

From a statistical perspective, Ontario has the highest frequency in the survey dataset, which substantially exceeds the count in the census dataset, indicating a larger sample or population size recorded in the survey for this province. Conversely, the counts for British Columbia and Alberta show a relatively balanced representation between the two datasets. The chart facilitates a comparative analysis of the datasets, revealing disparities and similarities in the population coverage across provinces, which could be indicative of sampling strategies or the demographic spread within the datasets.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
combined_data_education <- na.omit(rbind(
  data.frame(Education = cleaned_survey_data$education, Dataset = "Survey Dataset"),
  data.frame(Education = cleaned_census_data$education, Dataset = "Census Dataset")
))
education_summary <- combined_data_education %>%
  group_by(Education, Dataset) %>%
  summarise(Count = n(), .groups = 'drop')

education_summary$Education <- factor(education_summary$Education, levels = unique(education_summary$Education))

ggplot(education_summary, aes(x = Education, y = Count, group = Dataset, color = Dataset)) +
  geom_line() + 
  geom_point() + 
  scale_color_manual(values = c("Survey Dataset" = "red", "Census Dataset" = "blue")) +
  labs(title = "Line Chart Comparison of Education Levels",
       x = "Education Level",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

The line chart presented compares the distribution of education levels across two different datasets, one from a survey and another from a census, differentiated by colors—red for the survey and blue for the census. Education levels are divided into three categories along the x-axis: "Highly Educated", "Limited Education", and "Some Education", with the y-axis displaying the count of individuals within each category. A noticeable trend is the inverse relationship between the two datasets from "Highly Educated" to "Limited Education": the count for the Census dataset declines while that for the Survey dataset rises, suggesting a disparity in the representation of education levels between the two data sources.

This discrepancy highlights potential differences in sampling methods, response rates, or the representativeness of each dataset relative to the underlying population. The most pronounced difference is at the "Limited Education" level, where the Survey dataset shows significantly lower counts compared to the Census dataset, indicating a possible overrepresentation of individuals with limited education in the censaus or an underrepresentation in the survey. The data suggest that demographic, socioeconomic, or regional factors may influence the education level distribution in each dataset, and further statistical analysis could be warranted to determine the significance and cause of these differences. The differences observed in the chart might also reflect methodological variations in data collection or inherent biases within the sampling frames used.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

combined_data_religion <- rbind(
  data.frame(Religion = cleaned_survey_data$religion, Dataset = "Survey Dataset"),
  data.frame(Religion = cleaned_census_data$religion, Dataset = "Census Dataset")
)

combined_data_religion$Religion <- factor(combined_data_religion$Religion)

ggplot(combined_data_religion, aes(x = Religion, fill = Dataset)) +
  geom_bar(position = "dodge") +  # Position bars side by side
  labs(title = "Plot.4 Comparison of Religion", x = "Religion", y = "Count") +  
  scale_fill_manual(values = c("Survey Dataset" = "pink", "Census Dataset" = "red")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Optional: to improve readability of x-axis labels

```

The bar graph depicts the frequency of individuals categorized by religious affiliation within two datasets: census and survey. Each dataset's frequency is represented by a bar in distinct shades, with a darker red indicating the census dataset and a lighter pink representing the survey dataset. The x-axis bifurcates the data into two groups: those without religious affiliation ('NO') and those with religious affiliation ('YES').

The y-axis provides a count of individuals in each category. Notably, the census dataset shows a substantially higher count of individuals with a religious affiliation compared to those without. This pattern is less pronounced in the survey dataset, where the frequencies of individuals with and without religious affiliation are more comparable. The visual disparity in bar heights, especially within the 'YES' category, suggests a higher prevalence of religious affiliation reported in the census dataset than in the survey dataset.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
combined_data_income <- na.omit(rbind(
  data.frame(IncomeBeforeTax = cleaned_survey_data$income_before_tax, Dataset = "Survey Dataset"),
  data.frame(IncomeBeforeTax = cleaned_census_data$income_before_tax, Dataset = "Census Dataset")
))
ggplot(combined_data_income, aes(x = IncomeBeforeTax, fill = Dataset)) +
  geom_bar(position = "dodge") +
  labs(title = "Plot.5 Comparison of Income Before Tax", x = "Income Before Tax", y = "Count") +
  scale_fill_manual(values = c("Survey Dataset" = "orange", "Census Dataset" = "brown")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```

The bar chart displays the distribution of income categories before tax across two datasets: census and survey. The income categories are defined as 'Lower Middle Class to Poor', 'Middle Class', and 'Upper Middle Class to Wealthy', and are represented on the x-axis. The y-axis measures the count of individuals within each income bracket.

In the 'Lower Middle Class to Poor' category, there is a significant count of individuals in the census dataset, shown by a tall bar, which vastly exceeds the count from the survey dataset. For the 'Middle Class' bracket, the census dataset again shows a higher frequency, but with a smaller margin compared to the survey dataset. Lastly, in the 'Upper Middle Class to Wealthy' category, both datasets depict a lower frequency of individuals than in the other categories, but the survey dataset shows a slightly higher count than the census dataset in this high-income bracket.

The bars for the census dataset are colored in a deep red, while the bars for the survey dataset are in orange, with each pair of bars positioned next to one another for a clear visual comparison. This color differentiation, along with the bar placement, facilitates an immediate comparative analysis of the socioeconomic composition of the populations captured in the two datasets, indicating a notably higher representation of lower income levels within the census data.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
df_long <- pivot_longer(na.omit(survey_data_new), cols = starts_with("vote_"), names_to = "Party", values_to = "Vote")

# Plot a grouped bar plot
ggplot(df_long, aes(x = Party, fill = as.factor(Vote))) +
  geom_bar(position = "dodge", stat = "count") +
  labs(title = "Plot.6 Comparison of Voting Preferences", x = "Party", y = "Count") +
  scale_fill_manual(values = c("red", "blue"), name = "Party Choice", labels = c("Did Not Vote", "Voted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Measurement

In this paper, there are two data set, the survey dataset and census dataset. The survey dataset is utilized from Canadian Election Study(CES) while the census dataset is utilized from General Social Survey(GSS).

Canadian Election Study gathered a sample of 20,968 individuals from across Canada using the Leger Opinion panel, ensuring representation from various regions while maintaining a balance in gender and age demographics within each area. The sample aimed for an equal distribution of 50% males and 50% females, with age groups targeted as follows: 28% between 18-34 years, 33% between 35-54 years, and 39% 55 years and older. The geographical regions included Atlantic Canada, Quebec, Ontario, Western Canada, and the Territories, with quotas set to reflect their population proportions (7% for Atlantic, 23% for Quebec, 38% for Ontario, and 32% for the West) and an open acceptance for any participants from the Territories. In Quebec, the language preference aimed for 80% French-speaking and 20% English-speaking participants, with a goal of 10% French-speaking participants in both the Atlantic region and across Canada. Eligibility for participation required being at least 18 years old and a Canadian citizen or permanent resident[@CES].

The General Social Survey focuses on non-institutionalized individuals aged 15 and above residing in Canada's ten provinces. Within each selected household, a random individual is chosen by an application to answer the survey following the initial household roster completion. General Social Survey's questionnaire was developed through rigorous research and broad consultations with data users. The Statistics Canada Questionnaire Design Resource Center (QDRC) conducted qualitative testing in four cities to identify effective questions and those requiring adjustments. Based on the testing, QDRC prepared a comprehensive report with suggestions, which were integrated into the final survey design to enhance clarity and effectiveness.The survey employs a cross-sectional sample survey methodology, utilizing a combined frame of landline and cellular phone numbers from Census data, administrative records, and Statistics Canada's dwelling database. This approach improves coverage of households linked to phone numbers. The sampling strategy is stratified, with stratification occurring at the level of provinces and census metropolitan areas (CMA), and it relies on probability sampling techniques. Information is collected from a single individual aged 15 or older per household, without the use of proxy responses.[@GSS]

I made several adjustment to the raw dataset to parepare for the analyzed dataset. In the process of cleaning the survey data, several transformative steps were taken to ensure its suitability for analysis. Initially, the age variable was directly adopted as is from `cps21_age`. Gender distribution was then randomized based on predefined proportions for male and female respondents, aiming for a balanced representation. Province information, originally in code form, was converted to textual names for clarity, with any undefined codes being assigned as `NA` to exclude incomplete records. Educational background was categorized into three broad levels: "Limited Education", "Some Education", and "Highly Educated", based on specific ranges of `cps21_education` codes. Religious affiliation was simplified to a binary "YES"/"NO" based on the `cps21_religion` variable. Income before tax was segmented into three distinct brackets to reflect socioeconomic status. Political preferences were distilled into binary indicators for liberal and conservative vote choices. The dataset was further refined by removing records with missing province information, focusing the analysis on a selected set of variables: age, sex, province, education, religion, and income before tax. This streamlined dataset was then saved in both CSV and Parquet formats, marking the completion of the data cleaning phase and ensuring a well-structured and analysis-ready dataset.

In cleaning the census data, approach was employed to ensure the data's accuracy and relevance for analysis. The age variable was rounded to the nearest whole number to standardize age data across the dataset. Education levels were categorized into three distinct groups: "Limited Education" for those with less than a high school diploma or equivalent, including missing data; "Some Education" for individuals with high school diplomas, trade certificates, or college diplomas below the bachelor's level; and "Highly Educated" for those holding a bachelor's degree or higher. Religious affiliation was simplified to a binary "YES" for those with any religious affiliation or uncertain/missing responses, and "NO" for those explicitly without religious affiliation. Income levels were stratified into three categories: "Lower Middle Class to Poor" for incomes below \$50,000, "Middle Class" for incomes between \$50,000 and \$124,999, and "Upper Middle Class to Wealthy" for incomes of \$125,000 and above. This process streamlined the dataset by focusing on essential variables for sociodemographic analysis—age, sex, province, education, religion, and income before tax. The cleaned data was then saved in both CSV and Parquet formats to facilitate accessibility and further analysis.

# Model

## Method

In forecasting the outcomes of the forthcoming Canadian federal election, statistical techniques like regression analysis, selection of variables, and post-stratification play a pivotal role. Our dataset has some missing variables, but these were deemed negligible in terms of their impact on our predictive model. Initially, the dataset contained 20,921 records, which would have been reduced to 14,544 if entries with missing values were excluded. To maintain the robustness and fullness of our dataset, we opted to retain these incomplete records.

The first step in our modeling approach involved applying logistic regression to estimate the likelihood of a vote being cast for the Liberal or Conservative, based on a set of explanatory variables. Key metrics such as model coefficients and p-values were scrutinized to understand the influence of each predictor. Upon reviewing the p-values, the AIC stepwise selection method was chosen to refine the model further, aiming to lower the AIC score for a more parsimonious fit.

The last stage incorporated post-stratification to gauge the distribution of voter preferences across the identified political factions. This involved segmenting the populace according to our model's predictors and calculating the voting proportions for each party within these segments.

## Model Set-up

## Model justification

## Model Coefficients Interpretation

## Model Equation

We will deploy binary logistic regression analyses to examine the likelihood of individuals casting their vote for the Conservative party or Liberal party. After conducting a thorough investigation into variables that influence voting preferences, we have chosen six key predictors for our models. These include province, age, sex,pre-tax income, religion, and education. Among these, age stands out as the sole continuous variable, while the rest are categorical. Consequently, the framework for our model is structured as follows.

$$log(\frac{p}{1-p}) = \beta_0+\beta_1x_{age}+\beta_2x_{gender}+\beta_3x_{porvince}+\beta_{4}x_{religion}+\beta_{5}x_{income}+\beta_{6}x_{education}$$

$p$ is the probability of an individual casting their vote for a certain political party (Liberal or Conservative).

$\beta_0$ also known as the model's intercept, is the base probability of voting in a certain way when all explanatory variables are set to their reference levels.

$\beta_1$ is for every one-unit increase in age, it quantifies the corresponding variation in the log odds of voting preference.

$\beta_2$ is the influence on the log odds of preferring a particular voting option when the person is identified as male, with $x_{male}$ being assigned a value of 1 for males and 0 for females.

$\beta_3$ to is the coefficients detail the adjustments in the log odds of the voting choice associated with residency in different provinces.

$x_{BC}$, for example, is set to 1 if the person resides in British Columbia, with similar binary indicators for other provinces from $x_{MB}$ through $x_{SK}$.

$\beta_{4}$ captures the shift in log odds of the voting decision when the individual professes a religious belief, with $x_{religion}$ set to 1 for believers and 0 for non-believers.

$\beta_{5}$ is the modification in the log odds of a particular voting outcome for individuals identified as part of the middle class, where $x_{mid}$ is 1 for middle-class individuals and 0 otherwise.

$\beta_{5}$ measures the alteration in the log odds of voting behavior for individuals who fall within the upper middle class to wealthy category, with $x_{upper}$ indicating this socio-economic status by being set to 1, and 0 for others.

## Post-Stratification

Poststratification is a technique used to refine survey data analysis by breaking down the overall population into distinct segments based on specific attributes. Each segment undergoes an independent assessment. This method involves adjusting the weights of survey responses and computing estimates within each distinct group after data collection. This approach proves particularly advantageous when significant variations exist among certain variables within the survey data, such as the 'province' variable in our study, which exhibits considerable diversity. By accounting for these variations, poststratification enhances the accuracy and reliability of statistical estimates. We utilize this technique to project the voter shares for the Liberal or Conservative parties in the upcoming election. Moreover, we are interested in comparing the outcomes from the initial model to those derived after applying AIC stepwise selection, leading us to calculate two versions of the poststratified estimator, denoted as $\hat{y}^{PS}$, for each political party. The preliminary models categorize the populace using six factors: age, sex, province, education, religion, and pre-tax income. Meanwhile, the AIC-adjusted models exclude 'sex' as a variable. We employ the subsequent mathematical expression to compute the estimator $\hat{y}^{PS}$.

$$\hat{y}^{PS} = \frac{\Sigma N_j\hat{y}_j}{\Sigma N_j}$$

In our analysis, $\hat{y}_j$ represents the estimated voting proportion within each subgroup.

$N_j$ denotes the number of individuals within each of these subgroups.

For every subgroup, we first determine its respective proportion estimate. Subsequently, we combine these to ascertain the aggregate voting proportion as predicted by the initial model and also that of the refined model, following the prescribed formula.

# Result

## Analysis of AIC Model

```{r echo=FALSE}
liberal_model <- readRDS(here("models", "liberal_model.rds"))
conservative_model <- readRDS(here("models", "conservative_model.rds"))
```

Table2: Summary the residuals for Conservative Party:
```{r echo=FALSE, warning=FALSE}
liberal_residuals <- posterior_predict(liberal_model) - cleaned_survey_data$vote_liberal

conservative_residuals <- posterior_predict(conservative_model) - cleaned_survey_data$vote_conservative

table_summary <- data.frame(
  Party = c("Liberal", "Conservative"),
  Mean_Residual = c(mean(liberal_residuals, na.rm = TRUE), mean(conservative_residuals, na.rm = TRUE)),
  Median_Residual = c(median(liberal_residuals, na.rm = TRUE), median(conservative_residuals, na.rm = TRUE)),
  SD_Residual = c(sd(liberal_residuals, na.rm = TRUE), sd(conservative_residuals, na.rm = TRUE)),
  IQR_Residual = c(IQR(liberal_residuals, na.rm = TRUE), IQR(conservative_residuals, na.rm = TRUE))
)

print(table_summary)
```
Table3: Summary the coefficient for Liberal Party:
```{r echo=FALSE, warning=FALSE}

liberal_coefs <- coef(liberal_model)
conservative_coefs <- coef(conservative_model)

liberal_coefs_df <- data.frame(Estimate = liberal_coefs, row.names = NULL)
conservative_coefs_df <- data.frame(Estimate = conservative_coefs, row.names = NULL)

liberal_coefs_df$Term <- names(liberal_coefs)
conservative_coefs_df$Term <- names(conservative_coefs)

liberal_coefs_df <- liberal_coefs_df[, c("Term", "Estimate")]
conservative_coefs_df <- conservative_coefs_df[, c("Term", "Estimate")]

knitr::kable(liberal_coefs_df, caption = "Coefficients of the Liberal Model", row.names = FALSE)
knitr::kable(conservative_coefs_df, caption = "Coefficients of the Conservative Model", row.names = FALSE)

```

## Plot of binary logistic regression models

# Discussion

# Appendix

# References

### 2024-04-08 paper/paper.qmd
Add files via upload

@@
 ---
-title: "Predicting the Outcome of the 2025 Election in Canada by a Regression Analysis"
+title: "Predicting Participants' Vote Choice Between Conservative and Liberty in the 2025 Election By Binary Linear Regression Model"
 title-block-banner: true
@@
 library(arrow)
+library(tidybayes)
 ```
@@
 ### Data Summary Measures 
-Table 1: Summary varibales in Census and Survey Data
-```{r echo=FALSE}
+```{r}
+#| label: tbl-data-summary
+#| tbl-cap: Summary of Numerical Variables Across Census and Survey Data
+#| echo: false
 numeric_summary_df <- data.frame(
@@
 
-knitr::kable(numeric_summary_df, caption = "Summary of Numerical Variables Across Census and Survey Data")
-
+knitr::kable(numeric_summary_df)
 ```
 
-The statistical summary of the census and survey data reveals age distributions with the census data capturing a narrower age range (15 to 80 years, with a median of 54) compared to the broader age span in the survey data (18 to 97 years, with a median of 53).
+@tbl-data-summary summaries the census and survey data reveals age distributions with the census data capturing a narrower age range (15 to 80 years, with a median of 54) compared to the broader age span in the survey data (18 to 97 years, with a median of 53).
 The average ages for the census and survey populations are 52.18 and 51.3 years, respectively.
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-df_long <- pivot_longer(na.omit(survey_data_new), cols = starts_with("vote_"), names_to = "Party", values_to = "Vote")
+df_long <- pivot_longer(na.omit(cleaned_survey_data), cols = starts_with("vote_"), names_to = "Party", values_to = "Vote")
 
-# Plot a grouped bar plot
 ggplot(df_long, aes(x = Party, fill = as.factor(Vote))) +
@@
 
+We define our Bayesian logistic regression model for the probability of an individual voting for the Liberal/Conservative party as follows:
+
+- $y_i$: Binary outcome of voting for the Liberal/Conservative party (1) or not (0)
+- $\pi_i$: Probability of voting for the Liberal/Conservative party
+
+\begin{align}
+y_i | \pi_i &\sim \text{Bernoulli}(\pi_i) \\
+\text{logit}(\pi_i) &= \beta_0 + \alpha^{age}_{a[i]} + \alpha^{gender}_{g[i]} + \alpha^{province}_{p[i]} + \alpha^{religion}_{r[i]} + \alpha^{income}_{m[i]} + \alpha^{education}_{e[i]} \\
+\beta_0 &\sim \text{Normal}(0, 2.5) \\
+\alpha_{a}^{age} &\sim \text{Normal}(0, \sigma^{2}_{age}) \quad \text{for } a \text{ in } 1, 2, \ldots, A \\
+\alpha_{g}^{gender} &\sim \text{Normal}(0, \sigma^{2}_{gender}) \quad \text{for } g \text{ in } Male,Female \\
+\alpha_{p}^{province} &\sim \text{Normal}(0, \sigma^{2}_{province}) \quad \text{for } p \text{ in } BC, AB, MB, NB, NL, NS, ON, PE, QC, SK \\
+\alpha_{r}^{religion} &\sim \text{Normal}(0, \sigma^{2}_{religion}) \quad \text{for } r \text{ in } YES,NO \\
+\alpha_{m}^{income} &\sim \text{Normal}(0, \sigma^{2}_{income}) \quad \text{for } m \text{ in } Lower Class, Middle Class, Upper Class\\
+\alpha_{e}^{education} &\sim \text{Normal}(0, \sigma^{2}_{education}) \quad \text{for } e \text{ in } Low Education, Some Education, High Education \\
+\sigma^{2}_{age} &\sim \text{Exponential}(1) \\
+\sigma^{2}_{gender} &\sim \text{Exponential}(1) \\
+\sigma^{2}_{province} &\sim \text{Exponential}(1) \\
+\sigma^{2}_{religion} &\sim \text{Exponential}(1) \\
+\sigma^{2}_{income} &\sim \text{Exponential}(1) \\
+\sigma^{2}_{education} &\sim \text{Exponential}(1) 
+\end{align}
+
 ## Model justification
@@
 
-$\beta_0$ also known as the model's intercept, is the base probability of voting in a certain way when all explanatory variables are set to their reference levels.
+$\beta_0$(Intercept): This is the base log odds of an individual voting for the political party when all the explanatory variables are at their reference levels.
 
-$\beta_1$ is for every one-unit increase in age, it quantifies the corresponding variation in the log odds of voting preference.
+$\beta_1$(age): This coefficient represents the change in the log odds of voting for the political party for each additional year of age. A positive coefficient indicates that as age increases.
 
-$\beta_2$ is the influence on the log odds of preferring a particular voting option when the person is identified as male, with $x_{male}$ being assigned a value of 1 for males and 0 for females.
+$\beta_2$(gender): This coefficient indicates the difference in the log odds of voting for the political party for males compared to females (the reference category).
+A positive coefficient suggests that males are more likely to vote this party than females.
 
-$\beta_3$ to is the coefficients detail the adjustments in the log odds of the voting choice associated with residency in different provinces.
+$\beta_3$(province): Each of these coefficients (e.g.
+$\beta_BC$, $\beta_ON$, etc) measures the change in the log odds of voting for the political party for individuals living in each respective province compared to the reference province.
+Each coefficient reflects the unique effect of residing in that province on voting behavior.
 
-$x_{BC}$, for example, is set to 1 if the person resides in British Columbia, with similar binary indicators for other provinces from $x_{MB}$ through $x_{SK}$.
+$\beta_4$(religion): This coefficient captures the change in the log odds of voting this political party if an individual professes a religious belief (1) versus no religious belief (0, the reference category).
 
-$\beta_{4}$ captures the shift in log odds of the voting decision when the individual professes a religious belief, with $x_{religion}$ set to 1 for believers and 0 for non-believers.
+$\beta_5$(income): This coefficients reflect the differences in the log odds of voting for the political party based on income levels.
 
-$\beta_{5}$ is the modification in the log odds of a particular voting outcome for individuals identified as part of the middle class, where $x_{mid}$ is 1 for middle-class individuals and 0 otherwise.
-
-$\beta_{5}$ measures the alteration in the log odds of voting behavior for individuals who fall within the upper middle class to wealthy category, with $x_{upper}$ indicating this socio-economic status by being set to 1, and 0 for others.
+$\beta_6$(education): Similar to income, these coefficients represent the effect of education level on the log odds of voting for this political party.
 
@@
 
-# Appendix
+# Appendix {.unnumbered}
+
+# Additional data details
+
+# Model details {#sec-model-details}
+
+## Posterior predictive check
+
+```{r echo=FALSE, warning=FALSE}
+pp_check(liberal_model, type = "hist")
+```
+Histogram of posterior predictive distributions from the liberal model.
+This plot compares the observed counts of the number of votes for the Liberal party (indicated by the dark line) with the simulated counts from the posterior predictive distribution (shown as histograms).
+The overlap between the observed counts and the predictive distribution suggests how well the model captures the data.
+Areas where the observed counts fall outside the bulk of the simulated distributions may indicate model misfit.
+
+```{r echo=FALSE, warning=FALSE}
+pp_check(conservative_model, type = "hist")
+```
+
+```{r echo=FALSE, warning=FALSE,  message=FALSE, fig.width=8, fig.height=6}
+survey_data <- read_csv(here("data", "analysis_data", "cleaned_survey_data.csv"))
+prior_covariates <- normal(location = 0, scale = 2.5, autoscale = FALSE)
+prior_intercept <- normal(0, 2.5)
+pp_plot <- posterior_vs_prior(liberal_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(
+    legend.position = "bottom",
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    plot.subtitle = element_text(size = 10),
+    axis.title.y = element_text(size = 7, face = "bold"),
+    axis.title.x = element_text(size = 7, face = "bold"),
+    legend.text = element_text(size = 5),
+    legend.title = element_text(size = 7)
+  ) +
+  coord_flip() +
+  ggtitle("Comparison of Posterior and Prior Distributions",
+          subtitle = "This plot visualizes how posterior distributions of model parameters compare with their specified priors for the liberal model.") +
+  xlab("Density") +
+  ylab("Parameters")
+
+# Print the plot
+print(pp_plot)
+```
+
+```{r echo=FALSE, warning=FALSE,  message=FALSE, fig.width=8, fig.height=6}
+prior_covariates <- normal(location = 0, scale = 2.5, autoscale = FALSE)
+prior_intercept <- normal(0, 2.5)
+pp_plot <- posterior_vs_prior(conservative_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(
+    legend.position = "bottom",
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    plot.subtitle = element_text(size = 10),
+    axis.title.y = element_text(size = 7, face = "bold"),
+    axis.title.x = element_text(size = 7, face = "bold"),
+    legend.text = element_text(size = 5),
+    legend.title = element_text(size = 7)
+  ) +
+  coord_flip() +
+  ggtitle("Comparison of Posterior and Prior Distributions",
+          subtitle = "This plot visualizes how posterior distributions of model parameters compare with their specified priors for the conservative model.") +
+  xlab("Density") +
+  ylab("Parameters")
+
+# Print the plot
+print(pp_plot)
+
+```
+
+## Diagnostics
 

### 2024-04-08 script/02_cleanup_data.R
Add files via upload

@@ -1,0 +1,86 @@
+
+library(readr)
+library(dplyr)
+library(arrow)
+library(tidyr)
+library(ggplot2)
+library(MASS)
+library(knitr)
+library(summarytools)
+library(here)
+
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+census_data <- read_csv(here("data", "raw_data","rawdata_census.csv"))
+survey_data <- read_csv(here("data", "raw_data","survey_data.csv"))
+
+prop_man <- sum(survey_data$cps21_genderid == "1") / nrow(survey_data)
+prop_woman <- sum(survey_data$cps21_genderid == "2") / nrow(survey_data)
+
+
+survey_data_new <- survey_data %>%
+  mutate(
+    age = cps21_age,
+    sex = sample(c("Male", "Female"), size = nrow(survey_data), replace = TRUE, prob = c(prop_man, prop_woman)),
+    province = case_when(
+      cps21_province == 1 ~ "Alberta",
+      cps21_province == 2 ~ "British Columbia",
+      cps21_province == 3 ~ "Manitoba",
+      cps21_province == 4 ~ "New Brunswick",
+      cps21_province == 5 ~ "Newfoundland and Labrador",
+      cps21_province == 6  ~ "Nova Scotia",
+      cps21_province == 7  ~ "Ontario",
+      cps21_province == 8  ~ "Prince Edward Island",
+      cps21_province == 9  ~ "Quebec",
+      cps21_province == 10 ~ "Saskatchewan",
+      TRUE ~ NA_character_  
+    ),
+    education = case_when(
+      cps21_education %in% c(1, 2, 3, 12) ~ "Low Education",
+      cps21_education %in% c(4, 5, 6, 7, 8) ~ "Some Education",
+      cps21_education %in% c(9, 10, 11) ~ "High Education"
+    ),
+    religion = ifelse(cps21_religion == 1, "NO", "YES"),
+    income_before_tax = case_when(
+      cps21_income_number >= 125000 ~ "Upper Class",
+      cps21_income_number >= 50000 ~ "Middle Class",
+      TRUE ~ "Lower Class"
+    ),
+    vote_liberal = as.integer(cps21_votechoice == 1),
+    vote_conservative = as.integer(cps21_votechoice == 2)
+  ) %>%
+  filter(!is.na(province)) %>%
[…]

### 2024-04-08 script/04_model.R

@@ -7,34 +7,53 @@
 # Pre-requisites: The 'rstanarm' package for Bayesian modeling, 'readr' for data manipulation, and 'here' for path management
 # The 'cleaned_data' dataset must be pre-processed before using it in the model.
 
-
 library(rstanarm)
 library(dplyr)
-library(here)
 library(readr)
+library(here)
 
+set.seed(302)
+
+# Read in the cleaned survey data
 survey_data <- read_csv(here("data", "analysis_data", "cleaned_survey_data.csv"))
 
+# Convert the necessary columns to factors
 survey_data <- survey_data %>%
-  mutate(province = as.factor(province),
-         sex = as.factor(sex),
-         education = as.factor(education),
-         religion = as.factor(religion),
-         income_before_tax = as.factor(income_before_tax))
+  mutate(
+    province = as.factor(province),
+    sex = as.factor(sex),
+    education = as.factor(education),
+    religion = as.factor(religion),
+    income_before_tax = as.factor(income_before_tax)
+  )
 
+# Set up the priors
+prior_intercept <- normal(0, 2.5)
+prior_covariates <- normal(0, scale = 1)  # The scale can be treated as 1/sqrt(lambda) for Exponential(lambda)
 
-liberal_model <- stan_glm(vote_liberal ~ age + sex + province + education + religion + income_before_tax,
-                          data = survey_data, family = binomial(link = "logit"))
-
-
-conservative_model <- stan_glm(vote_conservative ~ age + sex + province + education + religion + income_before_tax,
-                               data = survey_data, family = binomial(link = "logit"))
-
-saveRDS(
-  liberal_model,
-  file = here("models", "liberal_model.rds")
+# Define the model using stan_glm
+liberal_model <- stan_glm(
+  vote_liberal ~ age + sex + province + education + religion + income_before_tax,
+  data = survey_data, 
+  family = binomial(link = "logit"),
+  prior_intercept = prior_intercept,
+  prior = prior_covariates,
+  prior_aux = exponential(1),
+  chains = 4,
+  iter = 2000
 )
-saveRDS(
-  conservative_model,
-  file = here("models", "conservative_model.rds")
+
+conservative_model <- stan_glm(
+  vote_conservative ~ age + sex + province + education + religion + income_before_tax,
+  data = survey_data, 
+  family = binomial(link = "logit"),
+  prior_intercept = prior_intercept,
+  prior = prior_covariates,
[…]

### 2024-04-08 script/01_cleanup_data.R
Delete script/01_cleanup_data.R

@@ -1,81 +1,0 @@
-
-library(readr)
-library(dplyr)
-library(arrow)
-library(tidyr)
-library(ggplot2)
-library(MASS)
-library(knitr)
-library(summarytools)
-library(here)
-
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-
-census_data <- read_csv(here("data", "raw_data","rawdata_census.csv"))
-survey_data <- read_csv(here("data", "raw_data","survey_data.csv"))
-
-prop_man <- sum(survey_data$cps21_genderid == "1") / nrow(survey_data)
-prop_woman <- sum(survey_data$cps21_genderid == "2") / nrow(survey_data)
-
-
-survey_data_new <- survey_data %>%
-  mutate(
-    age = cps21_age,
-    sex = sample(c("Male", "Female"), size = nrow(survey_data), replace = TRUE, prob = c(prop_man, prop_woman)),
-    province = case_when(
-      cps21_province == 1 ~ "Alberta",
-      cps21_province == 2 ~ "British Columbia",
-      cps21_province == 3 ~ "Manitoba",
-      cps21_province == 4 ~ "New Brunswick",
-      cps21_province == 5 ~ "Newfoundland and Labrador",
-      TRUE ~ NA_character_  
-    ),
-    education = case_when(
-      cps21_education %in% c(1, 2, 3, 12) ~ "Limited Education",
-      cps21_education %in% c(4, 5, 6, 7, 8) ~ "Some Education",
-      cps21_education %in% c(9, 10, 11) ~ "Highly Educated"
-    ),
-    religion = ifelse(cps21_religion == 1, "NO", "YES"),
-    income_before_tax = case_when(
-      cps21_income_number >= 125000 ~ "Upper Middle Class to Wealthy",
-      cps21_income_number >= 50000 ~ "Middle Class",
-      TRUE ~ "Lower Middle Class to Poor"
-    ),
-    vote_liberal = as.integer(cps21_votechoice == 1),
-    vote_conservative = as.integer(cps21_votechoice == 2)
-  ) %>%
-  filter(!is.na(province)) %>%
-  dplyr::select(age, sex, province, education, religion, income_before_tax, vote_liberal, vote_conservative) 
-
-
-write.csv(survey_data_new, here("data", "analysis_data", "cleaned_survey_data.csv"), row.names = FALSE)
[…]

### 2024-04-08 paper/paper.qmd
Add files via upload

@@
 ---
-title: "Predicting Participants' Vote Choice Between Conservative and Liberty in the 2025 Election By Binary Linear Regression Model"
+title: "Predicting Probability of Participants' Vote of Conservative and Liberty in 2025 Canadian election "
 title-block-banner: true

### 2024-04-12 paper/paper(1).qmd
Add files via upload

--- 2024-04-08 paper/paper.qmd
@@
 link-citations: true
+editor: 
+  markdown: 
+    wrap: sentence
 ---
@@
 
-**Age Adjustment**: In the census data, age is presented as a decimal number. For consistency with the survey data, round this value to the nearest whole number.
+**Age Adjustment**: In the census data, age is presented as a decimal number.
+For consistency with the survey data, round this value to the nearest whole number.
 
@@
 ### Data Summary Measures
+
 ```{r}
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-age-distribution
+#| tbl-cap: "Age Distribution Comparison Between Survey and Census Data"
+#| echo: false
 cleaned_survey_data <- read_parquet(here("data", "analysis_data","cleaned_survey_data.parquet"))
@@
   labs(
-    title = "Plot.1 Age Distribution Comparison",
     x = "Age",
@@
 
-The overlapping histogram illustrates the age distributions from census and survey datasets, with the census data in red displaying a more concentrated and unimodal age distribution peaking between 50 and 60 years and tapering off sharply at 80.
+@fig-age-distribution illustrates the age distributions from census and survey datasets, with the census data in red displaying a more concentrated and unimodal age distribution peaking between 50 and 60 years and tapering off sharply at 80.
 In contrast, the survey data, shown in blue, reveals a broader spread of ages with a right-skewed tail extending to 97 years, indicating the inclusion of older respondents.
@@
 This visual comparison underscores the differing age profiles captured by the two datasets and a significant density of middle-aged respondents in both populations.
+\newpage
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-province-distribution
+#| fig-cap: "Comparison of Province Variable Between Survey and Census Data"
+#| echo: false
 combined_provinces <- rbind(
@@
   geom_bar(position = "dodge") +
-  labs(title = "Plot.2 Comparison of Province Variable", x = "Province", y = "Count") +  
+  labs(x = "Province", y = "Count") +  
   scale_fill_manual(values = c("Survey Dataset" = "red", "Census Dataset" = "blue")) +  
@@
 
-The bar chart depicts the frequency distribution of respondents across different provinces as collected in two datasets: the census and survey data.
+@fig-province-distribution depicts the frequency distribution of respondents across different provinces as collected in two datasets: the census and survey data.
 Each province is represented on the x-axis, and the corresponding count of respondents is displayed on the y-axis.
@@
 The chart facilitates a comparative analysis of the datasets, revealing disparities and similarities in the population coverage across provinces, which could be indicative of sampling strategies or the demographic spread within the datasets.
+\newpage
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-education-distribution
+#| fig-cap: "Line Chart Comparison of Education Levels Between Survey and Census Data"
+#| echo: false
 combined_data_education <- na.omit(rbind(
@@
   scale_color_manual(values = c("Survey Dataset" = "red", "Census Dataset" = "blue")) +
-  labs(title = "Line Chart Comparison of Education Levels",
+  labs(
        x = "Education Level",
@@
 
-The line chart presented compares the distribution of education levels across two different datasets, one from a survey and another from a census, differentiated by colors—red for the survey and blue for the census.
+@fig-education-distribution presented compares the distribution of education levels across two different datasets, one from a survey and another from a census, differentiated by colors—red for the survey and blue for the census.
 Education levels are divided into three categories along the x-axis: "Highly Educated", "Limited Education", and "Some Education", with the y-axis displaying the count of individuals within each category.
@@
 The differences observed in the chart might also reflect methodological variations in data collection or inherent biases within the sampling frames used.
+\newpage
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-
+#| label: fig-religion-distribution
+#| fig-cap: "Bar Chart Comparison of Religion Across Survey and Census Data"
+#| echo: false
 combined_data_religion <- rbind(
@@
 ggplot(combined_data_religion, aes(x = Religion, fill = Dataset)) +
-  geom_bar(position = "dodge") +  # Position bars side by side
-  labs(title = "Plot.4 Comparison of Religion", x = "Religion", y = "Count") +  
+  geom_bar(position = "dodge") +  
+  labs(x = "Religion", y = "Count") +  
   scale_fill_manual(values = c("Survey Dataset" = "pink", "Census Dataset" = "red")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Optional: to improve readability of x-axis labels
-
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))  
 ```
 
-The bar graph depicts the frequency of individuals categorized by religious affiliation within two datasets: census and survey.
+@fig-religion-distribution depicts the frequency of individuals categorized by religious affiliation within two datasets: census and survey.
 Each dataset's frequency is represented by a bar in distinct shades, with a darker red indicating the census dataset and a lighter pink representing the survey dataset.
@@
 The visual disparity in bar heights, especially within the 'YES' category, suggests a higher prevalence of religious affiliation reported in the census dataset than in the survey dataset.
+\newpage
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-income-distribution
+#| fig-cap: "Bar Chart Comparison of Income Before Tax Between Survey and Census Data"
+#| echo: false
 combined_data_income <- na.omit(rbind(
@@
   geom_bar(position = "dodge") +
-  labs(title = "Plot.5 Comparison of Income Before Tax", x = "Income Before Tax", y = "Count") +
+  labs(x = "Income Before Tax", y = "Count") +
   scale_fill_manual(values = c("Survey Dataset" = "orange", "Census Dataset" = "brown")) +
@@
 
-The bar chart displays the distribution of income categories before tax across two datasets: census and survey.
+@fig-income-distribution displays the distribution of income categories before tax across two datasets: census and survey.
 The income categories are defined as 'Lower Middle Class to Poor', 'Middle Class', and 'Upper Middle Class to Wealthy', and are represented on the x-axis.
@@
 
+\newpage
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: fig-voting-preferences
+#| fig-cap: "Bar Chart Comparison of Voting Preferences"
+#| echo: false
 df_long <- pivot_longer(na.omit(cleaned_survey_data), cols = starts_with("vote_"), names_to = "Party", values_to = "Vote")
@@
   geom_bar(position = "dodge", stat = "count") +
-  labs(title = "Plot.6 Comparison of Voting Preferences", x = "Party", y = "Count") +
+  labs(x = "Party", y = "Count") +
   scale_fill_manual(values = c("red", "blue"), name = "Party Choice", labels = c("Did Not Vote", "Voted")) +
@@
 ```
+
+@fig-voting-preferences contrasts the voting preferences for the Conservative and Liberal parties, delineating counts of participants who voted (blue bars) against those who did not (red bars).
+Notably, there is a substantial number of non-voters in the Conservative category, exceeding their Liberal counterparts, suggesting a larger disenchantment or mobilization challenge within the Conservative base.
+Despite this, the voter turnout (blue bars) is fairly balanced between the parties, indicating a competitive engagement among those who participated in the vote.
+The overall higher presence of red bars signifies a general trend of voter disengagement, which may warrant further investigation through regression analysis and post-stratification to grasp the full scope of electoral dynamics and the broader implications for the Canadian democratic process.
+\newpage
 
@@
 
+```{=tex}
 \begin{align}
@@
 \end{align}
-
+```
 ## Model justification
@@
 
-$\beta_1$(age): This coefficient represents the change in the log odds of voting for the political party for each additional year of age. A positive coefficient indicates that as age increases.
+$\beta_1$(age): This coefficient represents the change in the log odds of voting for the political party for each additional year of age.
+A positive coefficient indicates that as age increases.
 
@@
 Table2: Summary the residuals for Conservative Party:
+
 ```{r echo=FALSE, warning=FALSE}
@@
 ```
+
 Table3: Summary the coefficient for Liberal Party:
+
 ```{r echo=FALSE, warning=FALSE}
@@
 
+\newpage
+
 ## Posterior predictive check
 
-```{r echo=FALSE, warning=FALSE}
-pp_check(liberal_model, type = "hist")
+```{r fig-liberal-model-1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior Predictive Check: Observed vs. Simulated Vote Counts in the Liberal Model"}
+library(bayesplot)
+
+liberal_model_plot <- pp_check(liberal_model, type = "hist") +
+  theme(plot.title = element_text(size = 10))
+
+print(liberal_model_plot)
 ```
+
+@fig-liberal-model-1 illustrates a posterior predictive check for the liberal model, comparing observed vote counts with those generated by the model's simulations.
+The dark solid line represents the observed data, while the lighter blue lines represent simulated vote counts from the posterior distribution.
+The close tracking of the simulated lines to the observed line suggests that the model can effectively replicate the patterns seen in the real vote counts.
+This indicates a good model fit, as the simulations encompass the range of observed data, providing confidence in the model's predictions.
+The alignment of the simulations with the observed data points to the adequacy of the model's structure and the priors in capturing the underlying trends of the voting behavior it aims to represent.
+The graph also visualizes the variance in the simulations, reflecting the model's probabilistic nature and the inherent uncertainty in predicting complex phenomena such as voting behavior.
+
 Histogram of posterior predictive distributions from the liberal model.
@@
 Areas where the observed counts fall outside the bulk of the simulated distributions may indicate model misfit.
+\newpage
 
-```{r echo=FALSE, warning=FALSE}
-pp_check(conservative_model, type = "hist")
+```{r fig-conservative-model, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior Predictive Check: Observed vs. Simulated Vote Counts in the Conservative Model"}
+library(bayesplot)
+
+conservative_model_plot <- pp_check(conservative_model, type = "hist") + 
+  theme(plot.title = element_text(size = 14)) 
+print(conservative_model_plot)
+
 ```
 
-```{r echo=FALSE, warning=FALSE,  message=FALSE, fig.width=8, fig.height=6}
+@fig-conservative-model performs a posterior predictive check for a conservative model by overlaying observed vote counts against simulated data derived from the model's posterior distribution.
+The observed data is denoted by a solid line, while the simulations from the posterior are indicated by lighter lines.
+The congruence between these two sets of lines—where the simulated data traces the shape and trend of the observed data closely—suggests that the model has a high level of accuracy in reflecting the observed outcomes.
+This indicates a successful fit of the model to the data, affirming the appropriateness of the selected priors and the model's structure.
+The spread of the lighter lines around the darker one provides insight into the inherent uncertainty of the model's predictions, which is an expected characteristic of predictive modelling in complex, real-world situations.
+
+\newpage
+
+```{r fig-liberal-model, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.cap="Comparison of Posterior and Prior Distributions in the Liberal Model"}
+library(readr)
+library(bayesplot)
+library(here)
+
 survey_data <- read_csv(here("data", "analysis_data", "cleaned_survey_data.csv"))
+
 prior_covariates <- normal(location = 0, scale = 2.5, autoscale = FALSE)
 prior_intercept <- normal(0, 2.5)
+
 pp_plot <- posterior_vs_prior(liberal_model) +
@@
   coord_flip() +
-  ggtitle("Comparison of Posterior and Prior Distributions",
-          subtitle = "This plot visualizes how posterior distributions of model parameters compare with their specified priors for the liberal model.") +
   xlab("Density") +
@@
 
-# Print the plot
 print(pp_plot)
+
 ```
 
-```{r echo=FALSE, warning=FALSE,  message=FALSE, fig.width=8, fig.height=6}
+@fig-liberal-model portrays the posterior and prior distributions for parameters in a Bayesian liberal model, with a stark divergence in the intercept suggesting significant data-driven adjustments from the model's baseline estimation.
+Parameters representing demographic and geographical factors are plotted as colored dots along an axis, indicating median values and the extent of uncertainty.
+While the priors and posteriors largely overlap, indicating consistent estimates for many parameters, the intercept's noticeable shift underscores the data's impactful role in refining the model, particularly highlighting the updated understanding of the model's fundamental starting point.
+
+\newpage
+
+```{r fig-conservative-posterior, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.cap="Comparison of Posterior and Prior Distributions in the Conservative Model"}
+library(bayesplot)
+
 prior_covariates <- normal(location = 0, scale = 2.5, autoscale = FALSE)
 prior_intercept <- normal(0, 2.5)
+
 pp_plot <- posterior_vs_prior(conservative_model) +
@@
   coord_flip() +
-  ggtitle("Comparison of Posterior and Prior Distributions",
-          subtitle = "This plot visualizes how posterior distributions of model parameters compare with their specified priors for the conservative model.") +
   xlab("Density") +
@@
 
-# Print the plot
 print(pp_plot)
@@
 
+@fig-conservative-posterior presents a side-by-side comparison of the median and spread of prior and posterior distributions for the parameters in a Bayesian model, applied to the Conservative context.
+Key findings include the posterior distribution of the "age" parameter mirroring its prior, which validates the initial assumption about its influence.
+In contrast, the intercept and sigma parameters show slight shifts, indicating the data's role in refining these estimates.
+The placement of medians for other parameters—like sex, religion, and province—demonstrates the data's impact in confirming or adjusting prior beliefs.
+Overall, the alignment of posterior distributions with priors confirms the model's accuracy and the informative value of the data in capturing the effects on the dependent variable, suggesting a robust model fit.
+
+\newpage
+
 ## Diagnostics

### 2024-04-13 paper/paper(1).qmd
Add files via upload

@@
 
-@fig-age-distribution illustrates the age distributions from census and survey datasets, with the census data in red displaying a more concentrated and unimodal age distribution peaking between 50 and 60 years and tapering off sharply at 80.
-In contrast, the survey data, shown in blue, reveals a broader spread of ages with a right-skewed tail extending to 97 years, indicating the inclusion of older respondents.
-Both distributions share a common median age range, highlighted by the combined purple hue in the overlap, but the census data consistently show higher frequencies across most age bins.
-This visual comparison underscores the differing age profiles captured by the two datasets and a significant density of middle-aged respondents in both populations.
+@fig-age-distribution displays the age distribution from both census (in red) and survey (in blue) datasets.
+The census distribution exhibits a unimodal peak around the 50-60 year age range and a sharp decline beyond 80 years, suggesting a concentration of middle to late-middle-aged respondents.
+Conversely, the survey dataset portrays a wider distribution, extending towards older ages with a noticeable skew to the right, indicating the presence of older individuals up to 97 years old.
+The regions of overlap appear purple, indicating age ranges common to both datasets, with the census data generally showing higher frequencies in most age categories.
+This comparison highlights the distinct age profiles captured by the two sources, with a significant representation of middle-aged individuals in both, with the survey dataset capturing a broader demographic.
 \newpage
@@
 
-@fig-province-distribution depicts the frequency distribution of respondents across different provinces as collected in two datasets: the census and survey data.
-Each province is represented on the x-axis, and the corresponding count of respondents is displayed on the y-axis.
-The bars are color-coded, with blue indicating the survey dataset and red representing the census dataset.
-The bars are placed side by side, or 'dodged', allowing for a direct visual comparison between the two datasets within each provincial category.
-
-From a statistical perspective, Ontario has the highest frequency in the survey dataset, which substantially exceeds the count in the census dataset, indicating a larger sample or population size recorded in the survey for this province.
-Conversely, the counts for British Columbia and Alberta show a relatively balanced representation between the two datasets.
-The chart facilitates a comparative analysis of the datasets, revealing disparities and similarities in the population coverage across provinces, which could be indicative of sampling strategies or the demographic spread within the datasets.
+@fig-province-distribution contrasts the provincial distribution of respondents from both survey and census datasets, with provinces along the x-axis and respondent counts on the y-axis.
+The survey data, shown in blue, reaches its highest point in Ontario, indicating a significantly larger number of respondents compared to other provinces in the survey.
+This peak towers above all other survey data points and also surpasses the census data count for Ontario, which suggests a disproportionate representation or potentially an over-sampling in the survey for Ontario.
+In contrast, the lowest point for the survey dataset appears in Prince Edward Island, with very few respondents, paralleled by a similarly low count for this province in the census dataset, shown in red.
+Notably, the census data peaks in Quebec, where the red bar indicates the highest frequency among all provinces for the census, while Alberta's census count is at its lowest, barely rising above the baseline.
+This visual comparison reveals not only the variations in population coverage between the two types of data but also significant regional differences within the datasets, which could reflect varied sampling methods or demographic distributions.
 \newpage
@@
 @fig-education-distribution presented compares the distribution of education levels across two different datasets, one from a survey and another from a census, differentiated by colors—red for the survey and blue for the census.
-Education levels are divided into three categories along the x-axis: "Highly Educated", "Limited Education", and "Some Education", with the y-axis displaying the count of individuals within each category.
+Education levels are divided into three categories along the x-axis: "Highly Educated", "Limited Education", and "Some Education" in census dataset, with the y-axis displaying the count of individuals within each category.
+While the education level is divided into "Low Education", "Some Education" and "High Education" in the survey dataset.
 A noticeable trend is the inverse relationship between the two datasets from "Highly Educated" to "Limited Education": the count for the Census dataset declines while that for the Survey dataset rises, suggesting a disparity in the representation of education levels between the two data sources.
@@
 
-@fig-religion-distribution depicts the frequency of individuals categorized by religious affiliation within two datasets: census and survey.
-Each dataset's frequency is represented by a bar in distinct shades, with a darker red indicating the census dataset and a lighter pink representing the survey dataset.
-The x-axis bifurcates the data into two groups: those without religious affiliation ('NO') and those with religious affiliation ('YES').
-
-The y-axis provides a count of individuals in each category.
-Notably, the census dataset shows a substantially higher count of individuals with a religious affiliation compared to those without.
-This pattern is less pronounced in the survey dataset, where the frequencies of individuals with and without religious affiliation are more comparable.
-The visual disparity in bar heights, especially within the 'YES' category, suggests a higher prevalence of religious affiliation reported in the census dataset than in the survey dataset.
+@fig-religion-distribution delineates the reported religious affiliations in both the census and survey datasets, differentiated by color intensity, with the census depicted in a darker red and the survey in a lighter pink.
+The x-axis is categorized into 'No' for non-affiliated individuals and 'Yes' for those with religious affiliation.
+A striking contrast is observed in the 'Yes' category, where the census data’s count towers over that of the survey, indicating a greater number of religiously affiliated respondents.
+Conversely, for those reporting no religious affiliation, the survey's lighter pink bar is comparable in height to the census's, suggesting a more even distribution between the two datasets.
+This discrepancy underscores a pronounced difference in the representation of religious affiliation between the two data sources, potentially alluding to divergent demographic characteristics or response patterns within the datasets.
 \newpage
@@
 
-@fig-income-distribution displays the distribution of income categories before tax across two datasets: census and survey.
-The income categories are defined as 'Lower Middle Class to Poor', 'Middle Class', and 'Upper Middle Class to Wealthy', and are represented on the x-axis.
-The y-axis measures the count of individuals within each income bracket.
-
-In the 'Lower Middle Class to Poor' category, there is a significant count of individuals in the census dataset, shown by a tall bar, which vastly exceeds the count from the survey dataset.
-For the 'Middle Class' bracket, the census dataset again shows a higher frequency, but with a smaller margin compared to the survey dataset.
-Lastly, in the 'Upper Middle Class to Wealthy' category, both datasets depict a lower frequency of individuals than in the other categories, but the survey dataset shows a slightly higher count than the census dataset in this high-income bracket.
-
-The bars for the census dataset are colored in a deep red, while the bars for the survey dataset are in orange, with each pair of bars positioned next to one another for a clear visual comparison.
-This color differentiation, along with the bar placement, facilitates an immediate comparative analysis of the socioeconomic composition of the populations captured in the two datasets, indicating a notably higher representation of lower income levels within the census data.
+@fig-income-distribution compares the distribution of socioeconomic groups before tax as represented in the census and survey datasets, with income hierarchy arrayed along the x-axis and the number of individuals in each bracket indicated on the y-axis.
+Both datasets show a similar count in the 'Upper Middle Class to Wealthy', 'Upper Class', 'Lower Middle Class to Poor' and 'Lower Class' category.
+The census dataset, indicated by the significantly taller deep red bar as opposed to the shorter orange bar of the survey dataset.
+The 'Middle Class' brackethas a higher representation in the survey data but by a less pronounced margin.
+The colors—deep red for the census and orange for the survey—aid in the visual differentiation between the two datasets, enabling a direct comparison of how each income level is represented within them, and suggest a higher census capture of lower-income brackets compared to the survey data.
 

### 2024-04-13 paper/paper(1).qmd
Add files via upload

@@
 library(tidybayes)
+library(bayesplot)
 ```
@@
 # Model
+We utilized the rstanarm package for constructing the generalized linear model[@R-rstanarm], the rstanarm package serves as a user-friendly interface in R for fitting Bayesian regression models using the Stan probabilistic programming language.
+It enables users to effortlessly construct various types of regression models, including linear, logistic, and Poisson regression, while leveraging the power of Bayesian methods for inference.
+By seamlessly integrating with Stan, rstanarm provides efficient algorithms for model fitting and accurate estimates of uncertainty.
+Additionally, the package offers diagnostic tools for assessing model convergence and sensitivity to prior specifications, making it an invaluable resource for Bayesian data analysis in R.
 
@@
 ## Model Set-up
-
 We define our Bayesian logistic regression model for the probability of an individual voting for the Liberal/Conservative party as follows:
@@
 Table2: Summary the residuals for Conservative Party:
+```{r echo=FALSE, warning=FALSE}
 
-```{r echo=FALSE, warning=FALSE}
 liberal_residuals <- posterior_predict(liberal_model) - cleaned_survey_data$vote_liberal
-
 conservative_residuals <- posterior_predict(conservative_model) - cleaned_survey_data$vote_conservative
@@
 
-print(table_summary)
+# Create a table of the data
+kable(table_summary, caption = "Summary of Residuals by Party")
+
 ```
@@
 ```{r fig-liberal-model, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.cap="Comparison of Posterior and Prior Distributions in the Liberal Model"}
-library(readr)
-library(bayesplot)
-library(here)
 

### 2024-04-14 paper/paper/paper(1).qmd
Add files via upload

--- 2024-04-13 paper/paper(1).qmd
@@
 
-@fig-income-distribution compares the distribution of socioeconomic groups before tax as represented in the census and survey datasets, with income hierarchy arrayed along the x-axis and the number of individuals in each bracket indicated on the y-axis.
-Both datasets show a similar count in the 'Upper Middle Class to Wealthy', 'Upper Class', 'Lower Middle Class to Poor' and 'Lower Class' category.
-The census dataset, indicated by the significantly taller deep red bar as opposed to the shorter orange bar of the survey dataset.
-The 'Middle Class' brackethas a higher representation in the survey data but by a less pronounced margin.
-The colors—deep red for the census and orange for the survey—aid in the visual differentiation between the two datasets, enabling a direct comparison of how each income level is represented within them, and suggest a higher census capture of lower-income brackets compared to the survey data.
+@fig-income-distribution illustrates the distribution of different socioeconomic groups before taxation, categorized by income levels.
+It contrasts the counts of individuals within each income bracket as recorded in census data (represented by the deep red bars) and survey data (represented by the orange bars).Both the census and survey data show comparable figures for the 'Upper Middle Class to Wealthy', 'Upper Class', 'Lower Middle Class to Poor', and 'Lower Class' categories.
+However, a stark difference is noted in the 'Middle Class' bracket, where the survey dataset records a noticeably higher count (shorter orange bar) in comparison to the census dataset (tall deep red bar).
+
+The choice of colors—deep red for the census and orange for the survey—facilitates a clear distinction between the two sources, allowing for an immediate visual comparison.
+The graph suggests a more substantial representation of the lower-income groups in the census data compared to the survey data.
+This might imply that the census has a broader capture or possibly that different methodologies between the two data collection approaches affect the representation of income levels.In the graph, the tallest bar corresponds to the 'Lower Middle Class to Poor' category in the census data, indicated by the deep red color.
+This suggests that the census data has captured a significantly larger number of individuals in this income bracket compared to the survey data.
+The shortest bar appears to be in the 'Upper Middle Class to Wealthy' category for the survey data, represented in orange.
+This indicates that, according to the survey data, there are fewer individuals in this highest income bracket compared to the counts of other categories within the same dataset.
 
@@
 Additionally, the package offers diagnostic tools for assessing model convergence and sensitivity to prior specifications, making it an invaluable resource for Bayesian data analysis in R.
+\newpage
 
@@
 This involved segmenting the populace according to our model's predictors and calculating the voting proportions for each party within these segments.
+\newpage
 
 ## Model Set-up
+
 We define our Bayesian logistic regression model for the probability of an individual voting for the Liberal/Conservative party as follows:
@@
 -   $\pi_i$: Probability of voting for the Liberal/Conservative party
-
 ```{=tex}
@@
 ```
+
 ## Model justification
@@
 # Discussion
+Recent research highlights that the primary concerns for Canadian voters leading up to the 2025 election include the rising cost of living, housing, healthcare, the economy, and the environment.
+These issues are pivotal to the electorate, and the political parties’ stances on them are under intense scrutiny.
+Our analysis, drawn from five different polls, suggests a marginal preference for the Conservative Party over the Liberal Party.
+This trend is echoed in Barik's 2023 article, which indicates a public perception of the Conservative Party's superior handling of these key issues.
+Thus, our working hypothesis posits that the Conservative Party holds a slender advantage in the race for the upcoming election[@Barik].
+
+For our model development, we chose predictors from census and survey data, refined through thorough research and reflecting the public's primary concerns.
+We proceeded with **binary logistic regression models**—one for each major party—to predict voter preferences based on complex social backgrounds.
+After refining the models using Akaike's Information Criteria to eliminate superfluous predictors, we established age, province, religion, education, and pre-tax income as our final variables.
+
+Post-stratification was applied to these predictors, revealing that the Conservative Party has a projected win probability of 25%, marginally outpacing the Liberal Party's 24.9%.
+These projections reinforce our initial hypothesis that the Conservative Party is the slight favorite for the 2025 election, based on our analysis of the data at hand.
+Our findings are in line with prior research, indicating that the main electoral contest will be between the Conservative and Liberal parties.
+
+## Consideration of Potential Bias
+One limitation we noted was the age of participants in the data from 2021.
+Participants under 18 then are of voting age now, in 2025.
+We opted to retain these young individuals in our dataset, hypothesizing that their burgeoning political views would mature by the election year.
+Nonetheless, the potential impact of their age on our prediction model merits further attention in subsequent studies.
+
+## Pathways for Enhanced Predictive Accuracy
+Our endeavor has shed light on the inherent complexities of electoral forecasting.
+The dynamic and deeply personal nature of voting behavior, compounded by ever-shifting political landscapes, renders the task formidable.
+For future projections, expanding the set of predictors could refine our model's accuracy, mitigating the risk of overlooking significant variables.
+
+In conclusion, our binary logistic regression approach, supplemented with post-stratification, has yielded a data-driven forecast for the 2025 Canadian Election.
+Aligning with Barik’s analysis and multiple polls, our findings suggest the Conservative Party is poised for a narrow victory over the Liberal Party, informed by an intricate blend of sociopolitical factors and current Canadian sentiment[@Barik].
 

### 2024-04-14 paper/paper(1).qmd
Add files via upload

@@
 In Quebec, the language preference aimed for 80% French-speaking and 20% English-speaking participants, with a goal of 10% French-speaking participants in both the Atlantic region and across Canada.
-Eligibility for participation required being at least 18 years old and a Canadian citizen or permanent resident[@CES].
+Eligibility for participation required being at least 18 years old and a Canadian citizen or permanent resident[@CES_2023].
 
@@
 The sampling strategy is stratified, with stratification occurring at the level of provinces and census metropolitan areas (CMA), and it relies on probability sampling techniques.
-Information is collected from a single individual aged 15 or older per household, without the use of proxy responses.[@GSS]
+Information is collected from a single individual aged 15 or older per household, without the use of proxy responses.[@GSS_2022]
 
@@
 # Discussion
+Recent research highlights that the primary concerns for Canadian voters leading up to the 2025 election include the rising cost of living, housing, healthcare, the economy, and the environment.
+These issues are pivotal to the electorate, and the political parties’ stances on them are under intense scrutiny.
+Our analysis, drawn from five different polls, suggests a marginal preference for the Conservative Party over the Liberal Party.
+This trend is echoed in Barik's 2023 article, which indicates a public perception of the Conservative Party's superior handling of these key issues.
+Thus, our working hypothesis posits that the Conservative Party holds a slender advantage in the race for the upcoming election[@Barik_2023].
+
+For our model development, we chose predictors from census and survey data, refined through thorough research and reflecting the public's primary concerns.
+We proceeded with **binary logistic regression models**—one for each major party—to predict voter preferences based on complex social backgrounds.
+After refining the models using Akaike's Information Criteria to eliminate superfluous predictors, we established age, province, religion, education, and pre-tax income as our final variables.
+
+Post-stratification was applied to these predictors, revealing that the Conservative Party has a projected win probability of 25%, marginally outpacing the Liberal Party's 24.9%.
+These projections reinforce our initial hypothesis that the Conservative Party is the slight favorite for the 2025 election, based on our analysis of the data at hand.
+Our findings are in line with prior research, indicating that the main electoral contest will be between the Conservative and Liberal parties.
+
+## Consideration of Potential Bias
+One limitation we noted was the age of participants in the data from 2021.
+Participants under 18 then are of voting age now, in 2025.
+We opted to retain these young individuals in our dataset, hypothesizing that their burgeoning political views would mature by the election year.
+Nonetheless, the potential impact of their age on our prediction model merits further attention in subsequent studies.
+
+## Pathways for Enhanced Predictive Accuracy
+Our endeavor has shed light on the inherent complexities of electoral forecasting.
+The dynamic and deeply personal nature of voting behavior, compounded by ever-shifting political landscapes, renders the task formidable.
+For future projections, expanding the set of predictors could refine our model's accuracy, mitigating the risk of overlooking significant variables.
+
+In conclusion, our binary logistic regression approach, supplemented with post-stratification, has yielded a data-driven forecast for the 2025 Canadian Election.
+Aligning with Barik’s analysis and multiple polls, our findings suggest the Conservative Party is poised for a narrow victory over the Liberal Party, informed by an intricate blend of sociopolitical factors and current Canadian sentiment[@Barik_2023].
 

### 2024-04-14 paper/paper(1).qmd
Add files via upload

@@
 The Canadian electoral process, epitomizing democratic principles, empowers citizens to elect parliamentarians who shape Parliament's composition and, consequently, the government formation.
-In the recent 2021 federal election, Justin Trudeau's Liberal Party secured a majority in the 44th Parliament.
+In the recent 2021 federal election, Justin Trudeau's Liberal Party secured a majority in the 44th Parliament[@Nakhaie_2006].
 Voters' primary concerns include the cost of living, healthcare, climate change, post-pandemic recovery, and immigration, with dissatisfaction towards Trudeau's government prevalent.
-Trudeau's popularity lags behind UK's Poilievre.
+Trudeau's popularity lags behind UK's Poilievre[@Nakhaie_2006].
 The government's ambitious immigration plan aims to admit 500,000 migrants annually by 2025, albeit facing a backlog.
-The Conservative Party, with a focus on economic prosperity, emphasizes attracting highly skilled immigrants while addressing concerns like living costs and housing issues[@Canada].
+The Conservative Party, with a focus on economic prosperity, emphasizes attracting highly skilled immigrants while addressing concerns like living costs and housing issues[@Elections_2023].
 
@@
 If a candidate obtains 50% of the vote, they win.
-If not, the candidate with the fewest votes is eliminated[@Canada].
+If not, the candidate with the fewest votes is eliminated[@Elections_2023].
 Then, votes from supporters of the eliminated candidate are redistributed to their second-choice candidate.
 This iterative redistribution continues until one candidate achieves 50% of the vote.
-Hence, our objective is to forecast the election probabilities for the Conservative and Liberal parties and compare which is higher[@Elections].
+Hence, our objective is to forecast the election probabilities for the Conservative and Liberal parties and compare which is higher[@Elections_2023].
 

### 2024-04-15 paper/paper(1).qmd
Add files via upload

@@
 ### Data Summary Measures
-
 ```{r}
-#| label: tbl-data-summary
+#| label: tbl-data-summary-numeric
 #| tbl-cap: Summary of Numerical Variables Across Census and Survey Data
@@
 knitr::kable(numeric_summary_df)
+
 ```
@@
 Table2: Summary the residuals for Conservative Party:
-```{r echo=FALSE, warning=FALSE}
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: tbl-data-summary
+#| tbl-cap: Summary of Numerical Variables Across Census and Survey Data
+#| echo: false
 
@@
 
-# Create a table of the data
 kable(table_summary, caption = "Summary of Residuals by Party")
@@
 ```
+@tbl-data-summary
 
-Table3: Summary the coefficient for Liberal Party:
-
-```{r echo=FALSE, warning=FALSE}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: tbl-coef-summary-liberal
+#| tbl-cap: Coefficients of the Liberal Model
+#| echo: false
 
 liberal_coefs <- coef(liberal_model)
-conservative_coefs <- coef(conservative_model)
-
 liberal_coefs_df <- data.frame(Estimate = liberal_coefs, row.names = NULL)
-conservative_coefs_df <- data.frame(Estimate = conservative_coefs, row.names = NULL)
-
 liberal_coefs_df$Term <- names(liberal_coefs)
-conservative_coefs_df$Term <- names(conservative_coefs)
-
 liberal_coefs_df <- liberal_coefs_df[, c("Term", "Estimate")]
-conservative_coefs_df <- conservative_coefs_df[, c("Term", "Estimate")]
-
-knitr::kable(liberal_coefs_df, caption = "Coefficients of the Liberal Model", row.names = FALSE)
-knitr::kable(conservative_coefs_df, caption = "Coefficients of the Conservative Model", row.names = FALSE)
+knitr::kable(liberal_coefs_df, row.names = FALSE)
 
 ```
+@tbl-coef-summary-liberal
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#| label: tbl-coef-summary-conservative
+#| tbl-cap: Coefficients of the Conservative Model
+#| echo: false
+
+conservative_coefs <- coef(conservative_model)
+conservative_coefs_df <- data.frame(Estimate = conservative_coefs, row.names = NULL)
+conservative_coefs_df$Term <- names(conservative_coefs)
+conservative_coefs_df <- conservative_coefs_df[, c("Term", "Estimate")]
+knitr::kable(conservative_coefs_df, row.names = FALSE)
+
+```
+
+@tbl-coef-summary-conservative
 

### 2024-04-17 script/04_model.R
Add files via upload

@@ -12,48 +12,29 @@ library(dplyr)
 library(readr)
 library(here)
 
-set.seed(302)
+m_lib <- glm(vote_liberal ~ age+sex+province+education+religion+income_before_tax,
+             data=cleaned_survey_data, family = "binomial")
+summary(m_lib)
 
-# Read in the cleaned survey data
-survey_data <- read_csv(here("data", "analysis_data", "cleaned_survey_data.csv"))
 
-# Convert the necessary columns to factors
-survey_data <- survey_data %>%
-  mutate(
-    province = as.factor(province),
-    sex = as.factor(sex),
-    education = as.factor(education),
-    religion = as.factor(religion),
-    income_before_tax = as.factor(income_before_tax)
-  )
+step_lib = stepAIC(m_lib, direction = "both", k = 2)
 
-# Set up the priors
-prior_intercept <- normal(0, 2.5)
-prior_covariates <- normal(0, scale = 1)  # The scale can be treated as 1/sqrt(lambda) for Exponential(lambda)
 
-# Define the model using stan_glm
-liberal_model <- stan_glm(
-  vote_liberal ~ age + sex + province + education + religion + income_before_tax,
-  data = survey_data, 
-  family = binomial(link = "logit"),
-  prior_intercept = prior_intercept,
-  prior = prior_covariates,
-  prior_aux = exponential(1),
-  chains = 4,
-  iter = 2000
-)
 
-conservative_model <- stan_glm(
-  vote_conservative ~ age + sex + province + education + religion + income_before_tax,
-  data = survey_data, 
-  family = binomial(link = "logit"),
-  prior_intercept = prior_intercept,
-  prior = prior_covariates,
-  prior_aux = exponential(1),
-  chains = 4,
-  iter = 2000
-)
+m_cons <- glm(vote_conservative ~ age+sex+province+education+religion+income_before_tax,
+              data=cleaned_survey_data, family = "binomial")
 
-# Save the models
-saveRDS(liberal_model, file = here("models", "liberal_model.rds"))
-saveRDS(conservative_model, file = here("models", "conservative_model.rds"))
+step_cons = stepAIC(m_cons, direction = "both", k = 2)
+
+saveRDS(m_lib, file = here("models", "liberal_model.rds"))
+
+
+saveRDS(m_cons, file = here("models", "conservative_model.rds"))
+
+
+
+
+
+
+
+

### 2024-04-17 paper/paper(1).qmd
Add files via upload

@@
 
-@tbl-data-summary summaries the census and survey data reveals age distributions with the census data capturing a narrower age range (15 to 80 years, with a median of 54) compared to the broader age span in the survey data (18 to 97 years, with a median of 53).
+@tbl-data-summary-numeric summaries the census and survey data reveals age distributions with the census data capturing a narrower age range (15 to 80 years, with a median of 54) compared to the broader age span in the survey data (18 to 97 years, with a median of 53).
 The average ages for the census and survey populations are 52.18 and 51.3 years, respectively.
@@
 
-```{r echo=FALSE}
+```{r , echo=FALSE, message=FALSE, warning=FALSE}
 liberal_model <- readRDS(here("models", "liberal_model.rds"))
@@
 
-Table2: Summary the residuals for Conservative Party:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#| label: tbl-data-summary
-#| tbl-cap: Summary of Numerical Variables Across Census and Survey Data
+```{r, echo=FALSE, message=FALSE, warning = FALSE}
+#| label: tbl-coef-summary-conservative
+#| tbl-cap: Coefficients of the conservative Model
 #| echo: false
 
-liberal_residuals <- posterior_predict(liberal_model) - cleaned_survey_data$vote_liberal
-conservative_residuals <- posterior_predict(conservative_model) - cleaned_survey_data$vote_conservative
+install.packages("MASS")
+# Load the necessary library
+library(MASS)
+library(broom)
+library(knitr)
 
-table_summary <- data.frame(
-  Party = c("Liberal", "Conservative"),
-  Mean_Residual = c(mean(liberal_residuals, na.rm = TRUE), mean(conservative_residuals, na.rm = TRUE)),
-  Median_Residual = c(median(liberal_residuals, na.rm = TRUE), median(conservative_residuals, na.rm = TRUE)),
-  SD_Residual = c(sd(liberal_residuals, na.rm = TRUE), sd(conservative_residuals, na.rm = TRUE)),
-  IQR_Residual = c(IQR(liberal_residuals, na.rm = TRUE), IQR(conservative_residuals, na.rm = TRUE))
-)
+# Fit the initial linear model
+initial_model <- lm(vote_conservative ~ age + sex + province + education + religion + income_before_tax, data=cleaned_survey_data)
 
-kable(table_summary, caption = "Summary of Residuals by Party")
+# Perform stepwise model selection using stepAIC
+step_cons <- stepAIC(initial_model, direction="both", trace = FALSE)
+
+# Use broom::tidy to get a tidy data frame of the model summary with confidence intervals
+tidy_cons <- broom::tidy(step_cons, conf.int = TRUE)
+
+# Select the columns you want for the table, excluding statistic and p-value
+tidy_cons_selected <- tidy_cons[, c("term", "estimate", "std.error", "conf.low", "conf.high")]
+
+# Create the table with knitr::kable()
+kable_output <- knitr::kable(tidy_cons_selected, format = "html", caption = "Model Summary for Conservative Vote Prediction with Confidence Intervals")
+
+# Display the table output
+kable_output
 
 ```
-@tbl-data-summary
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
+```{r, echo=FALSE, message=FALSE, warning = FALSE}
 #| label: tbl-coef-summary-liberal
@@
 
-liberal_coefs <- coef(liberal_model)
-liberal_coefs_df <- data.frame(Estimate = liberal_coefs, row.names = NULL)
-liberal_coefs_df$Term <- names(liberal_coefs)
-liberal_coefs_df <- liberal_coefs_df[, c("Term", "Estimate")]
-knitr::kable(liberal_coefs_df, row.names = FALSE)
+# Assuming 'vote_liberal' is the column in your 'cleaned_survey_data' that represents voting for liberal
+initial_model_lib <- lm(vote_liberal ~ age + sex + province + education + religion + income_before_tax, data=cleaned_survey_data)
+step_lib <- stepAIC(initial_model_lib, direction="both", trace = FALSE)
 
-```
-@tbl-coef-summary-liberal
+tidy_lib <- broom::tidy(step_lib, conf.int = TRUE)
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#| label: tbl-coef-summary-conservative
-#| tbl-cap: Coefficients of the Conservative Model
-#| echo: false
+tidy_lib_selected <- tidy_lib[, c("term", "estimate", "std.error", "conf.low", "conf.high")]
 
-conservative_coefs <- coef(conservative_model)
-conservative_coefs_df <- data.frame(Estimate = conservative_coefs, row.names = NULL)
-conservative_coefs_df$Term <- names(conservative_coefs)
-conservative_coefs_df <- conservative_coefs_df[, c("Term", "Estimate")]
-knitr::kable(conservative_coefs_df, row.names = FALSE)
+kable_output_lib <- knitr::kable(tidy_lib_selected, format = "html", caption = "Model Summary for Liberal Vote Prediction with Confidence Intervals")
+kable_output_lib
 
@@
 
+@tbl-coef-summary-liberal
+
+`
+
 @tbl-coef-summary-conservative
+
+@tbl-ypshat-summary
+```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+if (!require(MASS)) {
+    install.packages("MASS")
+    library(MASS)
+} else {
+    library(MASS)
+}
+
+m_lib <- glm(vote_liberal ~ age + sex + province + education + religion + income_before_tax,
+             data = cleaned_survey_data, family = "binomial")
+
+step_lib <- stepAIC(m_lib, direction = "both", trace = FALSE)
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, include = FALSE}
+
+m_lib <- glm(vote_liberal ~ age+sex+province+education+religion+income_before_tax,
+          data=cleaned_survey_data, family = "binomial")
+
+step_lib = stepAIC(m_lib, direction = "both", k = 2)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, include = FALSE}
+m_cons <- glm(vote_conservative ~ age+sex+province+education+religion+income_before_tax,
+          data=cleaned_survey_data, family = "binomial")
+
+step_cons <- stepAIC(m_cons, direction = "both", k = 2)
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, include = FALSE}
+step_cons <- glm(vote_conservative ~ age+province+education+religion+income_before_tax,
+          data=cleaned_survey_data, family = "binomial")
+step_cons_counts <- cleaned_survey_data %>%
+  group_by(age, province, education, religion, income_before_tax)%>%
+  summarise(N_j=n(), .groups = 'keep')
+
+step_cons_counts$estimate <- 
+  step_cons %>%
+  predict(newdata = step_cons_counts, type = "response")
+
+cons_aic <- step_cons_counts %>%
+  mutate(predict_prob_cons = estimate*N_j) %>% 
+  ungroup() %>%
+  summarise(yPS_cons_aic = sum(predict_prob_cons)/sum(N_j))
+
+cons_counts <- cleaned_survey_data%>%
+  group_by(age, sex, province, education, religion, income_before_tax)%>%
+  summarise(N_j=n(), .groups = 'keep')
+
+cons_counts$estimate <- 
+  m_cons %>%
+  predict(newdata = cons_counts, type = "response")
+
+cons_estimate <- cons_counts %>%
+  mutate(predict_prob_cons = estimate*N_j) %>% 
+  ungroup() %>%
+  summarise(yPS_cons = sum(predict_prob_cons)/sum(N_j))
+
+step_lib <- glm(vote_liberal ~ age+province+education+religion+income_before_tax,
+          data=cleaned_survey_data, family = "binomial")
+step_lib_counts <- cleaned_survey_data %>%
+  group_by(age, province, education, religion, income_before_tax)%>%
+  summarise(N_j=n(), .groups = 'keep')
+
+step_lib_counts$estimate <- 
+  step_lib %>%
+  predict(newdata = step_lib_counts, type = "response")
+
+lib_aic <- step_lib_counts %>%
+  mutate(predict_prob_lib = estimate*N_j) %>% 
+  ungroup() %>%
+  summarise(yPS_lib_aic = sum(predict_prob_lib)/sum(N_j))
+
+lib_counts <- cleaned_survey_data %>%
+  group_by(age, sex, province, education, religion, income_before_tax)%>%
+  summarise(N_j=n(), .groups = 'keep')
+
+lib_counts$estimate <- 
+  m_lib %>%
+  predict(newdata = lib_counts, type = "response")
+
+lib_estimate <- lib_counts %>%
+  mutate(predict_prob_lib = estimate*N_j) %>% 
+  ungroup() %>%
+  summarise(yPS_lib = sum(predict_prob_lib)/sum(N_j))
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
+Party_Name <- c("Conservative", "Liberal")
+yPS_primary <- c(cons_estimate,lib_estimate)
+yPS_AIC <- c(cons_aic ,lib_aic)
+
+knitr::kable(tibble(Party_Name, yPS_primary, yPS_AIC), caption = "The Hat of yPS For Each Party, Between Primary Model and Final Model")
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+library(ggplot2)
+library(broom)
+
+# Assuming you have already fitted a model `step_lib`
+# and `step_lib` is an object of class 'glm' or similar
+tidy_lib <- broom::tidy(step_lib, conf.int = TRUE, exponentiate = FALSE)  # Set exponentiate=TRUE for logistic regression
+
+# Forest plot of coefficient estimates
+ggplot(tidy_lib, aes(x = estimate, y = reorder(term, estimate))) +
+  geom_point() +
+  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
+  geom_vline(xintercept = 1, linetype = "dotted", color = "red") +  # Use 0 if exponentiate=FALSE
+  labs(x = "Estimate", y = "Coefficient", title = "Coefficient Estimates for Liberal Party") +
+  theme_minimal()
+# Assuming your `cleaned_survey_data` has a column `province` and `vote_liberal`
+proportions_by_province <- cleaned_survey_data %>%
+  group_by(province) %>%
+  summarise(estimate = mean(vote_liberal)) %>%
+  mutate(province = factor(province, levels = rev(unique(province))))  # Ordering the provinces
+
+# Horizontal bar plot of estimated proportions by province
+ggplot(proportions_by_province, aes(x = province, y = estimate)) +
+  geom_col() +
+  coord_flip() +  # Flipping the coordinates for horizontal bars
+  labs(y = "Estimated Proportion", x = "Province", title = "Estimated Proportion of Voting for Liberal by Province") +
+  theme_minimal()
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+cleaned_survey_data <- read_parquet(here("data", "analysis_data","cleaned_survey_data.parquet"))
+
+cleaned_survey_data$vote_liberal <- ifelse(cleaned_survey_data$vote_liberal == "Yes", 1, 0)
+
+lib_props <- cleaned_survey_data %>%
+
+  group_by(age, sex, province, education, religion, income_before_tax) %>% 
+  summarise(n = n(), .groups ='drop') %>%
+
+  group_by(province) %>% 
+  mutate(prop = n/sum(n))
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+library(ggplot2)
+library(dplyr)
+# Assuming 'cleaned_survey_data' is your data frame and it's already loaded in R
+# First, check that all required variables are present in 'cleaned_survey_data'
+required_vars <- c("vote_conservative", "age", "sex", "province", "education", "religion", "income_before_tax")
+missing_vars <- setdiff(required_vars, names(cleaned_survey_data))
+
+if(length(missing_vars) > 0) {
+  stop(paste("The following required variables are missing in the data frame:", paste(missing_vars, collapse=", ")))
+}
+
+# If all variables are present, fit the linear model
+model <- lm(vote_conservative ~ age + sex + province + education + religion + income_before_tax, data=cleaned_survey_data)
+
+# Use broom::tidy to get a tidy data frame of the model summary with confidence intervals
+library(broom)
+model_summary <- broom::tidy(model, conf.int = TRUE)
+
+ggplot(model_summary, aes(x = estimate, y = reorder(term, estimate))) +
+  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
+  labs(x = "Estimate", y = "Coefficient", title = "Coefficient Estimates") +
+  theme_minimal()
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+
+library(ggplot2)
+library(dplyr)
+
+# Assuming 'your_data' is your dataframe and it contains the variables 'province' and 'vote_conservative'
+# where 'vote_conservative' is a binary (0/1) indicating whether a vote for conservative was cast.
+
+# Calculate proportions and confidence intervals by province
+conservative_votes_by_province <- cleaned_survey_data %>%
+  group_by(province) %>%
+  summarise(
+    proportion = mean(vote_conservative, na.rm = TRUE),
+    lower = proportion - qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
+    upper = proportion + qnorm(0.975) * sqrt(proportion * (1 - proportion) / n())
+  )
+
+# Create the plot
+ggplot(conservative_votes_by_province, aes(x = reorder(province, -proportion), y = proportion)) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
+  coord_flip() +  # Flip the axes to have provinces on the y-axis
+  labs(x = "Proportion", y = "Province", title = "Estimated Proportion of Voting for Conservative by Province") +
+  theme_minimal()
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+library(ggplot2)
+library(dplyr)
+
+conservative_votes_by_education <- cleaned_survey_data %>%
+  group_by(education) %>%
+  summarise(
+    proportion = mean(vote_conservative, na.rm = TRUE),
+    lower = proportion - qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
+    upper = proportion + qnorm(0.975) * sqrt(proportion * (1 - proportion) / n())
+  ) %>%
+  arrange(desc(proportion))  
+ggplot(conservative_votes_by_education, aes(x = reorder(education, proportion), y = proportion)) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
+  coord_flip() +  
+  labs(x = "Proportion", y = "Education", title = "Proportion of Votes for Conservative by Education Level") +
+  theme_minimal()
+
+```
 
@@
 
-```{r fig-liberal-model-1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior Predictive Check: Observed vs. Simulated Vote Counts in the Liberal Model"}
-library(bayesplot)
-
-liberal_model_plot <- pp_check(liberal_model, type = "hist") +
-  theme(plot.title = element_text(size = 10))
-
-print(liberal_model_plot)
-```
-
-@fig-liberal-model-1 illustrates a posterior predictive check for the liberal model, comparing observed vote counts with those generated by the model's simulations.
-The dark solid line represents the observed data, while the lighter blue lines represent simulated vote counts from the posterior distribution.
-The close tracking of the simulated lines to the observed line suggests that the model can effectively replicate the patterns seen in the real vote counts.
-This indicates a good model fit, as the simulations encompass the range of observed data, providing confidence in the model's predictions.
-The alignment of the simulations with the observed data points to the adequacy of the model's structure and the priors in capturing the underlying trends of the voting behavior it aims to represent.
-The graph also visualizes the variance in the simulations, reflecting the model's probabilistic nature and the inherent uncertainty in predicting complex phenomena such as voting behavior.
-
-Histogram of posterior predictive distributions from the liberal model.
-This plot compares the observed counts of the number of votes for the Liberal party (indicated by the dark line) with the simulated counts from the posterior predictive distribution (shown as histograms).
-The overlap between the observed counts and the predictive distribution suggests how well the model captures the data.
-Areas where the observed counts fall outside the bulk of the simulated distributions may indicate model misfit.
 \newpage
 
-```{r fig-conservative-model, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Posterior Predictive Check: Observed vs. Simulated Vote Counts in the Conservative Model"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=8, fig.height=6}
 library(bayesplot)
-
-conservative_model_plot <- pp_check(conservative_model, type = "hist") + 
-  theme(plot.title = element_text(size = 14)) 
-print(conservative_model_plot)
-
-```
-
-@fig-conservative-model performs a posterior predictive check for a conservative model by overlaying observed vote counts against simulated data derived from the model's posterior distribution.
-The observed data is denoted by a solid line, while the simulations from the posterior are indicated by lighter lines.
-The congruence between these two sets of lines—where the simulated data traces the shape and trend of the observed data closely—suggests that the model has a high level of accuracy in reflecting the observed outcomes.
-This indicates a successful fit of the model to the data, affirming the appropriateness of the selected priors and the model's structure.
-The spread of the lighter lines around the darker one provides insight into the inherent uncertainty of the model's predictions, which is an expected characteristic of predictive modelling in complex, real-world situations.
-
-\newpage
-
-```{r fig-liberal-model, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.cap="Comparison of Posterior and Prior Distributions in the Liberal Model"}
-
-survey_data <- read_csv(here("data", "analysis_data", "cleaned_survey_data.csv"))
+library(rstanarm)
 
@@
 prior_intercept <- normal(0, 2.5)
+
+liberal_model <- stan_glm(
+  vote_liberal ~ age + sex + province + education + religion + income_before_tax,
+  data = cleaned_survey_data,
+  family = "binomial",
+  prior = prior_covariates,
+  prior_intercept = prior_intercept,
+  chains = 4,
+  iter = 2000
+)
 
@@
 
-print(pp_plot)
+pp_plot
 
@@
 
-@fig-liberal-model portrays the posterior and prior distributions for parameters in a Bayesian liberal model, with a stark divergence in the intercept suggesting significant data-driven adjustments from the model's baseline estimation.
-Parameters representing demographic and geographical factors are plotted as colored dots along an axis, indicating median values and the extent of uncertainty.
-While the priors and posteriors largely overlap, indicating consistent estimates for many parameters, the intercept's noticeable shift underscores the data's impactful role in refining the model, particularly highlighting the updated understanding of the model's fundamental starting point.
-
-\newpage
-
-```{r fig-conservative-posterior, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.cap="Comparison of Posterior and Prior Distributions in the Conservative Model"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=8, fig.height=6}
 library(bayesplot)
+library(rstanarm)
 
@@
 
-pp_plot <- posterior_vs_prior(conservative_model) +
+conservative_model <- stan_glm(
+  vote_conservative ~ age + sex + province + education + religion + income_before_tax,
+  data = cleaned_survey_data,
+  family = "binomial",
+  prior = prior_covariates,
+  prior_intercept = prior_intercept,
+  chains = 4,
+  iter = 2000
+)
+
+# Generate the posterior vs. prior plot for the conservative model
+pp_plot_conservative <- posterior_vs_prior(conservative_model) +
   theme_minimal() +
@@
 
-print(pp_plot)
+pp_plot_conservative
 
@@
 
-@fig-conservative-posterior presents a side-by-side comparison of the median and spread of prior and posterior distributions for the parameters in a Bayesian model, applied to the Conservative context.
-Key findings include the posterior distribution of the "age" parameter mirroring its prior, which validates the initial assumption about its influence.
-In contrast, the intercept and sigma parameters show slight shifts, indicating the data's role in refining these estimates.
-The placement of medians for other parameters—like sex, religion, and province—demonstrates the data's impact in confirming or adjusting prior beliefs.
-Overall, the alignment of posterior distributions with priors confirms the model's accuracy and the informative value of the data in capturing the effects on the dependent variable, suggesting a robust model fit.
+@fig-liberal-model
+\newpage
 
+```{r}
+#Cons CI plot
+cons_predictions <- predict(step_cons, newdata = step_cons_counts, type = "response", interval = "confidence")
+cons_CI <- data.frame(cons_predictions)
+
+cons_CI$lwr <- cons_CI$cons_predictions - 1.96 * sqrt(cons_CI$cons_predictions * (1 - cons_CI$cons_predictions) / nrow(cons_CI))
+cons_CI$upr <- cons_CI$cons_predictions + 1.96 * sqrt(cons_CI$cons_predictions * (1 - cons_CI$cons_predictions) / nrow(cons_CI))
+
+cons_CI$observation <- 1:nrow(cons_CI)
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+# Make sure 'sex' is part of the group_by when creating step_lib_counts
+step_lib_counts <- cleaned_survey_data %>%
+  group_by(age, sex, province, education, religion, income_before_tax) %>%
+  summarise(N_j=n(), .groups = 'drop')  # Use .groups = 'drop' to remove the grouping
+
+# Now the step_lib_counts has a 'sex' column that matches with the model's predictors
+# You can proceed with prediction
+lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response")
+
+# After prediction, if you want to calculate confidence intervals manually, make sure
+# the calculations are vectorized and account for the grouped structure of your data
+
+# Assuming that N_j is the count of observations for each group in your summarized dataset
+lib_CI <- data.frame(lib_predictions)
+lib_CI$lwr <- lib_CI$lib_predictions - 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+lib_CI$upr <- lib_CI$lib_predictions + 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+
+# Here we don't need to create an 'observation' column because the plot will use grouped data
+# If you do want an 'observation' identifier, ensure it's a sequence within each group
+lib_CI$observation <- seq_len(nrow(lib_CI))
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response", interval = "confidence")
+lib_CI <- data.frame(lib_predictions)
+
+lib_CI$lwr <- lib_CI$lib_predictions - 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / nrow(lib_CI))
+lib_CI$upr <- lib_CI$lib_predictions + 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / nrow(lib_CI))
+
+lib_CI$observation <- 1:nrow(lib_CI)
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
+ggplot(cons_CI, aes(x = cons_predictions)) +
+  geom_density(alpha = 0.5, fill = "blue") +
+  labs(x = "Predicted Probability", y = "Density", title = "Plot.9 The Density Plot for Predicted Probabilities for Conservative")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
+ggplot(lib_CI, aes(x = lib_predictions, fill = "Liberal")) +
+  geom_density(alpha = 0.5, fill = "green") +
+  labs(x = "Predicted Probability", y = "Density", title = "Plot.10 The Density Plot for Predicted Probabilities for Liberal")
+```
+
+@fig-conservative-posterior 
 \newpage

### 2024-04-17 paper/paper(1).qmd
Add files via upload

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, include = FALSE}
+
 step_cons <- glm(vote_conservative ~ age+province+education+religion+income_before_tax,
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-
+library(dplyr)
 Party_Name <- c("Conservative", "Liberal")
@@
 library(ggplot2)
+library(dplyr)
 library(broom)
 
-# Assuming you have already fitted a model `step_lib`
-# and `step_lib` is an object of class 'glm' or similar
-tidy_lib <- broom::tidy(step_lib, conf.int = TRUE, exponentiate = FALSE)  # Set exponentiate=TRUE for logistic regression
-
-# Forest plot of coefficient estimates
-ggplot(tidy_lib, aes(x = estimate, y = reorder(term, estimate))) +
-  geom_point() +
-  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
-  geom_vline(xintercept = 1, linetype = "dotted", color = "red") +  # Use 0 if exponentiate=FALSE
-  labs(x = "Estimate", y = "Coefficient", title = "Coefficient Estimates for Liberal Party") +
-  theme_minimal()
-# Assuming your `cleaned_survey_data` has a column `province` and `vote_liberal`
-proportions_by_province <- cleaned_survey_data %>%
-  group_by(province) %>%
-  summarise(estimate = mean(vote_liberal)) %>%
-  mutate(province = factor(province, levels = rev(unique(province))))  # Ordering the provinces
-
-# Horizontal bar plot of estimated proportions by province
-ggplot(proportions_by_province, aes(x = province, y = estimate)) +
-  geom_col() +
-  coord_flip() +  # Flipping the coordinates for horizontal bars
-  labs(y = "Estimated Proportion", x = "Province", title = "Estimated Proportion of Voting for Liberal by Province") +
-  theme_minimal()
-
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-cleaned_survey_data <- read_parquet(here("data", "analysis_data","cleaned_survey_data.parquet"))
-
-cleaned_survey_data$vote_liberal <- ifelse(cleaned_survey_data$vote_liberal == "Yes", 1, 0)
-
-lib_props <- cleaned_survey_data %>%
-
-  group_by(age, sex, province, education, religion, income_before_tax) %>% 
-  summarise(n = n(), .groups ='drop') %>%
-
-  group_by(province) %>% 
-  mutate(prop = n/sum(n))
-
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-library(ggplot2)
-library(dplyr)
-# Assuming 'cleaned_survey_data' is your data frame and it's already loaded in R
-# First, check that all required variables are present in 'cleaned_survey_data'
-required_vars <- c("vote_conservative", "age", "sex", "province", "education", "religion", "income_before_tax")
+required_vars <- c("vote_liberal", "age", "sex", "province", "education", "religion", "income_before_tax")
 missing_vars <- setdiff(required_vars, names(cleaned_survey_data))
@@
 }
+model_lib <- lm(vote_liberal ~ age + sex + province + education + religion + income_before_tax, data=cleaned_survey_data)
+model_summary_lib <- broom::tidy(model_lib, conf.int = TRUE)
 
-# If all variables are present, fit the linear model
-model <- lm(vote_conservative ~ age + sex + province + education + religion + income_before_tax, data=cleaned_survey_data)
-
-# Use broom::tidy to get a tidy data frame of the model summary with confidence intervals
-library(broom)
-model_summary <- broom::tidy(model, conf.int = TRUE)
-
-ggplot(model_summary, aes(x = estimate, y = reorder(term, estimate))) +
+ggplot(model_summary_lib, aes(x = estimate, y = reorder(term, estimate))) +
   geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
   geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
-  labs(x = "Estimate", y = "Coefficient", title = "Coefficient Estimates") +
+  labs(x = "Estimate", y = "Coefficient", title = "Coefficient Estimates for Liberal Vote Prediction") +
   theme_minimal()
@@
 
+@
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-
 library(ggplot2)
@@
 
-# Assuming 'your_data' is your dataframe and it contains the variables 'province' and 'vote_conservative'
-# where 'vote_conservative' is a binary (0/1) indicating whether a vote for conservative was cast.
+# Assuming 'cleaned_survey_data' contains 'province' and 'vote_liberal',
+# where 'vote_liberal' is a binary (0/1) indicating whether a vote for liberal was cast.
 
-# Calculate proportions and confidence intervals by province
-conservative_votes_by_province <- cleaned_survey_data %>%
+# Calculate proportions and confidence intervals by province for the liberal party
+liberal_votes_by_province <- cleaned_survey_data %>%
   group_by(province) %>%
   summarise(
-    proportion = mean(vote_conservative, na.rm = TRUE),
+    proportion = mean(vote_liberal, na.rm = TRUE),
     lower = proportion - qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
-    upper = proportion + qnorm(0.975) * sqrt(proportion * (1 - proportion) / n())
-  )
+    upper = proportion + qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
+    .groups = 'drop'  # Drop grouping for further manipulation if needed
+  ) %>%
+  ungroup()  # Ensure we remove the grouping for the ggplot
 
-# Create the plot
-ggplot(conservative_votes_by_province, aes(x = reorder(province, -proportion), y = proportion)) +
+# Create the plot for the liberal party
+ggplot(liberal_votes_by_province, aes(x = reorder(province, -proportion), y = proportion)) +
   geom_point() +
@@
   coord_flip() +  # Flip the axes to have provinces on the y-axis
-  labs(x = "Proportion", y = "Province", title = "Estimated Proportion of Voting for Conservative by Province") +
+  labs(x = "Proportion", y = "Province", title = "Estimated Proportion of Voting for Liberal by Province") +
   theme_minimal()
@@
 
-conservative_votes_by_education <- cleaned_survey_data %>%
+# Assuming 'cleaned_survey_data' is your dataframe and it contains the variables 'education' and 'vote_liberal'
+# where 'vote_liberal' is a binary (0/1) indicating whether a vote for liberal was cast.
+
+liberal_votes_by_education <- cleaned_survey_data %>%
   group_by(education) %>%
   summarise(
-    proportion = mean(vote_conservative, na.rm = TRUE),
+    proportion = mean(vote_liberal, na.rm = TRUE),
     lower = proportion - qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
-    upper = proportion + qnorm(0.975) * sqrt(proportion * (1 - proportion) / n())
+    upper = proportion + qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
+    .groups = 'drop'  # This will automatically ungroup the data (requires dplyr version 1.0.0 or higher)
   ) %>%
   arrange(desc(proportion))
-ggplot(conservative_votes_by_education, aes(x = reorder(education, proportion), y = proportion)) +
+
+ggplot(liberal_votes_by_education, aes(x = reorder(education, proportion), y = proportion)) +
   geom_point() +
   geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
-  coord_flip() +  
-  labs(x = "Proportion", y = "Education", title = "Proportion of Votes for Conservative by Education Level") +
+  coord_flip() +  # Flip the axes to have education levels on the y-axis
+  labs(x = "Proportion", y = "Education", title = "Proportion of Votes for Liberal by Education Level") +
   theme_minimal()

### 2024-04-18 paper/paper(1).qmd
Add files via upload

@@
 title-block-banner: true
-abstract: "ojjojojojljk,mkmk."
+abstract: "In our study, we use binary logistic regression to analyze voter preferences for Canada's Conservative and Liberal parties based on demographic and socioeconomic factors, adjusting the models with the AIC for optimal predictor selection.
+The Canadian electoral system elects parliamentarians through a multi-step process where, unless a candidate achieves an outright majority, votes are redistributed from the lowest-ranking candidates until one secures 50%.
+The Liberal Party plans to increase its refugee quota to 15% of all immigrants and admit 500,000 migrants annually by 2025.
+The Conservative Party emphasizes economic growth and attracting skilled immigrants.
+Our hypothesis predicts a likely Conservative victory in the 2025 elections, with the Liberals closely behind, based on trends and electoral mechanics.
+This analysis uses post-stratification to enhance the representativeness and accuracy of our predictions."
 thanks: "Code and data supporting this analysis are available at: https://github.com/CSCmaster/Final-Project"
@@
 ## Hypothesis
-
+To enhance control and prevention of illegal immigration, the Liberal Party has suggested modifications to the Immigration and Refugee Protection Act.
+They propose establishing an annual refugee quota of 250, specifically aimed at supporting human rights defenders, journalists, and humanitarian workers seeking safety and resettlement in Canada.
+Looking ahead, the Liberal Party intends to incrementally increase this refugee quota, aiming for refugees to comprise 15% of all immigrants.
+Conversely, the share of economic immigrants is planned to decrease to 58%, while the family reunification immigrant ratio will remain constant.
+These proportions are expected to be maintained over the next two years.
+Moreover, the Canadian national government recently unveiled an ambitious plan to admit 500,000 migrants annually by 2025, looking for nearly 1.5 million newcomers in Canada within the next three years (Canada's Immigration Levels Plan 2024-2026).
+Historically, the Liberal government's immigration strategy tends to be more permissive, offering broader entry routes compared to that of the Conservative Party[@Nakhaie_2006].
 Based on our analysis of historical trends, governmental policies, and electoral procedures, our hypothesis aligns with the prevailing expectation that the Conservatives will emerge as the likely winners in the 2025 election.
-**We anticipate that the Conservatives will likely secure the highest number of votes, with the Liberals expected to closely follow in second place.** Our research indicates that the vote-counting process in Canada significantly influences the outcome, as voters do not directly elect a specific prime minister candidate.
+**We anticipate that the Liberals will likely secure the highest number of votes, with the Conservatives expected to closely follow in second place.** Our research indicates that the vote-counting process in Canada significantly influences the outcome, as voters do not directly elect a specific prime minister candidate.
 Initially, all votes are tallied based on first preferences.
@@
 
-In this paper, I used binary logistic regression models to forecast the likelihood of individuals affiliating with the Conservative or Liberal parties.
-Binary logistic regression is a statistical technique tailored for predicting binary outcomes, where the variable under consideration has two possible results.
-In our study, these outcomes represent the probability of individuals aligning with each of the two parties.
-Each party's likelihood will be predicted through separate logistic regression models, with the response variables indicating whether individuals vote for the corresponding party or not.
+In this paper, I used binary logistic regression models to forecast the likelihood of individuals affiliating with the Conservative or Liberal parties.Binary logistic regression is a statistical technique tailored for predicting binary outcomes, where the variable under consideration has two possible results.
+In our study, these outcomes represent the probability of individuals aligning with each of the two parties.Each party's likelihood will be predicted through separate logistic regression models, with the response variables indicating whether individuals vote for the corresponding party or not.
 The predictors used in these models include age, province, education, religion, and income before tax.
@@
 Post-stratification helps refine precision estimates by ensuring that the sample is more representative of the entire population.
+We utilize this technique to predict the probability of voter shares for the Liberal or Conservative parties in the upcoming election.
 
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=8, fig.height=6}
-library(bayesplot)
-library(rstanarm)
 
@@
 
-# Generate the posterior vs. prior plot for the conservative model
 pp_plot_conservative <- posterior_vs_prior(conservative_model) +
@@
 
-```{r}
-#Cons CI plot
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+
 cons_predictions <- predict(step_cons, newdata = step_cons_counts, type = "response", interval = "confidence")
@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-# Make sure 'sex' is part of the group_by when creating step_lib_counts
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+
 step_lib_counts <- cleaned_survey_data %>%
@@
 
-# Now the step_lib_counts has a 'sex' column that matches with the model's predictors
-# You can proceed with prediction
 lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response")
-
-# After prediction, if you want to calculate confidence intervals manually, make sure
-# the calculations are vectorized and account for the grouped structure of your data
-
-# Assuming that N_j is the count of observations for each group in your summarized dataset
 lib_CI <- data.frame(lib_predictions)
@@
 
-# Here we don't need to create an 'observation' column because the plot will use grouped data
-# If you do want an 'observation' identifier, ensure it's a sequence within each group
 lib_CI$observation <- seq_len(nrow(lib_CI))

### 2024-04-18 paper/paper/paper(1).qmd
Add files via upload

@@
 The Canadian electoral process, epitomizing democratic principles, empowers citizens to elect parliamentarians who shape Parliament's composition and, consequently, the government formation.
-In the recent 2021 federal election, Justin Trudeau's Liberal Party secured a majority in the 44th Parliament.
+In the recent 2021 federal election, Justin Trudeau's Liberal Party secured a majority in the 44th Parliament[@Nakhaie_2006].
 Voters' primary concerns include the cost of living, healthcare, climate change, post-pandemic recovery, and immigration, with dissatisfaction towards Trudeau's government prevalent.
-Trudeau's popularity lags behind UK's Poilievre.
+Trudeau's popularity lags behind UK's Poilievre[@Nakhaie_2006].
 The government's ambitious immigration plan aims to admit 500,000 migrants annually by 2025, albeit facing a backlog.
-The Conservative Party, with a focus on economic prosperity, emphasizes attracting highly skilled immigrants while addressing concerns like living costs and housing issues[@Canada].
+The Conservative Party, with a focus on economic prosperity, emphasizes attracting highly skilled immigrants while addressing concerns like living costs and housing issues[@Elections_2023].
 
 ## Hypothesis
-
+To enhance control and prevention of illegal immigration, the Liberal Party has suggested modifications to the Immigration and Refugee Protection Act.
+They propose establishing an annual refugee quota of 250, specifically aimed at supporting human rights defenders, journalists, and humanitarian workers seeking safety and resettlement in Canada.
+Looking ahead, the Liberal Party intends to incrementally increase this refugee quota, aiming for refugees to comprise 15% of all immigrants.
+Conversely, the share of economic immigrants is planned to decrease to 58%, while the family reunification immigrant ratio will remain constant.
+These proportions are expected to be maintained over the next two years.
+Moreover, the Canadian national government recently unveiled an ambitious plan to admit 500,000 migrants annually by 2025, looking for nearly 1.5 million newcomers in Canada within the next three years (Canada's Immigration Levels Plan 2024-2026).
+Historically, the Liberal government's immigration strategy tends to be more permissive, offering broader entry routes compared to that of the Conservative Party[@Nakhaie_2006].
 Based on our analysis of historical trends, governmental policies, and electoral procedures, our hypothesis aligns with the prevailing expectation that the Conservatives will emerge as the likely winners in the 2025 election.
-**We anticipate that the Conservatives will likely secure the highest number of votes, with the Liberals expected to closely follow in second place.** Our research indicates that the vote-counting process in Canada significantly influences the outcome, as voters do not directly elect a specific prime minister candidate.
+**We anticipate that the Liberals will likely secure the highest number of votes, with the Conservatives expected to closely follow in second place.** Our research indicates that the vote-counting process in Canada significantly influences the outcome, as voters do not directly elect a specific prime minister candidate.
 Initially, all votes are tallied based on first preferences.
 If a candidate obtains 50% of the vote, they win.
-If not, the candidate with the fewest votes is eliminated[@Canada].
+If not, the candidate with the fewest votes is eliminated[@Elections_2023].
 Then, votes from supporters of the eliminated candidate are redistributed to their second-choice candidate.
 This iterative redistribution continues until one candidate achieves 50% of the vote.
-Hence, our objective is to forecast the election probabilities for the Conservative and Liberal parties and compare which is higher[@Elections].
+Hence, our objective is to forecast the election probabilities for the Conservative and Liberal parties and compare which is higher[@Elections_2023].
 
@@
 knitr::kable(numeric_summary_df)
+
 ```
 
-@tbl-data-summary summaries the census and survey data reveals age distributions with the census data capturing a narrower age range (15 to 80 years, with a median of 54) compared to the broader age span in the survey data (18 to 97 years, with a median of 53).
+@tbl-data-summary-numeric summaries the census and survey data reveals age distributions with the census data capturing a narrower age range (15 to 80 years, with a median of 54) compared to the broader age span in the survey data (18 to 97 years, with a median of 53).
 The average ages for the census and survey populations are 52.18 and 51.3 years, respectively.
@@
 This involved segmenting the populace according to our model's predictors and calculating the voting proportions for each party within these segments.
-\newpage
 
@@
 -   $\pi_i$: Probability of voting for the Liberal/Conservative party
+
 ```{=tex}
@@
 y_i | \pi_i &\sim \text{Bernoulli}(\pi_i) \\
-\text{logit}(\pi_i) &= \beta_0 + \alpha^{age}_{a[i]} + \alpha^{gender}_{g[i]} + \alpha^{province}_{p[i]} + \alpha^{religion}_{r[i]} + \alpha^{income}_{m[i]} + \alpha^{education}_{e[i]} \\
-\beta_0 &\sim \text{Normal}(0, 2.5) \\
-\alpha_{a}^{age} &\sim \text{Normal}(0, \sigma^{2}_{age}) \quad \text{for } a \text{ in } 1, 2, \ldots, A \\
-\alpha_{g}^{gender} &\sim \text{Normal}(0, \sigma^{2}_{gender}) \quad \text{for } g \text{ in } Male,Female \\
-\alpha_{p}^{province} &\sim \text{Normal}(0, \sigma^{2}_{province}) \quad \text{for } p \text{ in } BC, AB, MB, NB, NL, NS, ON, PE, QC, SK \\
-\alpha_{r}^{religion} &\sim \text{Normal}(0, \sigma^{2}_{religion}) \quad \text{for } r \text{ in } YES,NO \\
-\alpha_{m}^{income} &\sim \text{Normal}(0, \sigma^{2}_{income}) \quad \text{for } m \text{ in } Lower Class, Middle Class, Upper Class\\
-\alpha_{e}^{education} &\sim \text{Normal}(0, \sigma^{2}_{education}) \quad \text{for } e \text{ in } Low Education, Some Education, High Education \\
-\sigma^{2}_{age} &\sim \text{Exponential}(1) \\
-\sigma^{2}_{gender} &\sim \text{Exponential}(1) \\
-\sigma^{2}_{province} &\sim \text{Exponential}(1) \\
-\sigma^{2}_{religion} &\sim \text{Exponential}(1) \\
-\sigma^{2}_{income} &\sim \text{Exponential}(1) \\
-\sigma^{2}_{education} &\sim \text{Exponential}(1) 
+\text{logit}(\pi_i) &= \beta_0 + \beta_1 x_{i,\text{age}} + \beta_2 x_{i,\text{gender}} + \beta_3 x_{i,\text{province}} + \beta_4 x_{i,\text{religion}} + \beta_5 x_{i,\text{income}} + \beta_6 x_{i,\text{education}} \\
+\beta_0 &\sim \text{Normal}(0, 1) \\
+\beta_1, \beta_2, \beta_3, \beta_4, \beta_5, \beta_6 &\sim \text{Normal}(0, 1)
 \end{align}
+
 ```
 
-## Model justification
+The model, as formulated in the Bayesian logistic regression framework, is designed to examine the impact of various sociodemographic factors on the probability of an individual voting for a specific political party, such as the Liberals or Conservatives in Canada.
+The probability $p_i$of a particular voting outcome follows a Bernoulli distribution, where each individual's probability of voting for the party is modeled using logistic regression.
 
-## Model Coefficients Interpretation
+## Components of the Model
+
+## Bernoulli Distribution
+Each binary outcome $y_i$ (whether an individual votes for the party or not) follows a Bernoulli distribution with success probability $pi_i$, which is the probability that $y_i = 1$.
+
+### Logit Link Function
+The logistic function or logit link transforms the linear combination of predictors into a probability (0 to 1).
+It is defined as $\log(\frac{\pi_i}{1-\pi_i})$, mapping real numbers from the linear predictors to the interval $[0,1]$.
+
+### Predictors and Coefficients
+   - $\beta_0$ (Intercept): Represents the baseline log-odds of voting for the party when all predictor variables are at zero or their reference categories.
+   - $\beta_1$ (Age): Reflects the influence of age on the probability of voting for the party.
+A positive $\beta_1$ indicates increasing age is associated with a higher likelihood of voting for the party.
+   - $\beta_2$(Gender): Adjusts the probability based on gender, typically comparing males to females if females are the reference category.
+   - $\beta_3$(Province): Accounts for regional variations in voting patterns, with coefficients for each province relative to a reference province.
+   - $\beta_4$ (Religion): Represents the difference in voting probability between individuals identifying with a religion versus those who do not.
+   - $\beta_5$ (Income): Captures the effect of income on voting behavior.
+   - $\beta_6$ (Education): Reflects how varying levels of education influence voting decisions.
+
+### Prior Distributions
+All coefficients, including the intercept, are assumed to follow a Normal(0, 1) distribution as priors.
+These priors are weakly informative, centering the expected value of each effect around zero but allowing the data to inform the final posterior distributions.
+This approach helps in regularizing the estimates, particularly in complex models or when data are limited.
+
+The model effectively quantifies how demographic and socioeconomic factors influence political behavior using Bayesian inference.
+This method provides a probabilistic framework that not only gives estimates of the effects but also accounts for uncertainty in a coherent way, offering more flexibility and insight than traditional frequentist approaches.
+By assuming normal priors, you are indicating a prior belief that none of the predictors has an unusually large effect, but you remain open to being informed by the data collected.
 
@@
 $$log(\frac{p}{1-p}) = \beta_0+\beta_1x_{age}+\beta_2x_{gender}+\beta_3x_{porvince}+\beta_{4}x_{religion}+\beta_{5}x_{income}+\beta_{6}x_{education}$$
-
+## Model Coefficients Interpretation
 $p$ is the probability of an individual casting their vote for a certain political party (Liberal or Conservative).
@@
 
-Table2: Summary the residuals for Conservative Party:
-```{r echo=FALSE, warning=FALSE}
+```{r, echo=FALSE, message=FALSE, warning = FALSE}
+#| label: tbl-coef-summary-conservative
+#| tbl-cap: Coefficients of the conservative Model
+#| echo: false
 
-liberal_residuals <- posterior_predict(liberal_model) - cleaned_survey_data$vote_liberal
-conservative_residuals <- posterior_predict(conservative_model) - cleaned_survey_data$vote_conservative
+install.packages("MASS")
 
-table_summary <- data.frame(
-  Party = c("Liberal", "Conservative"),
-  Mean_Residual = c(mean(liberal_residuals, na.rm = TRUE), mean(conservative_residuals, na.rm = TRUE)),
-  Median_Residual = c(median(liberal_residuals, na.rm = TRUE), median(conservative_residuals, na.rm = TRUE)),
-  SD_Residual = c(sd(liberal_residuals, na.rm = TRUE), sd(conservative_residuals, na.rm = TRUE)),
-  IQR_Residual = c(IQR(liberal_residuals, na.rm = TRUE), IQR(conservative_residuals, na.rm = TRUE))
-)
+library(MASS)
+library(broom)
+library(knitr)
 
-# Create a table of the data
-kable(table_summary, caption = "Summary of Residuals by Party")
+initial_model <- lm(vote_conservative ~ age + sex + province + education + religion + income_before_tax, data=cleaned_survey_data)
+
+step_cons <- stepAIC(initial_model, direction="both", trace = FALSE)  
+tidy_cons <- broom::tidy(step_cons, conf.int = TRUE)
+
+tidy_cons_selected <- tidy_cons[, c("term", "estimate", "std.error", "conf.low", "conf.high")]
+
+kable_output <- knitr::kable(tidy_cons_selected, format = "html", caption = "Model Summary for Conservative Vote Prediction with Confidence Intervals")
+
+kable_output
 
@@
 
-Table3: Summary the coefficient for Liberal Party:
+```{r, echo=FALSE, message=FALSE, warning = FALSE}
+#| label: tbl-coef-summary-liberal
+#| tbl-cap: Coefficients of the Liberal Model
+#| echo: false
 
-```{r echo=FALSE, warning=FALSE}
+# Assuming 'vote_liberal' is the column in your 'cleaned_survey_data' that represents voting for liberal
+initial_model_lib <- lm(vote_liberal ~ age + sex + province + education + religion + income_before_tax, data=cleaned_survey_data)
+step_lib <- stepAIC(initial_model_lib, direction="both", trace = FALSE)
 
-liberal_coefs <- coef(liberal_model)
-conservative_coefs <- coef(conservative_model)
+tidy_lib <- broom::tidy(step_lib, conf.int = TRUE)
 
-liberal_coefs_df <- data.frame(Estimate = liberal_coefs, row.names = NULL)
-conservative_coefs_df <- data.frame(Estimate = conservative_coefs, row.names = NULL)
+tidy_lib_selected <- tidy_lib[, c("term", "estimate", "std.error", "conf.low", "conf.high")]
 
-liberal_coefs_df$Term <- names(liberal_coefs)
-conservative_coefs_df$Term <- names(conservative_coefs)
+kable_output_lib <- knitr::kable(tidy_lib_selected, format = "html", caption = "Model Summary for Liberal Vote Prediction with Confidence Intervals")
+kable_output_lib
 
-liberal_coefs_df <- liberal_coefs_df[, c("Term", "Estimate")]
-conservative_coefs_df <- conservative_coefs_df[, c("Term", "Estimate")]
+```
 
-knitr::kable(liberal_coefs_df, caption = "Coefficients of the Liberal Model", row.names = FALSE)
-knitr::kable(conservative_coefs_df, caption = "Coefficients of the Conservative Model", row.names = FALSE)
+@tbl-coef-summary-liberal
+
+`
+
+@tbl-coef-summary-conservative
+
+@tbl-ypshat-summary
+```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+if (!require(MASS)) {
+    install.packages("MASS")
+    library(MASS)
+} else {
+    library(MASS)
+}
+
+m_lib <- glm(vote_liberal ~ age + sex + province + education + religion + income_before_tax,
+             data = cleaned_survey_data, family = "binomial")
+
+step_lib <- stepAIC(m_lib, direction = "both", trace = FALSE)
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, include = FALSE}
+
+m_lib <- glm(vote_liberal ~ age+sex+province+education+religion+income_before_tax,
+          data=cleaned_survey_data, family = "binomial")
+
+step_lib = stepAIC(m_lib, direction = "both", k = 2)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, include = FALSE}
+m_cons <- glm(vote_conservative ~ age+sex+province+education+religion+income_before_tax,
+          data=cleaned_survey_data, family = "binomial")
+
+step_cons <- stepAIC(m_cons, direction = "both", k = 2)
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, include = FALSE}
+
+step_cons <- glm(vote_conservative ~ age+province+education+religion+income_before_tax,
+          data=cleaned_survey_data, family = "binomial")
+step_cons_counts <- cleaned_survey_data %>%
+  group_by(age, province, education, religion, income_before_tax)%>%
+  summarise(N_j=n(), .groups = 'keep')
+
+step_cons_counts$estimate <- 
+  step_cons %>%
+  predict(newdata = step_cons_counts, type = "response")
+
+cons_aic <- step_cons_counts %>%
+  mutate(predict_prob_cons = estimate*N_j) %>% 
+  ungroup() %>%
+  summarise(yPS_cons_aic = sum(predict_prob_cons)/sum(N_j))
+
+cons_counts <- cleaned_survey_data%>%
+  group_by(age, sex, province, education, religion, income_before_tax)%>%
+  summarise(N_j=n(), .groups = 'keep')
+
+cons_counts$estimate <- 
+  m_cons %>%
+  predict(newdata = cons_counts, type = "response")
+
+cons_estimate <- cons_counts %>%
+  mutate(predict_prob_cons = estimate*N_j) %>% 
+  ungroup() %>%
+  summarise(yPS_cons = sum(predict_prob_cons)/sum(N_j))
+
+step_lib <- glm(vote_liberal ~ age+province+education+religion+income_before_tax,
+          data=cleaned_survey_data, family = "binomial")
+step_lib_counts <- cleaned_survey_data %>%
+  group_by(age, province, education, religion, income_before_tax)%>%
+  summarise(N_j=n(), .groups = 'keep')
+
+step_lib_counts$estimate <- 
+  step_lib %>%
+  predict(newdata = step_lib_counts, type = "response")
+
+lib_aic <- step_lib_counts %>%
+  mutate(predict_prob_lib = estimate*N_j) %>% 
+  ungroup() %>%
+  summarise(yPS_lib_aic = sum(predict_prob_lib)/sum(N_j))
+
+lib_counts <- cleaned_survey_data %>%
+  group_by(age, sex, province, education, religion, income_before_tax)%>%
+  summarise(N_j=n(), .groups = 'keep')
+
+lib_counts$estimate <- 
+  m_lib %>%
+  predict(newdata = lib_counts, type = "response")
+
+lib_estimate <- lib_counts %>%
+  mutate(predict_prob_lib = estimate*N_j) %>% 
+  ungroup() %>%
+  summarise(yPS_lib = sum(predict_prob_lib)/sum(N_j))
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+library(dplyr)
+Party_Name <- c("Conservative", "Liberal")
+yPS_primary <- c(cons_estimate,lib_estimate)
+yPS_AIC <- c(cons_aic ,lib_aic)
+
+knitr::kable(tibble(Party_Name, yPS_primary, yPS_AIC), caption = "The Hat of yPS For Each Party, Between Primary Model and Final Model")
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+library(ggplot2)
+library(dplyr)
+library(broom)
+
+required_vars <- c("vote_liberal", "age", "sex", "province", "education", "religion", "income_before_tax")
+missing_vars <- setdiff(required_vars, names(cleaned_survey_data))
+
+if(length(missing_vars) > 0) {
+  stop(paste("The following required variables are missing in the data frame:", paste(missing_vars, collapse=", ")))
+}
+model_lib <- lm(vote_liberal ~ age + sex + province + education + religion + income_before_tax, data=cleaned_survey_data)
+model_summary_lib <- broom::tidy(model_lib, conf.int = TRUE)
+
+ggplot(model_summary_lib, aes(x = estimate, y = reorder(term, estimate))) +
+  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
+  labs(x = "Estimate", y = "Coefficient", title = "Coefficient Estimates for Liberal Vote Prediction") +
+  theme_minimal()
+
+```
+
+@
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+library(ggplot2)
+library(dplyr)
+
+# Assuming 'cleaned_survey_data' contains 'province' and 'vote_liberal',
+# where 'vote_liberal' is a binary (0/1) indicating whether a vote for liberal was cast.
+
+# Calculate proportions and confidence intervals by province for the liberal party
+liberal_votes_by_province <- cleaned_survey_data %>%
+  group_by(province) %>%
+  summarise(
+    proportion = mean(vote_liberal, na.rm = TRUE),
+    lower = proportion - qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
+    upper = proportion + qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
+    .groups = 'drop'  # Drop grouping for further manipulation if needed
+  ) %>%
+  ungroup()  # Ensure we remove the grouping for the ggplot
+
+# Create the plot for the liberal party
+ggplot(liberal_votes_by_province, aes(x = reorder(province, -proportion), y = proportion)) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
+  coord_flip() +  # Flip the axes to have provinces on the y-axis
+  labs(x = "Proportion", y = "Province", title = "Estimated Proportion of Voting for Liberal by Province") +
+  theme_minimal()
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+library(ggplot2)
+library(dplyr)
+
+# Assuming 'cleaned_survey_data' is your dataframe and it contains the variables 'education' and 'vote_liberal'
+# where 'vote_liberal' is a binary (0/1) indicating whether a vote for liberal was cast.
+
+liberal_votes_by_education <- cleaned_survey_data %>%
+  group_by(education) %>%
+  summarise(
+    proportion = mean(vote_liberal, na.rm = TRUE),
+    lower = proportion - qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
+    upper = proportion + qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
+    .groups = 'drop'  # This will automatically ungroup the data (requires dplyr version 1.0.0 or higher)
+  ) %>%
+  arrange(desc(proportion))
+
+ggplot(liberal_votes_by_education, aes(x = reorder(education, proportion), y = proportion)) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
+  coord_flip() +  # Flip the axes to have education levels on the y-axis
+  labs(x = "Proportion", y = "Education", title = "Proportion of Votes for Liberal by Education Level") +
+  theme_minimal()
 
@@
 This trend is echoed in Barik's 2023 article, which indicates a public perception of the Conservative Party's superior handling of these key issues.
-Thus, our working hypothesis posits that the Conservative Party holds a slender advantage in the race for the upcoming election[@Barik].
+Thus, our working hypothesis posits that the Conservative Party holds a slender advantage in the race for the upcoming election[@Barik_2023].
 
@@
 In conclusion, our binary logistic regression approach, supplemented with post-stratification, has yielded a data-driven forecast for the 2025 Canadian Election.
-Aligning with Barik’s analysis and multiple polls, our findings suggest the Conservative Party is poised for a narrow victory over the Liberal Party, informed by an intricate blend of sociopolitical factors and current Canadian sentiment[@Barik].
+Aligning with Barik’s analysis and multiple polls, our findings suggest the Conservative Party is poised for a narrow victory over the Liberal Party, informed by an intricate blend of sociopolitical factors and current Canadian sentiment[@Barik_2023].
 
@@
 
-@fig-liberal-model portrays the posterior and prior distributions for parameters in a Bayesian liberal model, with a stark divergence in the intercept suggesting significant data-driven adjustments from the model's baseline estimation.
-Parameters representing demographic and geographical factors are plotted as colored dots along an axis, indicating median values and the extent of uncertainty.
-While the priors and posteriors largely overlap, indicating consistent estimates for many parameters, the intercept's noticeable shift underscores the data's impactful role in refining the model, particularly highlighting the updated understanding of the model's fundamental starting point.
-
-\newpage
-
-```{r fig-conservative-posterior, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.cap="Comparison of Posterior and Prior Distributions in the Conservative Model"}
-library(bayesplot)
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=8, fig.height=6}
 
@@
 
-pp_plot <- posterior_vs_prior(conservative_model) +
+conservative_model <- stan_glm(
+  vote_conservative ~ age + sex + province + education + religion + income_before_tax,
+  data = cleaned_survey_data,
+  family = "binomial",
+  prior = prior_covariates,
+  prior_intercept = prior_intercept,
+  chains = 4,
+  iter = 2000
+)
+
+pp_plot_conservative <- posterior_vs_prior(conservative_model) +
   theme_minimal() +
@@
 
-@fig-conservative-posterior presents a side-by-side comparison of the median and spread of prior and posterior distributions for the parameters in a Bayesian model, applied to the Conservative context.
-Key findings include the posterior distribution of the "age" parameter mirroring its prior, which validates the initial assumption about its influence.
-In contrast, the intercept and sigma parameters show slight shifts, indicating the data's role in refining these estimates.
-The placement of medians for other parameters—like sex, religion, and province—demonstrates the data's impact in confirming or adjusting prior beliefs.
-Overall, the alignment of posterior distributions with priors confirms the model's accuracy and the informative value of the data in capturing the effects on the dependent variable, suggesting a robust model fit.
+@fig-liberal-model
+\newpage
 
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+
+cons_predictions <- predict(step_cons, newdata = step_cons_counts, type = "response", interval = "confidence")
+cons_CI <- data.frame(cons_predictions)
+
+cons_CI$lwr <- cons_CI$cons_predictions - 1.96 * sqrt(cons_CI$cons_predictions * (1 - cons_CI$cons_predictions) / nrow(cons_CI))
+cons_CI$upr <- cons_CI$cons_predictions + 1.96 * sqrt(cons_CI$cons_predictions * (1 - cons_CI$cons_predictions) / nrow(cons_CI))
+
+cons_CI$observation <- 1:nrow(cons_CI)
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+
+step_lib_counts <- cleaned_survey_data %>%
+  group_by(age, sex, province, education, religion, income_before_tax) %>%
+  summarise(N_j=n(), .groups = 'drop')  # Use .groups = 'drop' to remove the grouping
+
+lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response")
+lib_CI <- data.frame(lib_predictions)
+lib_CI$lwr <- lib_CI$lib_predictions - 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+lib_CI$upr <- lib_CI$lib_predictions + 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+
+lib_CI$observation <- seq_len(nrow(lib_CI))
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response", interval = "confidence")
+lib_CI <- data.frame(lib_predictions)
+
+lib_CI$lwr <- lib_CI$lib_predictions - 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / nrow(lib_CI))
+lib_CI$upr <- lib_CI$lib_predictions + 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / nrow(lib_CI))
+
+lib_CI$observation <- 1:nrow(lib_CI)
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
+ggplot(cons_CI, aes(x = cons_predictions)) +
+  geom_density(alpha = 0.5, fill = "blue") +
+  labs(x = "Predicted Probability", y = "Density", title = "Plot.9 The Density Plot for Predicted Probabilities for Conservative")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
+ggplot(lib_CI, aes(x = lib_predictions, fill = "Liberal")) +
+  geom_density(alpha = 0.5, fill = "green") +
+  labs(x = "Predicted Probability", y = "Density", title = "Plot.10 The Density Plot for Predicted Probabilities for Liberal")
+```
+
+@fig-conservative-posterior 
 \newpage

### 2024-04-18 paper/paper(1).qmd
Add files via upload

@@
 ## Import necessary libraries
+install.packages("MASS")
 library(ggplot2)
@@
 library(bayesplot)
+library(MASS)
+library(broom)
 ```
@@
 ## Hypothesis
+
 To enhance control and prevention of illegal immigration, the Liberal Party has suggested modifications to the Immigration and Refugee Protection Act.
@@
 We've made necessary adjustments to ensure it matches our survey data.
-Data collection aims to provide a detailed snapshot of demographic, economic, and social characteristics.The GSS is a nationwide survey program designed to collect data on societal trends, behaviors, and attributes across the entire population, offering insights into the changing dynamics of communities.
+Data collection aims to provide a detailed snapshot of demographic, economic, and social characteristics.The GSS is a nationwide survey program designed to collect data on societal trends, behaviors, and attributes across the entire population, offering insights into the changing dynamics of communities[@GSS_2022].
 
@@
 The CES focuses specifically on voter behavior, attitudes, and the electoral process within the Canadian context.
-Unlike the GSS, which aims for a comprehensive overview, the CES targets specific topics of interest to derive insights from a segment of the population.
+Unlike the GSS, which aims for a comprehensive overview, the CES targets specific topics of interest to derive insights from a segment of the population[@CES_2023].
 
@@
 
+\newpage
 ### Data Visualization
@@
 This comparison highlights the distinct age profiles captured by the two sources, with a significant representation of middle-aged individuals in both, with the survey dataset capturing a broader demographic.
+
 \newpage
@@
 This visual comparison reveals not only the variations in population coverage between the two types of data but also significant regional differences within the datasets, which could reflect varied sampling methods or demographic distributions.
+
 \newpage
@@
 The differences observed in the chart might also reflect methodological variations in data collection or inherent biases within the sampling frames used.
+
 \newpage
@@
 This discrepancy underscores a pronounced difference in the representation of religious affiliation between the two data sources, potentially alluding to divergent demographic characteristics or response patterns within the datasets.
+
 \newpage
@@
 The overall higher presence of red bars signifies a general trend of voter disengagement, which may warrant further investigation through regression analysis and post-stratification to grasp the full scope of electoral dynamics and the broader implications for the Canadian democratic process.
+
 \newpage
@@
 # Model
+
 We utilized the rstanarm package for constructing the generalized linear model[@R-rstanarm], the rstanarm package serves as a user-friendly interface in R for fitting Bayesian regression models using the Stan probabilistic programming language.
@@
 -   $y_i$: Binary outcome of voting for the Liberal/Conservative party (1) or not (0)
--   $\pi_i$: Probability of voting for the Liberal/Conservative party
+-   $\log(\frac{\pi_i}{1-\pi_i})$: Probability of voting for the Liberal/Conservative party
+
 ```{=tex}
@@
 y_i | \pi_i &\sim \text{Bernoulli}(\pi_i) \\
-\text{logit}(\pi_i) &= \beta_0 + \alpha^{age}_{a[i]} + \alpha^{gender}_{g[i]} + \alpha^{province}_{p[i]} + \alpha^{religion}_{r[i]} + \alpha^{income}_{m[i]} + \alpha^{education}_{e[i]} \\
-\beta_0 &\sim \text{Normal}(0, 2.5) \\
-\alpha_{a}^{age} &\sim \text{Normal}(0, \sigma^{2}_{age}) \quad \text{for } a \text{ in } 1, 2, \ldots, A \\
-\alpha_{g}^{gender} &\sim \text{Normal}(0, \sigma^{2}_{gender}) \quad \text{for } g \text{ in } Male,Female \\
-\alpha_{p}^{province} &\sim \text{Normal}(0, \sigma^{2}_{province}) \quad \text{for } p \text{ in } BC, AB, MB, NB, NL, NS, ON, PE, QC, SK \\
-\alpha_{r}^{religion} &\sim \text{Normal}(0, \sigma^{2}_{religion}) \quad \text{for } r \text{ in } YES,NO \\
-\alpha_{m}^{income} &\sim \text{Normal}(0, \sigma^{2}_{income}) \quad \text{for } m \text{ in } Lower Class, Middle Class, Upper Class\\
-\alpha_{e}^{education} &\sim \text{Normal}(0, \sigma^{2}_{education}) \quad \text{for } e \text{ in } Low Education, Some Education, High Education \\
-\sigma^{2}_{age} &\sim \text{Exponential}(1) \\
-\sigma^{2}_{gender} &\sim \text{Exponential}(1) \\
-\sigma^{2}_{province} &\sim \text{Exponential}(1) \\
-\sigma^{2}_{religion} &\sim \text{Exponential}(1) \\
-\sigma^{2}_{income} &\sim \text{Exponential}(1) \\
-\sigma^{2}_{education} &\sim \text{Exponential}(1) 
+\text{logit}(\frac{\pi_i}{1-\pi_i}) &= \beta_0 + \beta_1 x_{i,\text{age}} + \beta_2 x_{i,\text{gender}} + \beta_3 x_{i,\text{province}} + \beta_4 x_{i,\text{religion}} + \beta_5 x_{i,\text{income}} + \beta_6 x_{i,\text{education}} \\
+\beta_0 &\sim \text{Normal}(0, 1) \\
+\beta_1, \beta_2, \beta_3, \beta_4, \beta_5, \beta_6 &\sim \text{Normal}(0, 1)
 \end{align}
 ```
+The model, as formulated in the Bayesian logistic regression framework, is designed to examine the impact of various sociodemographic factors on the probability of an individual voting for a specific political party, such as the Liberals or Conservatives in Canada.
+The probability $\log(\frac{\pi_i}{1-\pi_i})$of a particular voting outcome follows a Bernoulli distribution, where each individual's probability of voting for the party is modeled using logistic regression.
 
-## Model justification
+## Components of the Model
 
-## Model Coefficients Interpretation
+**Bernoulli Distribution** Each binary outcome $y_i$ (whether an individual votes for the party or not) follows a Bernoulli distribution with success probability $\log(\frac{\pi_i}{1-\pi_i})$, which is the probability that $y_i = 1$.
+
+**Logit Link Function** The logistic function or logit link transforms the linear combination of predictors into a probability (0 to 1).
+It is defined as $\log(\frac{\pi_i}{1-\pi_i})$, mapping real numbers from the linear predictors to the interval $[0,1]$.
+
+**Predictors and Coefficients** - $\beta_0$ (Intercept): Represents the baseline log-odds of voting for the party when all predictor variables are at zero or their reference categories.
+- $\beta_1$ (Age): Reflects the influence of age on the probability of voting for the party.
+A positive $\beta_1$ indicates increasing age is associated with a higher likelihood of voting for the party.
+- $\beta_2$(Gender): Adjusts the probability based on gender, typically comparing males to females if females are the reference category.
+- $\beta_3$(Province): Accounts for regional variations in voting patterns, with coefficients for each province relative to a reference province.
+- $\beta_4$ (Religion): Represents the difference in voting probability between individuals identifying with a religion versus those who do not.
+- $\beta_5$ (Income): Captures the effect of income on voting behavior.
+- $\beta_6$ (Education): Reflects how varying levels of education influence voting decisions.
+
+**Prior Distributions** All coefficients, including the intercept, are assumed to follow a Normal(0, 1) distribution as priors.
+These priors are weakly informative, centering the expected value of each effect around zero but allowing the data to inform the final posterior distributions.
+This approach helps in regularizing the estimates, particularly in complex models or when data are limited.
+
+The model effectively quantifies how demographic and socioeconomic factors influence political behavior using Bayesian inference.
+This method provides a probabilistic framework that not only gives estimates of the effects but also accounts for uncertainty in a coherent way, offering more flexibility and insight than traditional frequentist approaches.
+By assuming normal priors, it indicating a prior belief that none of the predictors has an unusually large effect, but remain open to being informed by the data collected.
 
@@
 
-$$log(\frac{p}{1-p}) = \beta_0+\beta_1x_{age}+\beta_2x_{gender}+\beta_3x_{porvince}+\beta_{4}x_{religion}+\beta_{5}x_{income}+\beta_{6}x_{education}$$
-
-$p$ is the probability of an individual casting their vote for a certain political party (Liberal or Conservative).
+$$log(\frac{p}{1-p}) = \beta_0+\beta_1x_{age}+\beta_2x_{gender}+\beta_3x_{porvince}+\beta_{4}x_{religion}+\beta_{5}x_{income}+\beta_{6}x_{education}$$ **Model Coefficients Interpretation** $p$ is the probability of an individual casting their vote for a certain political party (Liberal or Conservative).
 
@@
 
-install.packages("MASS")
-# Load the necessary library
 library(MASS)
@@
 
-# Fit the initial linear model
 initial_model <- lm(vote_conservative ~ age + sex + province + education + religion + income_before_tax, data=cleaned_survey_data)
 
-# Perform stepwise model selection using stepAIC
 step_cons <- stepAIC(initial_model, direction="both", trace = FALSE)  
-
-# Use broom::tidy to get a tidy data frame of the model summary with confidence intervals
 tidy_cons <- broom::tidy(step_cons, conf.int = TRUE)
 
-# Select the columns you want for the table, excluding statistic and p-value
 tidy_cons_selected <- tidy_cons[, c("term", "estimate", "std.error", "conf.low", "conf.high")]
 
-# Create the table with knitr::kable()
-kable_output <- knitr::kable(tidy_cons_selected, format = "html", caption = "Model Summary for Conservative Vote Prediction with Confidence Intervals")
+kable_output <- knitr::kable(tidy_cons_selected, format = "html")
 
-# Display the table output
 kable_output
@@
 ```
+
+@tbl-coef-summary-conservative presents calculated coefficients that integrate into our logistic regression model for conservative party, derived from the survey dataset from General Social Survey[@GSS_2022].
+The `knitr` package [@rKnitr] was utilized to generate the table.
+These coefficients represent the adjusted effects of various predictors such as age, province, education, religion, and income brackets on the log odds of an individual reporting a certain behavior or characteristic.
+
+In the context of R Studio, the `MASS` package[@MASS], although not directly used here, is often employed for its functions related to linear and quadratic discriminant function analysis, while the `broom` package tidies the output of statistical tests into data frames to facilitate further data analysis or visualization.
+Specifically, `broom` [@broom]can convert the summary output of regression models into an easy-to-handle data frame, as shown in the table.
+
+The table details the point estimates for each predictor along with their standard errors and confidence intervals, providing insight into the precision of the estimates and the potential range within which the true value of the coefficients may lie.
+Notably, the intercept and coefficients for variables such as 'provincePrince Edward Island' and 'income_before_taxUpper Class' have both negative and positive values, indicating their varied influence on the outcome variable.
+The confidence intervals suggest the level of certainty about the estimates, where a narrower interval represents a more precise estimate.
+These results contribute to our understanding of the factors influencing voter behavior, guiding the development of targeted strategies for engagement and policy-making.
 
@@
 
-# Assuming 'vote_liberal' is the column in your 'cleaned_survey_data' that represents voting for liberal
 initial_model_lib <- lm(vote_liberal ~ age + sex + province + education + religion + income_before_tax, data=cleaned_survey_data)
@@
 
-kable_output_lib <- knitr::kable(tidy_lib_selected, format = "html", caption = "Model Summary for Liberal Vote Prediction with Confidence Intervals")
+kable_output_lib <- knitr::kable(tidy_lib_selected, format = "html")
 kable_output_lib
@@
 
-@tbl-coef-summary-liberal
+@tbl-coef-summary-liberal provided outlines the logistic regression model coefficients pertinent to predicting voting behavior for the Liberal Party, based on the survey data extracted from the General Social Survey [@GSS_2022].
+Fabricated through the adept use of the `knitr` package [@rKnitr], the table concisely encapsulates the nuanced influence of various demographic and socioeconomic predictors — age, gender, province, educational, religion, and income — on the likelihood of an individual voting Liberal.
 
-`
+Diving into the details, the table lists the estimated coefficients and their accompanying standard errors, offering a statistical measure of the precision of the estimates.
+The confidence intervals provided for each coefficient — lower (conf.low) and higher (conf.high) bounds — delineate the range in which the true coefficient values are likely to fall, with tighter intervals indicating higher precision.
+For instance, the negative coefficient for 'provincePrince Edward Island' suggests a lesser inclination to vote Liberal in that region compared to the reference province, while the positive coefficients for 'provinceNewfoundland and Labrador' and 'provinceOntario' reflect a stronger propensity for Liberal support.
 
-@tbl-coef-summary-conservative
+While not employed directly in the analysis leading to this table, the `MASS` package [@MASS] is typically revered for its robust functionalities in linear discriminant analysis, an alternative approach to examining group differences.
+Complementing this, the `broom` package [@broom] elegantly streamlines the model outputs into tidy data frames, greatly simplifying the transition from statistical testing to interpretable results and potential graphical representation.
 
-@tbl-ypshat-summary
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-library(dplyr)
+```{r, label="tbl-yps-summary", echo=FALSE, message=FALSE, warning=FALSE}
+#| label: tbl-yps-summary
+#| tbl-cap: The Hat of yPS For Each Party, Between Primary Model and Final Model
+#| echo: false
 Party_Name <- c("Conservative", "Liberal")
@@
 
-knitr::kable(tibble(Party_Name, yPS_primary, yPS_AIC), caption = "The Hat of yPS For Each Party, Between Primary Model and Final Model")
+knitr::kable(tibble(Party_Name, yPS_primary, yPS_AIC))
 
@@
 
+Based on @tbl-yps-summary, the estimates suggest differing probabilities for each major party.
+For the Conservative Party, the final model adjustment indicates an estimated voting probability of about 28.66%.
+This projection implies that roughly 28.66% of the population, characterized by certain age, province, education, religion, and income factors, would likely vote Conservative in the 2025 Canadian Election.
+In contrast, the Liberal Party's estimated voting probability is slightly higher at approximately 28.83% under the AIC-adjusted model, suggesting that nearly 28.83% of individuals with the specified demographics are predicted to cast their vote for the Liberals.
+\newpage
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-library(ggplot2)
-library(dplyr)
-library(broom)
-
+#| label: fig-liberal-coefficients
+#| tbl-cap: "Coefficient Estimates for Liberal Vote Prediction"
+#| echo: false
 required_vars <- c("vote_liberal", "age", "sex", "province", "education", "religion", "income_before_tax")
@@
   geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
-  labs(x = "Estimate", y = "Coefficient", title = "Coefficient Estimates for Liberal Vote Prediction") +
+  labs(x = "Estimate", y = "Coefficient") +
   theme_minimal()
@@
 
-@
+@fig-liberal-coefficients displays the logistic regression model's estimated coefficients relating to the likelihood of supporting the Liberal party, based on various factors.
+Each point (dot) on the plot signifies the model's coefficient for a specific predictor, with the position on the x-axis indicating the magnitude and direction of the predictor's effect.
+Horizontal lines represent the confidence intervals, giving a visual representation of the estimate's precision and the range within which we can be confident that the actual value of the coefficient lies.
+
+The intercept, situated near zero, represents the baseline log-odds of voting for the Liberal party when all predictors are at their reference levels.
+The estimates for provinces such as Newfoundland and Labrador, Ontario, and New Brunswick are situated to the right of the intercept, demonstrating a positive relationship with Liberal support.
+Conversely, the coefficient for Prince Edward Island is markedly left of the intercept, suggesting a negative association with the likelihood of voting for the Liberals.
+
+Notably, the coefficient for 'sexMale' is negative, indicating that being male is associated with a lower likelihood of voting for the Liberal party compared to the reference group, presumably females.
+Age shows a small positive coefficient, hinting at a slight increase in Liberal support with advancing age.
+
+'Upper Class' and 'Middle Class' both have positive coefficients, suggesting higher income brackets may correlate with increased support for the Liberal party.
+In terms of education, 'Low Education' and 'Some Education' have negative coefficients, indicating these groups might be less inclined to vote Liberal.
+
+The red dashed line at zero is a reference that indicates no effect; coefficients to the right demonstrate a positive influence on Liberal support, while those to the left indicate a negative influence.
+The plot orders the variables on the y-axis, providing a hierarchy of impact, from the most positive at the top to the most negative at the bottom.
+
+This figure offers a nuanced understanding of how different demographic and socioeconomic variables might influence Liberal party support, informing strategic political engagement and policy development.
+The spread of the confidence intervals highlights areas of greater or lesser certainty in the model's predictions, essential for interpreting the robustness of the variables' effects.
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-library(ggplot2)
-library(dplyr)
-
-# Assuming 'cleaned_survey_data' contains 'province' and 'vote_liberal',
-# where 'vote_liberal' is a binary (0/1) indicating whether a vote for liberal was cast.
-
-# Calculate proportions and confidence intervals by province for the liberal party
+#| label: fig-liberal-votes-by-province
+#| tbl-cap: "Estimated Proportion of Voting for Liberal by Province"
+#| echo: false
 liberal_votes_by_province <- cleaned_survey_data %>%
@@
     upper = proportion + qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
-    .groups = 'drop'  # Drop grouping for further manipulation if needed
+    .groups = 'drop'  
   ) %>%
-  ungroup()  # Ensure we remove the grouping for the ggplot
+  ungroup()
 
-# Create the plot for the liberal party
 ggplot(liberal_votes_by_province, aes(x = reorder(province, -proportion), y = proportion)) +
@@
   geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
-  coord_flip() +  # Flip the axes to have provinces on the y-axis
-  labs(x = "Proportion", y = "Province", title = "Estimated Proportion of Voting for Liberal by Province") +
+  coord_flip() +  
+  labs(x = "Proportion", y = "Province") +
   theme_minimal()
@@
 ```
+@fig-liberal-votes-by-province visualizes the estimated proportions of support for the Liberal party across various Canadian provinces.
+Each dot on the graph indicates the mean proportion of Liberal votes within a province, while the horizontal lines represent the error bars, which detail the confidence interval for these proportions.
+The span of each line reflects the level of uncertainty or variability in the estimate—wider lines suggest more uncertainty.
+
+From top to bottom, provinces are listed in order of descending support for the Liberal party.
+For example, Newfoundland and Labrador exhibit the highest point estimate, indicating a stronger inclination towards the Liberal party, whereas Prince Edward Island shows a significantly lower estimate of Liberal support.
+There is no dashed line at the 50% mark here, unlike in the referenced Trump support graph, because the graph aims to show the varying levels of Liberal support across provinces rather than a majority threshold.
+
+The variability in the error bars suggests that certain provinces, such as Ontario and Newfoundland and Labrador, have more precise estimates of Liberal support, while provinces like Nova Scotia have wider confidence intervals, indicating less certainty in the estimated proportion.
+This graphic presentation allows for an at-a-glance comparison of Liberal party support among the provinces, highlighting regions where the party is either particularly strong or may need to focus more campaign efforts.
+\newpage
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-library(ggplot2)
-library(dplyr)
-
-# Assuming 'cleaned_survey_data' is your dataframe and it contains the variables 'education' and 'vote_liberal'
-# where 'vote_liberal' is a binary (0/1) indicating whether a vote for liberal was cast.
-
+#| label: fig-liberal-votes-by-education
+#| fig-cap: "Proportion of Votes for Liberal by Education Level"
+#| echo: false
 liberal_votes_by_education <- cleaned_survey_data %>%
@@
     upper = proportion + qnorm(0.975) * sqrt(proportion * (1 - proportion) / n()),
-    .groups = 'drop'  # This will automatically ungroup the data (requires dplyr version 1.0.0 or higher)
+    .groups = 'drop'  
   ) %>%
@@
   geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
-  coord_flip() +  # Flip the axes to have education levels on the y-axis
-  labs(x = "Proportion", y = "Education", title = "Proportion of Votes for Liberal by Education Level") +
+  coord_flip() + 
+  labs(x = "Proportion", y = "Education") +
   theme_minimal()
@@
 ```
+@fig-liberal-votes-by-education depicts the estimated proportions of liberal votes across different education levels.
+Each point on the graph represents the mean proportion of votes for the Liberal party within each educational category.
+The horizontal error bars signify the confidence intervals around these estimates, indicating the degree of uncertainty or the range within which the true proportion is likely to fall.
 
-## Plot of binary logistic regression models
+The y-axis categorizes education into 'Low Education', 'Some Education', and 'High Education'.
+The x-axis measures the proportion of votes, with the plotted points reflecting the central tendency of votes for the Liberal party within each education group.
+Notably, the confidence intervals for 'Some Education' and 'High Education' are narrow, suggesting a higher degree of certainty in these estimates, whereas the 'Low Education' group exhibits a wider interval, denoting greater uncertainty.
+
+This visual analysis suggests a relationship between education level and voting patterns, with the 'High Education' group showing the highest estimated support for the Liberal party.
+In contrast, the 'Low Education' group appears to have the lowest, potentially indicating differing political preferences based on education.
+These insights could guide campaign strategies to address the educational divide in political support.
 
 # Discussion
+
 Recent research highlights that the primary concerns for Canadian voters leading up to the 2025 election include the rising cost of living, housing, healthcare, the economy, and the environment.
@@
 ## Consideration of Potential Bias
+
 One limitation we noted was the age of participants in the data from 2021.
@@
 ## Pathways for Enhanced Predictive Accuracy
+
 Our endeavor has shed light on the inherent complexities of electoral forecasting.
@@
 
-@fig-liberal-model
-\newpage
+@fig-liberal-model \newpage
 
@@
 
-@fig-conservative-posterior 
-\newpage
+@fig-conservative-posterior \newpage
 

### 2024-04-18 paper 2/paper(1).qmd
Add files via upload

--- 2024-04-18 paper/paper(1).qmd
@@
 The table details the point estimates for each predictor along with their standard errors and confidence intervals, providing insight into the precision of the estimates and the potential range within which the true value of the coefficients may lie.
-Notably, the intercept and coefficients for variables such as 'provincePrince Edward Island' and 'income_before_taxUpper Class' have both negative and positive values, indicating their varied influence on the outcome variable.
+Notably, the intercept and coefficients for variables such as 'provincePrince Edward Island' and 'provinceOntario' have both negative and positive values, indicating their varied influence on the outcome variable.
 The confidence intervals suggest the level of certainty about the estimates, where a narrower interval represents a more precise estimate.
@@
 
-From top to bottom, provinces are listed in order of descending support for the Liberal party.
-For example, Newfoundland and Labrador exhibit the highest point estimate, indicating a stronger inclination towards the Liberal party, whereas Prince Edward Island shows a significantly lower estimate of Liberal support.
-There is no dashed line at the 50% mark here, unlike in the referenced Trump support graph, because the graph aims to show the varying levels of Liberal support across provinces rather than a majority threshold.
+From top to bottom, provinces are listed in order of increasing support for the Liberal party.
+For example, Newfoundland and Labrador exhibit the highest point estimate (about 39%), indicating a stronger inclination towards the Liberal party, whereas Prince Edward Island shows a significantly lower estimate of Liberal support (about 0%).
+The graph aims to show the varying levels of Liberal support across provinces, the black dot on the graph indicates the point estimate of the proportion of voters within the corresponding province who are predicted to vote for Liberal party.
 
-The variability in the error bars suggests that certain provinces, such as Ontario and Newfoundland and Labrador, have more precise estimates of Liberal support, while provinces like Nova Scotia have wider confidence intervals, indicating less certainty in the estimated proportion.
+The variability in the error bars suggests that certain provinces, such as Ontario and Newfoundland and New Brunswick, have more precise estimates of Liberal support, while provinces like Nova Scotia have wider confidence intervals, indicating less certainty in the estimated proportion.
 This graphic presentation allows for an at-a-glance comparison of Liberal party support among the provinces, highlighting regions where the party is either particularly strong or may need to focus more campaign efforts.
@@
 The horizontal error bars signify the confidence intervals around these estimates, indicating the degree of uncertainty or the range within which the true proportion is likely to fall.
+Moreover, the black dot notes the point estimate of the proportion of voters within the corresponding education category who are predicted to vote for liberal party.
 
@@
 
-This visual analysis suggests a relationship between education level and voting patterns, with the 'High Education' group showing the highest estimated support for the Liberal party.
-In contrast, the 'Low Education' group appears to have the lowest, potentially indicating differing political preferences based on education.
+This visual analysis suggests a relationship between education level and voting patterns, with the 'High Education' group showing the highest estimated support for the Liberal party (about 33%).
+In contrast, the 'Low Education' group appears to have the lowest (about 23%), potentially indicating differing political preferences based on education.
 These insights could guide campaign strategies to address the educational divide in political support.
@@
 
-## Consideration of Potential Bias
+## Consideration of Potential Bias and Limitations
 
@@
 Nonetheless, the potential impact of their age on our prediction model merits further attention in subsequent studies.
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+step_lib_counts <- cleaned_survey_data %>%
+  group_by(age, sex, province, education, religion, income_before_tax) %>%
+  summarise(N_j=n(), .groups = 'drop')
+
+lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response")
+lib_CI <- data.frame(lib_predictions)
+lib_CI$lwr <- lib_CI$lib_predictions - 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+lib_CI$upr <- lib_CI$lib_predictions + 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+
+lib_CI$observation <- seq_len(nrow(lib_CI))
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+step_lib_counts <- cleaned_survey_data %>%
+  group_by(age, sex, province, education, religion, income_before_tax) %>%
+  summarise(N_j=n(), .groups = 'drop')
+
+lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response")
+lib_CI <- data.frame(lib_predictions)
+lib_CI$lwr <- lib_CI$lib_predictions - 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+lib_CI$upr <- lib_CI$lib_predictions + 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+
+lib_CI$observation <- seq_len(nrow(lib_CI))
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide', include =FALSE}
+
+lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response")
+
+lib_CI <- data.frame(
+  estimate = lib_predictions,
+
+  observation = seq_along(lib_predictions)
+)
+
+head(lib_CI)
+
+```
+
+```{r}
+#| label: fig-liberal-votes-and-consrvative_votes
+#| fig-cap: "predicted probabilities for the Conservative and Liberal parties"
+#| echo: false
+cons_probs <- predict(step_cons, newdata = cleaned_survey_data, type = "response")
+lib_probs <- predict(step_lib, newdata = cleaned_survey_data, type = "response")
+
+combined_predictions <- data.frame(
+  PredictedProbability = c(cons_probs, lib_probs),
+  Party = rep(c("Conservative", "Liberal"), each = length(cons_probs))
+)
+
+ggplot(combined_predictions, aes(x = PredictedProbability, fill = Party)) +
+  geom_density(alpha = 0.5) +
+  facet_wrap(~ Party, nrow = 2) +
+  scale_fill_manual(values = c("red", "green")) +
+  labs(x = "Predicted Probability", y = "Density") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+```
+
+@fig-liberal-votes-and-consrvative_votes provide density plots illustrating the distribution of predicted probabilities for the Conservative and Liberal parties, respectively.
+Both plots reveal a slight left skew, indicating a greater concentration of predictions at the lower probability range, nearer to 0.2.
+This skew suggests that while both parties are predicted to have a significant chance of receiving votes, there's a tendency for the model to assign a moderate likelihood rather than a strong certainty of voting outcomes.
+
+Notably, the Liberal party's density plot reaches a higher peak, which points to a narrower, more defined range of predicted probabilities.
+This contrast implies that the model predicts voting probabilities for the Liberal party with more confidence, as the predictions are less spread out over a range of values compared to the Conservative party.
+
+Additionally, the visible overlap between the two distributions signifies a degree of ambiguity or uncertainty in differentiating the predicted probabilities for the two parties.
+The shared area of the plots indicates that for a substantial portion of predictions, the likelihood of individuals voting for either party is comparably uncertain.
+
+This graphical representation underscores the nuanced nature of electoral predictions, where despite clear tendencies, there remains a non-negligible degree of overlap and hence, predictive uncertainty.
+It is important to note that the analysis does not incorporate predictions for the NDP party, focusing solely on the Conservative and Liberal parties.
 
@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-
-cons_predictions <- predict(step_cons, newdata = step_cons_counts, type = "response", interval = "confidence")
-cons_CI <- data.frame(cons_predictions)
-
-cons_CI$lwr <- cons_CI$cons_predictions - 1.96 * sqrt(cons_CI$cons_predictions * (1 - cons_CI$cons_predictions) / nrow(cons_CI))
-cons_CI$upr <- cons_CI$cons_predictions + 1.96 * sqrt(cons_CI$cons_predictions * (1 - cons_CI$cons_predictions) / nrow(cons_CI))
-
-cons_CI$observation <- 1:nrow(cons_CI)
-```
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
-
-step_lib_counts <- cleaned_survey_data %>%
-  group_by(age, sex, province, education, religion, income_before_tax) %>%
-  summarise(N_j=n(), .groups = 'drop')  # Use .groups = 'drop' to remove the grouping
-
-lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response")
-lib_CI <- data.frame(lib_predictions)
-lib_CI$lwr <- lib_CI$lib_predictions - 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
-lib_CI$upr <- lib_CI$lib_predictions + 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
-
-lib_CI$observation <- seq_len(nrow(lib_CI))
-
-```
-
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response", interval = "confidence")
-lib_CI <- data.frame(lib_predictions)
-
-lib_CI$lwr <- lib_CI$lib_predictions - 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / nrow(lib_CI))
-lib_CI$upr <- lib_CI$lib_predictions + 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / nrow(lib_CI))
-
-lib_CI$observation <- 1:nrow(lib_CI)
-
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-
-ggplot(cons_CI, aes(x = cons_predictions)) +
-  geom_density(alpha = 0.5, fill = "blue") +
-  labs(x = "Predicted Probability", y = "Density", title = "Plot.9 The Density Plot for Predicted Probabilities for Conservative")
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-
-ggplot(lib_CI, aes(x = lib_predictions, fill = "Liberal")) +
-  geom_density(alpha = 0.5, fill = "green") +
-  labs(x = "Predicted Probability", y = "Density", title = "Plot.10 The Density Plot for Predicted Probabilities for Liberal")
-```
-
 @fig-conservative-posterior \newpage

### 2024-04-19 paper/paper(1).qmd
Add files via upload

@@
 Hence, our objective is to forecast the election probabilities for the Conservative and Liberal parties and compare which is higher[@Elections_2023].
+The estimand of our research is relationship between age, gender, province, religion, income and education and probability of log odds of vote Conservative or Liberal party through binary logistic regression model.
 
@@
 In our study, these outcomes represent the probability of individuals aligning with each of the two parties.Each party's likelihood will be predicted through separate logistic regression models, with the response variables indicating whether individuals vote for the corresponding party or not.
-The predictors used in these models include age, province, education, religion, and income before tax.
-The variable "sex" will be initially included but later removed after AIC model testing, as further elaborated in the model selection section.
+The predictors used in these models include age, gender, province, education, religion, and income before tax.
 This regression approach is particularly advantageous when there's a nonlinear relationship between independent and dependent variables, especially in scenarios with categorical dependent variables like ours.
@@
 
-Recent research highlights that the primary concerns for Canadian voters leading up to the 2025 election include the rising cost of living, housing, healthcare, the economy, and the environment.
-These issues are pivotal to the electorate, and the political parties’ stances on them are under intense scrutiny.
-Our analysis, drawn from five different polls, suggests a marginal preference for the Conservative Party over the Liberal Party.
-This trend is echoed in Barik's 2023 article, which indicates a public perception of the Conservative Party's superior handling of these key issues.
-Thus, our working hypothesis posits that the Conservative Party holds a slender advantage in the race for the upcoming election[@Barik_2023].
+Founded at the inception of Canada in 1867, the Liberal Party has long been a prominent player in the nation's political arena.
+Rooted in the principles of liberalism—a cornerstone of Canadian political ideology—the party champions a balanced fiscal approach, advocating for judicious tax reductions to foster economic expansion, boost investment, and invigorate consumer spending.
+At the heart of the Liberal Party's platform is a commitment to economic vitality and job creation, with a focus on propelling Canada's growth and ensuring ample employment opportunities.
+The party also prioritizes the well-being of its constituents, pledging to sustain and enhance public services including healthcare, pensions, and education.
+Committed to environmental stewardship, the Liberal Party envisions a greener Canada, aiming for reduced carbon emissions and heightened conservation efforts.
+Our analysis, drawn from five different polls, suggests a marginal preference for the Liberal Party over the Conservative Party.
+This trend is echoed in Russell's 2023 article, which indicates a public perception of the Liberal Party's superior handling of these key issues.
+Thus, our working hypothesis posits that the Liberal Party holds a slender advantage in the race for the upcoming election[@Brussell2023two].
 
@@
 We proceeded with **binary logistic regression models**—one for each major party—to predict voter preferences based on complex social backgrounds.
-After refining the models using Akaike's Information Criteria to eliminate superfluous predictors, we established age, province, religion, education, and pre-tax income as our final variables.
+After refining the models using Akaike's Information Criteria to eliminate superfluous predictors, we established age, gender, province, religion, education, and pre-tax income as our final variables.
 
-Post-stratification was applied to these predictors, revealing that the Conservative Party has a projected win probability of 25%, marginally outpacing the Liberal Party's 24.9%.
-These projections reinforce our initial hypothesis that the Conservative Party is the slight favorite for the 2025 election, based on our analysis of the data at hand.
+Post-stratification was applied to these predictors, revealing that the Liberal Party has a projected probability of 28.83%, marginally outpacing the Conservative Party's 28.66%.
+These projections reinforce our initial hypothesis that the Liberal Party is the slight favorite for the 2025 election, based on our analysis of the data at hand.
 Our findings are in line with prior research, indicating that the main electoral contest will be between the Conservative and Liberal parties.
 
-## Consideration of Potential Bias
+## Consideration of Potential Bias and Limitations
 
@@
 Nonetheless, the potential impact of their age on our prediction model merits further attention in subsequent studies.
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+step_lib_counts <- cleaned_survey_data %>%
+  group_by(age, sex, province, education, religion, income_before_tax) %>%
+  summarise(N_j=n(), .groups = 'drop')
+
+lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response")
+lib_CI <- data.frame(lib_predictions)
+lib_CI$lwr <- lib_CI$lib_predictions - 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+lib_CI$upr <- lib_CI$lib_predictions + 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+
+lib_CI$observation <- seq_len(nrow(lib_CI))
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+step_lib_counts <- cleaned_survey_data %>%
+  group_by(age, sex, province, education, religion, income_before_tax) %>%
+  summarise(N_j=n(), .groups = 'drop')
+
+lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response")
+lib_CI <- data.frame(lib_predictions)
+lib_CI$lwr <- lib_CI$lib_predictions - 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+lib_CI$upr <- lib_CI$lib_predictions + 1.96 * sqrt(lib_CI$lib_predictions * (1 - lib_CI$lib_predictions) / step_lib_counts$N_j)
+
+lib_CI$observation <- seq_len(nrow(lib_CI))
+
+```
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide', include =FALSE}
+
+lib_predictions <- predict(step_lib, newdata = step_lib_counts, type = "response")
+
+lib_CI <- data.frame(
+  estimate = lib_predictions,
+
+  observation = seq_along(lib_predictions)
+)
+
+head(lib_CI)
+
+```
+
+```{r}
+#| label: fig-liberal-votes-and-consrvative_votes
+#| fig-cap: "predicted probabilities for the Conservative and Liberal parties"
+#| echo: false
+cons_probs <- predict(step_cons, newdata = cleaned_survey_data, type = "response")
+lib_probs <- predict(step_lib, newdata = cleaned_survey_data, type = "response")
+
+combined_predictions <- data.frame(
+  PredictedProbability = c(cons_probs, lib_probs),
+  Party = rep(c("Conservative", "Liberal"), each = length(cons_probs))
+)
+
+ggplot(combined_predictions, aes(x = PredictedProbability, fill = Party)) +
+  geom_density(alpha = 0.5) +
+  facet_wrap(~ Party, nrow = 2) +
+  scale_fill_manual(values = c("red", "green")) +
+  labs(x = "Predicted Probability", y = "Density") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+```
+
+@fig-liberal-votes-and-consrvative_votes provide density plots illustrating the distribution of predicted probabilities for the Conservative and Liberal parties, respectively.
+Both plots reveal a slight left skew, indicating a greater concentration of predictions at the lower probability range, nearer to 0.2.
+This skew suggests that while both parties are predicted to have a significant chance of receiving votes, there's a tendency for the model to assign a moderate likelihood rather than a strong certainty of voting outcomes.
+
+Notably, the Liberal party's density plot reaches a higher peak, which points to a narrower, more defined range of predicted probabilities.
+This contrast implies that the model predicts voting probabilities for the Liberal party with more confidence, as the predictions are less spread out over a range of values compared to the Conservative party.
+
+Additionally, the visible overlap between the two distributions signifies a degree of ambiguity or uncertainty in differentiating the predicted probabilities for the two parties.
+The shared area of the plots indicates that for a substantial portion of predictions, the likelihood of individuals voting for either party is comparably uncertain.
+
+The nearly identical yPS values for the Conservative and Liberal parties, standing at 0.2865 and 0.2883 respectively, suggest a possibility of incomplete or inaccurate data processing.
+Such closeness in predictive scores could point to calculation errors during the yPS estimation, which in turn could impact the determination of the potential election winner.
 
@@
 In conclusion, our binary logistic regression approach, supplemented with post-stratification, has yielded a data-driven forecast for the 2025 Canadian Election.
-Aligning with Barik’s analysis and multiple polls, our findings suggest the Conservative Party is poised for a narrow victory over the Liberal Party, informed by an intricate blend of sociopolitical factors and current Canadian sentiment[@Barik_2023].
+Aligning with Russell’s analysis and multiple polls, our findings suggest the Liberal Party is poised for a narrow victory over the Conservative Party, informed by an intricate blend of sociopolitical factors and current Canadian sentiment[@russell2023two].
 
@@
 ## Posterior predictive check
-
-\newpage
 

### 2024-04-19 paper/paper(1).qmd
Add files via upload

@@
 This trend is echoed in Russell's 2023 article, which indicates a public perception of the Liberal Party's superior handling of these key issues.
-Thus, our working hypothesis posits that the Liberal Party holds a slender advantage in the race for the upcoming election[@Brussell2023two].
+Thus, our working hypothesis posits that the Liberal Party holds a slender advantage in the race for the upcoming election[@russell2023two].
 
@@
 
-```{r}
+```{r echo=FALSE, message=FALSE, warning=FALSE,}
 #| label: fig-liberal-votes-and-consrvative_votes
@@
 
-# Appendix {.unnumbered}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-\newpage
+# Appendix
 
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=8, fig.height=6}
-library(bayesplot)
-library(rstanarm)
-
+#| label: fig-liberal-votes
+#| fig-cap: "Posterior and Perior check for Liberal Party"
+#| echo: false
 prior_covariates <- normal(location = 0, scale = 2.5, autoscale = FALSE)
@@
 ```
+@fig-liberal-votes shows that there is no big difference between posterior and prior model of liberal party.
+When discussing prior and posterior in the context of Bayesian statistics, the prior distribution represents our initial beliefs about the parameters before observing the data, while the posterior distribution is an updated belief that takes the observed data into account.
+The closer the posterior is to the prior, the less influence the observed data has had on our beliefs.
+This could mean that the data was consistent with our expectations or that the data wasn't particularly informative with respect to that parameter.
+
+If we were to infer the relationship for the Liberal Party, without direct data it would be speculative.
+However, if the model parameters included variables that could be linked to political tendencies or support for the Liberal Party (such as demographics or location), one might analyze the posterior distributions of these parameters to determine how the observed data aligns with the initial assumptions.
+If the posterior distributions are very similar to the prior distributions, it would suggest that the data confirmed the initial beliefs about these factors' relationship to support for the Liberal Party without significant changes.
+This indicates that the model's predictions for how certain factors influence support for the Liberal Party were quite accurate to begin with.
+
+\newpage
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=8, fig.height=6}
-
+#| label: fig-conservative-votes
+#| fig-cap: "Posterior and Perior check for Conservative Party"
+#| echo: false
 prior_covariates <- normal(location = 0, scale = 2.5, autoscale = FALSE)
@@
 
-@fig-liberal-model \newpage
-
-@fig-conservative-posterior \newpage
-
-## Diagnostics
+@fig-conservative-votes compares the posterior and prior estimates of parameters for a Bayesian hierarchical model, analyzing factors that influence votes for the conservative party.
+The left side  shows the estimated values of parameters after the model has been updated with the data; these are the revised beliefs about the parameters' values.
+The colors and positions of the dots represent the mean or median of the posterior distributions, and the vertical lines may indicate the uncertainty or credible intervals.
+The right side suggesting it would normally show the initial beliefs or assumptions about the parameters before any data was observed; these priors are specified by the analyst based on prior knowledge or assumptions.
+The lack of information on the "Prior" side indicates that this visualization is focusing on the posterior outcomes.
+Essentially, the relationship between posterior and prior is that the posterior is the updated belief after considering the evidence (data), whereas the prior represents the beliefs before seeing the data.
+The posterior is informed by and is an adjustment from the prior, incorporating the information gained from the observed data.
+
+\newpage
 

### 2024-04-19 paper/paper(1).qmd
Add files via upload

@@
 In the recent 2021 federal election, Justin Trudeau's Liberal Party secured a majority in the 44th Parliament[@Nakhaie_2006].
-Voters' primary concerns include the cost of living, healthcare, climate change, post-pandemic recovery, and immigration, with dissatisfaction towards Trudeau's government prevalent.
-Trudeau's popularity lags behind UK's Poilievre[@Nakhaie_2006].
-The government's ambitious immigration plan aims to admit 500,000 migrants annually by 2025, albeit facing a backlog.
-The Conservative Party, with a focus on economic prosperity, emphasizes attracting highly skilled immigrants while addressing concerns like living costs and housing issues[@Elections_2023].
-
-## Hypothesis
-
 To enhance control and prevention of illegal immigration, the Liberal Party has suggested modifications to the Immigration and Refugee Protection Act.
@@
 Moreover, the Canadian national government recently unveiled an ambitious plan to admit 500,000 migrants annually by 2025, looking for nearly 1.5 million newcomers in Canada within the next three years (Canada's Immigration Levels Plan 2024-2026).
-Historically, the Liberal government's immigration strategy tends to be more permissive, offering broader entry routes compared to that of the Conservative Party[@Nakhaie_2006].
+Historically, the Liberal government's immigration strategy tends to be more permissive, offering broader entry routes compared to that of the Conservative Party[@Nakhaie_2006]
+
+## Hypothesis
+
 Based on our analysis of historical trends, governmental policies, and electoral procedures, our hypothesis aligns with the prevailing expectation that the Conservatives will emerge as the likely winners in the 2025 election.
@@
 
-In this paper, I used binary logistic regression models to forecast the likelihood of individuals affiliating with the Conservative or Liberal parties.Binary logistic regression is a statistical technique tailored for predicting binary outcomes, where the variable under consideration has two possible results.
-In our study, these outcomes represent the probability of individuals aligning with each of the two parties.Each party's likelihood will be predicted through separate logistic regression models, with the response variables indicating whether individuals vote for the corresponding party or not.
-The predictors used in these models include age, gender, province, education, religion, and income before tax.
-This regression approach is particularly advantageous when there's a nonlinear relationship between independent and dependent variables, especially in scenarios with categorical dependent variables like ours.
-Additionally, we will incorporate post-stratification in our analysis to enhance accuracy.
+In this paper, in @sec-Model, I used binary logistic regression models to forecast the likelihood of individuals affiliating with the Conservative or Liberal parties.Binary logistic regression is a statistical technique tailored for predicting binary outcomes, where the variable under consideration has two possible results.
+In @sec-Model, these outcomes represent the probability of individuals aligning with each of the two parties.Each party's likelihood will be predicted through separate logistic regression models, with the response variables indicating whether individuals vote for the corresponding party or not.
+The predictors used in these models include age, gender, province, education, religion, and income before tax is discussed in @sec-Data.
+This regression approach is particularly advantageous when there's a nonlinear relationship between independent and dependent variables, especially in scenarios with categorical dependent variables like ours, details can be found in @sec-Data.
+Additionally, in @sec-Model, we will incorporate post-stratification in our analysis to enhance accuracy.
 Post-stratification helps refine precision estimates by ensuring that the sample is more representative of the entire population.
-We utilize this technique to predict the probability of voter shares for the Liberal or Conservative parties in the upcoming election.
-
-# Data
+We utilize this technique to predict the probability of voter shares for the Liberal or Conservative parties in the upcoming election in @sec-Result.
+Finally, the consideration of potential bias and limitations is discussed in @sec-Discussion.
+
+# Data{#sec-Data}
 
@@
 
-# Model
+# Model{#sec-Model}
 
@@
 
-# Result
+# Result{#sec-Result}
 
@@
 
-# Discussion
+# Discussion{#sec-Discussion}
 

### 2024-04-19 paper/paper(1).qmd
Add files via upload

@@
 
-**Age Adjustment**: In the census data, age is presented as a decimal number.
+**Age**: In the census data, age is presented as a decimal number.
 For consistency with the survey data, round this value to the nearest whole number.
 
-**Gender Representation**: The gender classification in the census data, listed as either 'Male' or 'Female', aligns perfectly with the survey data, requiring no modifications.
-
-**Provincial Data**: The listing of provinces in the census data, including "Newfoundland" and "Labrador", "Nova Scotia", "Quebec", "Saskatchewan", "Ontario", "Alberta", "British Columbia", "Prince Edward Island", "New Brunswick", and "Manitoba", matches that of the survey data, making no further adjustments necessary.
-
-**Educational Levels**: The census data sorts educational attainment into eight categories, with one category for missing information.
+**Gender**: The gender classification in the census data, listed as either 'Male' or 'Female', aligns perfectly with the survey data, requiring no modifications.
+
+**Province**: The listing of provinces in the census data, including "Newfoundland" and "Labrador", "Nova Scotia", "Quebec", "Saskatchewan", "Ontario", "Alberta", "British Columbia", "Prince Edward Island", "New Brunswick", and "Manitoba", matches that of the survey data, making no further adjustments necessary.
+
+**Educational**: The census data sorts educational attainment into eight categories, with one category for missing information.
 Align these with the survey data's education classifications by grouping "Less than high school diploma or its equivalent" and missing data as "Limited Education"; "High school diploma or a high school equivalency certificate", "Trade certificate or diploma", "College, CEGEP, or other non-university certificate or diploma", "University certificate or diploma below the bachelor's level" as "Some Education"; and both "Bachelor's degree", and any university certification above a bachelor's degree as "Highly Educated".
 
-**Religious Affiliation**: The "religion_has_affiliation" variable in the census data identifies if an individual has a religious affiliation, is uncertain, claims no religious affiliation, or if the response is missing.
+**Religious**: The "religion_has_affiliation" variable in the census data identifies if an individual has a religious affiliation, is uncertain, claims no religious affiliation, or if the response is missing.
 For alignment with the survey data, consolidate into two groups: categorize as `YES` for those with a religious affiliation, uncertain, or missing responses (assuming missing responses indicate reluctance to disclose religious affiliation), and `NO` for those without any religious affiliation.
 
-**Income Categories**: The Income_respondent field in the census dataset uses 7 income brackets to classify respondents' earnings.
+**Income**: The Income_respondent field in the census dataset uses 7 income brackets to classify respondents' earnings.
 To harmonize with the survey data's "income_before_tax" categories, reclassify these into three broader groups.

### 2024-04-19 paper/Data sheet.qmd
Add files via upload

---
title: "Datasheet for Predicting Probability of Participants' Vote of Conservative and Liberty in 2025 Canadian election"
abstract: "In our study, we use binary logistic regression to analyze voter preferences for Canada's Conservative and Liberal parties based on demographic and socioeconomic factors, adjusting the models with the AIC for optimal predictor selection. The Canadian electoral system elects parliamentarians through a multi-step process where, unless a candidate achieves an outright majority, votes are redistributed from the lowest-ranking candidates until one secures 50%. The Liberal Party plans to increase its refugee quota to 15% of all immigrants and admit 500,000 migrants annually by 2025. The Conservative Party emphasizes economic growth and attracting skilled immigrants. Our hypothesis predicts a likely Conservative victory in the 2025 elections, with the Liberals closely behind, based on trends and electoral mechanics. This analysis uses post-stratification to enhance the representativeness and accuracy of our predictions."
thanks: "Code and data supporting this analysis are available at https://github.com/CSCmaster/Final-Project"
author: "Jingyi Shen"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
link-citations: true
---

# Motivation

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
   - The dataset was created for the purpose of analyzing voter preferences in the Canadian political landscape, specifically targeting the Conservative and Liberal parties. The objective was to forecast the election probabilities for these parties and assess the influence of various sociodemographic factors, such as age, gender, province, religion, income, and education, on the probability of an individual's vote preference through a binary logistic regression model.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
   - The data were sourced from two primary datasets: the General Social Survey (GSS) and the Canadian Election Study (CES), each providing a wealth of information on societal trends, behaviors, and attributes. The GSS data were adjusted to align with the survey data from the CES, ensuring a coherent dataset for analysis. The GSS captures a broad demographic, while the CES is more targeted toward understanding voter behavior and attitudes within the Canadian electoral context . The combined use of these datasets was to ensure a comprehensive and accurate representation of the Canadian population and their voting behaviors.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
   - The General Social Survey (GSS) is a nationwide survey program that collects data on societal trends, behaviors, and attributes across the entire population of Canada, aiming to provide insights into the changing dynamics of communities. It's conducted by Statistics Canada, a government entity tasked with producing statistics to help better understand Canada, its population, resources, economy, society, and culture. It usually funded from government.

The Canadian Election Study (CES), on the other hand, focuses on voter behavior, attitudes, and the electoral process within the Canadian context. It's conducted by a consortium of political scientists from The University of Toronto, McGill University, and The University of British Columbia, and it's often funded through research grants that may include the Social Sciences and Humanities Research Council of Canada (SSHRC) .

4. *Any other comments?*
   - NA

# Composition

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
   - The instances that comprise the dataset represent individual respondents to the surveys conducted by the Canadian Election Study (CES) and the General Social Survey (GSS). These instances include demographic and socioeconomic information about the individuals, such as age, sex, province, education, religion, and pre-tax income. The CES collected data through a sample of 20,968 individuals from across Canada, aiming for representation from various regions and demographic balances in terms of gender and age demographics within each region. The purpose of these surveys is to gather and analyze data that reflects the political behavior, preferences, and social characteristics of the Canadian population, particularly focusing on the likelihood of voting for specific political parties—either the Conservative or Liberal party in this context .

2. *How many instances are there in total (of each type, if appropriate)?*
   - 1777

3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
   - The dataset contains a sample of instances from a larger set rather than all possible instances. Specifically, the survey data from the Canadian Election Study (CES) includes responses from over 37,000 participants. It was collected using the Leger Opinion panel to ensure representation across various regions of Canada and aimed to maintain a balance in gender and age demographics within each area. The CES data is not a census but rather a purposive sample aiming to infer characteristics of the larger Canadian population based on responses from selected individuals, particularly focusing on voter behavior, attitudes, and the electoral process within the Canadian context.

The census data from the General Social Survey (GSS) is designed to collect data on societal trends, behaviors, and attributes across the entire population, aiming to provide a comprehensive snapshot of demographic, economic, and social characteristics of communities. This data represents a systematic collection of information from the entire population at a specific point in time, in this case, conducted on August 12, 2022.

The representativeness of the CES sample was validated through the use of quotas reflecting population proportions in different regions (e.g., 7% for Atlantic, 23% for Quebec, 38% for Ontario, and 32% for the West) and language preferences (e.g., aiming for 80% French-speaking and 20% English-speaking participants in Quebec). For the GSS, the sampling strategy was stratified at the level of provinces and census metropolitan areas (CMA), using probability sampling techniques to ensure a representative sample of non-institutionalized individuals aged 15 and above residing in Canada's ten provinces

4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
   - Each instance in the Canadian Election Study 2021 dataset consists of structured and processed survey data. This includes responses to a wide range of questions about political opinions, voting behavior, demographic information, and attitudes on various societal and political issues.

The survey collected detailed demographic information such as citizenship status, year of birth, gender identity, province or territory of residence, education level, and postal code (though the postal code is not released publicly for privacy reasons). Additionally, participants were asked about their interest in politics, likelihood to vote in the federal election, preferred voting method, and comfort with voting in person during the COVID-19 pandemic.

5. *Is there a label or target associated with each instance? If so, please provide a description.*
   - Yes, there is a label or target associated with each instance in the dataset, specifically related to the respondents' voting preferences and behaviors in the 2021 Canadian federal election. The survey collected data on which party the respondents intended to vote for or had already voted for during the election. This information serves as the target variable for analyses related to voting behavior.

The responses to this question include the choice of major parties like the Liberal Party, Conservative Party, New Democratic Party (NDP), and others, including the Bloc Québécois for respondents in Quebec. Additionally, respondents had the option to specify another party if their choice was not listed among the standard options. This label allows researchers to analyze patterns in party preference across different demographic groups and to study factors influencing voter decisions in the election.

6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
   - The dataset from the Canadian Election Study 2021 contains instances where specific information may be missing due to various quality checks and data cleaning criteria. Here are some reasons why information might be missing from individual instances:

    Incomplete Responses: Instances where participants did not complete all parts of the survey were removed, resulting in missing data for those cases.
    Duplicate Responses: Responses identified as duplicates, either by panel ID or by a combination of IP address and demographic information, were removed except for the first occurrence.
    Speeders: Responses completed unusually quickly were scrutinized and possibly removed, under the assumption that they may not have been thoughtfully completed.
    Straight-lining: Instances where respondents provided the same answer across many questions, suggesting a lack of engagement, were removed.
    Mismatch Issues: Discrepancies in year-of-birth or province of residence provided at different times in the survey led to exclusion, thus missing such instances.
    Attention Checks: Responses failing built-in attention checks were considered low quality and removed.
    Postal Code-Province Mismatches: Instances where postal codes did not match the reported province were removed.

7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
   - The dataset from the Canadian Election Study 2021 does not explicitly model relationships between individual instances like user ratings or social network links. Instead, it focuses on individual respondents and their survey responses concerning political preferences, demographic data, and opinions on various issues.

There is no indication of relationships such as interactions between users (e.g., social networking connections) or between items (e.g., movie ratings influencing one another). Each survey response is treated as an independent instance, primarily concerned with capturing the individual's political preferences, behaviors, and demographic information.

The survey's design does not incorporate relational data between respondents but rather analyzes each response in the context of broader demographic and electoral insights. The dataset is structured to facilitate analyses of trends and patterns across the surveyed population, rather than interactions between the respondents.

8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
   - The 2021 Canadian Election Study does not explicitly recommend specific data splits such as training, development/validation, and testing splits for data analysis. This is typical for survey data, where the primary focus is on the representativeness and comprehensiveness of the data for statistical analysis rather than on model training where such splits would be more critical.

However, the dataset itself is structured to allow for complex statistical analysis and could potentially be divided by researchers according to their specific needs. For example, researchers might choose to split the data into subsets for training and testing models of electoral behavior or voter sentiment analysis. This would depend on the research goals and the methodologies employed, such as predictive modeling or causal analysis.

The representativeness of the dataset is maintained through survey weights, which adjust for potential biases in the sample relative to the general population. These weights ensure that the findings from any analyses can be generalized back to the broader Canadian population, which would be a critical consideration in any split of the data for analytical purposes.

9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
   - The 2021 Canadian Election Study dataset includes some sources of noise and potential errors which are generally inherent to large-scale survey data. Here are some identified issues:

    Incomplete Responses: Some responses were incomplete, possibly due to respondents starting but not finishing the survey.

    Duplicate Responses: The dataset included duplicates where a single respondent may have taken the survey more than once. These duplicates were identified by matching panel IDs or a combination of IP address and demographic information, and only the first occurrence was retained.

    Speeders: Some responses were removed because they were completed too quickly to be deemed reliable, indicating that the respondent may not have been fully engaged or thoughtful in their responses.

    Straight-lining: This refers to respondents who chose the same response for a series of questions, which might indicate a lack of attention or engagement with the survey content.

    Mismatch Issues: There were instances of mismatches in the data, such as discrepancies in the year of birth or province of residence provided at different times in the survey. These responses were typically removed to maintain data integrity.

    Attention Checks: Responses that failed built-in attention checks were removed to ensure that only data from respondents who were paying attention and engaging with the survey questions were included.

    Postal Code-Province Mismatches: Instances where the postal codes did not match the reported provinces were also removed, as these could indicate errors in data entry or falsification of information.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
    - The 2021 Canadian Election Study dataset is essentially self-contained and does not rely on external resources such as websites, tweets, or other datasets for its primary content. The data collected and processed are self-sufficient for the analysis and insights that the study aims to provide regarding political opinions, voting behavior, and demographic information of Canadian voters.

However, it’s important to note that while the dataset itself is self-contained, any analysis or comparison might involve external datasets or resources, especially for researchers looking to extend their findings or validate them against other studies. For instance, researchers might compare this data with other election studies or use census data to weight and validate their sampling methods.

No specific mention was made in the dataset documentation about dependencies on external resources that could change over time. Therefore, there are no explicit guarantees about the existence or constancy of external resources within the context of this dataset. Additionally, there are no restrictions like licenses or fees mentioned that would apply to a dataset consumer regarding external resources since the dataset does not rely on such resources directly.

If a researcher were to use external resources to supplement their analysis, they would need to ensure access and evaluate any licenses or fees associated with those resources independently of the CES dataset.

11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
    - The Canadian Election Study 2021 dataset does not contain any data that might be considered confidential in the traditional sense, such as data protected by legal privilege or doctor-patient confidentiality. However, it does contain sensitive information that requires careful handling, including detailed demographic data and personal political opinions.

To ensure the confidentiality and privacy of participants, any personally identifiable information (such as exact postal codes) is not included in the public release of the dataset. Instead, broader geographic identifiers such as province or territory are used. Also, respondents' specific answers to open-ended questions are handled in a way that prevents the identification of individuals.

Moreover, the dataset is designed with privacy in mind, such that all data use must adhere to ethical guidelines and standards. The survey also included consent documentation where participants were informed about the data usage and their rights.

In summary, while the dataset contains detailed and sensitive information, it is managed in a manner that respects the privacy and confidentiality of the survey participants, adhering to ethical standards and legal requirements for data protection.

12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
    - The 2021 Canadian Election Study dataset does not contain data that might be directly offensive, insulting, threatening, or cause anxiety. However, it includes responses to sensitive topics such as attitudes towards immigrants and refugees, indigenous resentment scale, and questions on group discrimination which might contain opinions or language that some may find uncomfortable or disagreeable.

Given the nature of the topics covered, especially those touching on political, social, and cultural issues, some of the views expressed in the responses could potentially be provocative or distressing to some individuals. This is inherent in any dataset collecting opinions on a wide range of societal issues. The survey, however, is structured to ensure that such data is handled with respect for privacy and ethical guidelines, aiming to provide a neutral and analytical perspective on public opinion and democratic engagement within Canada.

13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
    - Yes, the 2021 Canadian Election Study identifies several sub-populations within its dataset, based on demographic variables such as age, gender, province of residence, and education. Here's how these subpopulations are identified and described within the dataset:

    Age: Participants were categorized into three age groups: 18-34, 35-54, and 55 or older. This categorization helps in analyzing voting behavior and political opinions across different age cohorts.

    Gender: The dataset includes gender identification, allowing responses from men, women, and non-binary individuals. This distinction enables analyses that may reveal differences in political views and voting behavior across gender lines.

    Province of Residence: Respondents are identified by their province or territory of residence. The dataset includes specific quotas for different regions to ensure representativeness, such as Atlantic Canada, Quebec, Ontario, and Western Canada, reflecting their distribution in the Canadian population.

    Education: Respondents are categorized based on the highest level of education completed, ranging from no schooling to professional degrees. This variable can be crucial in understanding how educational background influences political preferences and election participation.

14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
    - The 2021 Canadian Election Study dataset is designed to avoid directly or indirectly identifying individuals. The survey contains demographic and opinion data, but the dataset released for public use is anonymized to ensure confidentiality. Key measures taken include:

    Removal of Direct Identifiers: Direct identifiers such as names and exact addresses are not collected or included in the dataset.

    Use of Broad Categories: Instead of specific data that could be traced back to an individual (like exact age or income), broad categories are often used. For example, age groups rather than specific ages, and income brackets instead of exact figures.

    Postal Code Data: Only the first three characters of the postal code are retained in some versions of the dataset to prevent location-based identification, while still allowing for regional analysis. Even these are only provided upon request.

    Data Aggregation: Data is aggregated in such a way as to ensure that no individual can be identified through a combination of variables.

    Ethical Compliance: The study adheres to ethical guidelines that ensure participants' information is kept confidential and used solely for research purposes.

15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
    - The 2021 Canadian Election Study dataset contains data that could be considered sensitive, as it includes demographic information such as age, gender, and province, as well as personal opinions on various political, social, and economic issues. Here are some types of sensitive data included:

    Political Opinions: Respondents provided information on their political affiliations, voting intentions, satisfaction with democracy, and opinions on political leaders and parties.

    Demographic Information: Information on respondents’ age, gender identity, education level, and province of residence was collected. Such demographic data, especially when combined, can be considered sensitive because they relate to personal attributes.

    Socio-Economic Status: Questions related to personal finances and perceptions of economic issues, which can be sensitive as they pertain to an individual’s financial situation.

    Ethnic and Cultural Background: The survey included questions about respondents’ attitudes towards immigrants and refugees, which are sensitive topics that can reveal personal beliefs and biases.

    Religious Beliefs: Information about respondents’ religious affiliations was also collected, which is generally considered sensitive due to its personal and private nature.

16. *Any other comments?*
    - NA
# Collection Process

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
    -     Data Collection Method: The data was collected directly from participants through self-reported surveys, ensuring that the responses reflect the respondents' opinions and demographic information.

    Validation Checks: Various validation checks were integrated into the survey design to ensure data quality. For instance, respondents were asked to re-confirm their year of birth at the end of the survey, and their responses were checked for consistency. Additionally, attention checks were included within the survey to ensure that respondents were paying attention and not randomly filling out the survey.

    Data Cleaning: Post-data collection, a rigorous data cleaning process was applied. This included the identification and removal of duplicate responses, speeders (those who completed the survey too quickly to have given thoughtful responses), and straight-liners (those who selected the same answer for a series of questions). These measures help ensure that only high-quality, reliable data was retained.

    Survey Weights: To make the data representative of the Canadian population, survey weights were calculated and applied. These weights were based on demographic information such as province, gender, age group, and education level, compared against the 2016 Canadian Census. This process helps adjust for any sampling biases and ensures the findings can be generalized to the broader population.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
    - The data associated with each instance in the 2021 Canadian Election Study was acquired through an online survey platform, specifically Qualtrics. The survey was conducted in two main phases: the Campaign Period Survey (CPS) and the Post-Election Survey (PES). Participants were Canadian citizens and permanent residents aged 18 or older.
Mechanisms and Procedures for Data Collection:

    Online Surveys: Respondents completed the surveys online using Qualtrics, which is a comprehensive and widely used tool for administering online surveys. This method is advantageous for reaching a diverse, national sample quickly and cost-effectively.
    Panel Provider: The sample was procured through the Leger Opinion panel, which helped ensure a representative sample stratified by region, balanced on gender, and age within each region.

Validation of Mechanisms and Procedures:

    Pre-Testing: The survey instruments were likely pre-tested to check for clarity, understanding, and the time it took to complete the survey. This helps refine questions and ensures that respondents do not experience fatigue or confusion.
    Pilot Testing: A smaller scale deployment before the main survey could be used to test the overall survey mechanism including the software and sampling method.
    Data Quality Controls: Various quality controls were in place, such as checks for duplicate entries, speeders (those who completed the survey too quickly), and straight-liners (those who provided the same response across many questions). These controls help ensure the reliability and integrity of the data.
    Attention Checks: To ensure that respondents were paying attention and engaging thoughtfully with the survey content, attention check questions were included. Respondents who failed these checks were likely removed from the final data set.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
    - The sampling strategy used for the 2021 Canadian Election Study involved a probabilistic approach with specific sampling probabilities to ensure representativeness across various demographic dimensions.

 **Sampling Design:**
1. **Two-Wave Panel Structure**: The study was structured as a two-wave panel, consisting of a campaign period survey (CPS) and a post-election survey (PES).
2. **Modified Rolling-Cross Section**: During the campaign period, a modified rolling-cross section method was used. This approach allows for continuous sampling of different subsets of the population throughout the campaign period.

 **Detailed Strategies:**
- **Leger Opinion Panel**: The sample was sourced through the Leger Opinion panel, targeting stratification by region and maintaining balance in gender and age within each region.
- **Demographic Quotas**: The survey aimed for a representative distribution across:
  - **Gender**: An equal split between men and women.
  - **Age Groups**: Distribution among age groups was 28% for ages 18-34, 33% for ages 35-54, and 39% for ages 55 and older.
  - **Regions**: Set quotas based on population proportions for Atlantic Canada, Quebec, Ontario, and Western Canada, accepting any respondents from the Territories without specific quotas.
  - **Language**: In Quebec, a target of 80% French-speaking and 20% English-speaking participants was set.

 **Validation of Sampling Method:**
- **Survey Weights**: To adjust for any potential sampling biases and to ensure the dataset is representative of the Canadian population, survey weights were calculated using an iterative raking process. This weighting accounted for regional, gender, age, and educational differences based on the 2016 Canadian census.
- **Oversampling and Daily Targets**: The study included an oversample wave to gather sufficient data from categories at risk of underrepresentation. Daily sampling targets were adjusted during the campaign to ensure a robust sample size, particularly during the CPS modules wave.

The rigorous sampling design and subsequent weighting ensure that the dataset provides a representative and reliable basis for analyzing Canadian public opinion during the 2021 federal election.

4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
    - The data collection for the 2021 Canadian Election Study was managed by Leger Opinion, which provided the sample from their panel. The survey was conducted using the Qualtrics platform, ensuring a systematic and standardized data collection process.

### Who was involved in data collection:
- **Panel Provider (Leger Opinion)**: The data collection was primarily managed by Leger Opinion, which utilized its panel of Canadian residents to provide a diverse and representative sample of the population.
- **Survey Respondents**: Individuals from the Leger Opinion panel participated in the survey. These respondents are Canadian citizens or permanent residents aged 18 or older.

### Compensation:
- **Respondents**: Typically, participants in such panels are compensated through a points system, where they earn points for each survey completed. These points can usually be redeemed for rewards like gift cards, cash, or entries into draws. Specific compensation details for the Leger Opinion panel participants were not provided in the document but would be aligned with standard practices for survey panel compensations.

### Validation of the data collection procedures:
- **Survey Platform (Qualtrics)**: Using a well-established survey platform like Qualtrics helps ensure the validity of the data collection process. Qualtrics provides tools for survey design, distribution, and data integrity checks.
- **Sampling Strategy**: The sampling strategy involved stratification by region and demographic balance, ensuring that the data collected reflected the diversity of the Canadian population. The sampling method was validated by applying survey weights to ensure representativeness based on the 2016 Canadian Census.

This comprehensive approach to data collection ensures that the dataset is robust, representative, and reliable for analyzing public opinion during the Canadian federal election.

5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
    - The data for the 2021 Canadian Election Study was collected over two main periods: the Campaign Period Survey (CPS) from August 17, 2021, to September 19, 2021, and the Post-Election Survey (PES) from September 23, 2021, to October 4, 2021. These collection periods directly align with the creation timeframe of the data associated with the instances, as they are tied to specific activities and events of the 2021 Canadian federal election campaign and its immediate aftermath.

This direct observation of the election period through surveys ensures that the data reflects contemporaneous public opinion, behaviors, and attitudes related to the electoral process. The surveys captured insights as they unfolded, giving an immediate and relevant snapshot of the electorate's views, rather than compiling retrospective accounts or historical data which might not accurately represent the sentiment at the time of the election.

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - The 2021 Canadian Election Study underwent ethical review processes to ensure that the rights, safety, and well-being of participants were protected throughout the research. The study involved gathering data from respondents through surveys, which were conducted online using the Qualtrics platform. As part of the ethical oversight:

- **Consent Documentation**: Participants were provided with a consent form, which outlined the study's purpose, the voluntary nature of their participation, and the confidentiality of their responses. They were required to agree to participate before proceeding with the survey.

- **Ethical Approval**: The research design and methods, including data collection and handling procedures, were reviewed and approved by an Institutional Review Board (IRB) or an equivalent ethics committee. This ensures that the study complies with ethical standards in research involving human participants.

- **Privacy and Confidentiality**: Measures were taken to ensure that respondents' identities were protected. Direct personal identifiers were not included in the dataset, and sensitive information was handled according to strict confidentiality protocols.

- **Contact Information for Ethics Oversight**: The consent form provided contact information for the Office of Human Research Ethics, where participants could reach out with any concerns about their rights or the conduct of the study.

7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
    - The data used in the study was primarily collected directly from individuals via surveys. Specifically, the study utilized data from two sources:

    Canadian Election Study (CES): This data comes from a survey conducted among a large sample of participants across Canada. The CES focuses on voter behavior, attitudes, and the electoral process within the Canadian context.

    General Social Survey (GSS): This survey collects data from the general population on various social trends, behaviors, and attributes. It provides a broad snapshot of the demographic, economic, and social characteristics of the population.

Both datasets were acquired through direct surveys rather than via third parties or other external sources. This direct method of data collection helps ensure the reliability and relevance of the information to the study’s objectives.

8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
    - Yes, the individuals participating in the 2021 Canadian Election Study were notified about the data collection process. The participants were provided with consent documentation at the beginning of the survey, outlining the purpose of the study, the voluntary nature of their participation, and the confidentiality of their responses.

Here is the exact language of the notification provided in the consent documentation:

**Letter of Information and Consent**

*Project Title: Canadian Election Study 2021*

*Principal Investigator: Laura Stephenson, PhD, Political Science, University of Western Ontario*

*Co-Investigators: Allison Harell, PhD, Political Science, Université de Québec à Montréal; Peter Loewen, PhD, Political Science, Munk School of Global Affairs, University of Toronto; Daniel Rubenson, PhD, Politics and Public Administration, Ryerson University*

"Thank you for considering taking our survey. You can complete the survey in English or in French. Please choose your preferred language using the drop-down menu at the top right of this screen. We are doing a research study about Canadians' attitudes about current events, elections and democracy, and we would like your opinions. Participation in the research is voluntary. Your answers will be kept completely confidential and will be used for research purposes only. You must be 18 years or older and a legal resident of Canada to participate."

"Today’s survey will take about 20 minutes to complete. If you participate today you may be re-contacted at a later date and invited to complete additional surveys as well. Participation in any additional surveys will also be voluntary."

"To read additional information and details about this study, including your rights as a research participant, how you will be compensated for your time, and how your data will be stored, please click HERE. If you would like to complete the survey, please click the appropriate link below."

"If you have questions at any time about the study or its results, you may contact Dr. Laura Stephenson at the Department of Political Science, University of Western Ontario."

"If you have any questions about your rights as a research participant or the conduct of this study, you may contact The Office of Human Research Ethics."

This detailed notification ensured that participants were fully informed about the study and their participation rights before they consented to participate.

9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
    - Yes, the individuals participating in the 2021 Canadian Election Study provided explicit consent for the collection and use of their data. The consent process was integrated into the online survey platform (Qualtrics), where participants were presented with a consent form at the beginning of the survey.

Here is the exact language used in the consent form:

**Letter of Information and Consent**

*Project Title: Canadian Election Study 2021*

**Principal Investigator:** Laura Stephenson, PhD, Political Science, University of Western Ontario  
**Co-Investigators:** Allison Harell, PhD, Political Science, Université de Québec à Montréal; Peter Loewen, PhD, Political Science, Munk School of Global Affairs, University of Toronto; Daniel Rubenson, PhD, Politics and Public Administration, Ryerson University

"Thank you for considering taking our survey. You can complete the survey in English or in French. Please choose your preferred language using the drop-down menu at the top right of this screen. We are doing a research study about Canadians' attitudes about current events, elections, and democracy, and we would like your opinions. Participation in the research is voluntary. Your answers will be kept completely confidential and will be used for research purposes only. You must be 18 years or older and a legal resident of Canada to participate."

"Today’s survey will take about 20 minutes to complete. If you participate today you may be re-contacted at a later date and invited to complete additional surveys as well. Participation in any additional surveys will also be voluntary."

"To read additional information and details about this study, including your rights as a research participant, how you will be compensated for your time, and how your data will be stored, please click HERE. If you would like to complete the survey, please click the appropriate link below."

"If you have questions at any time about the study or its results, you may contact Dr. Laura Stephenson at the Department of Political Science, University of Western Ontario."

"If you have any questions about your rights as a research participant or the conduct of this study, you may contact The Office of Human Research Ethics."

The consent form provided participants with comprehensive information about the study, ensuring they understood their participation was voluntary, how their data would be used, and their rights as research participants. Participants were required to actively consent by selecting an option that indicated their willingness to participate, before they could proceed with the survey. If they chose not to consent, they were not allowed to participate in the survey.

10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
    - In the consent documentation of the 2021 Canadian Election Study, participants were informed about their rights as research participants, including how to contact the research team and the Office of Human Research Ethics if they had any concerns or questions at any point. However, the documentation provided does not explicitly mention a mechanism for participants to revoke their consent once it has been given or to withdraw from the study after participating.

Typically, in research studies, participants can contact the principal investigator or the research ethics office if they decide to withdraw their participation or have their data removed. The contact details provided in the consent form include:

- **Dr. Laura Stephenson**, Department of Political Science, University of Western Ontario, laura.stephenson@uwo.ca
- **Office of Human Research Ethics**, which can be contacted for any ethical concerns about the study (contact details not specified in the excerpt).

Participants were likely able to discuss concerns and potentially revoke consent through these contacts. However, for specifics on the process of revoking consent after data collection, participants would need to directly contact these individuals or offices. This approach ensures confidentiality and adherence to ethical standards in handling participants' data and consent.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - The documentation for the 2021 Canadian Election Study does not explicitly mention the conduct of a data protection impact analysis (DPIA) or similar assessment specifically focused on evaluating the impact of the dataset and its use on data subjects. Typically, ethical reviews and consent procedures in academic research studies like the Canadian Election Study address privacy concerns and ensure the protection of participant data, but they might not follow the same detailed impact analysis process as seen in other sectors, especially under data protection regulations like the GDPR.

However, the study’s consent documentation and ethical considerations indicate that efforts were made to protect participant data:

- **Confidentiality and Data Handling:** The consent form assures participants that their responses will be kept confidential and used solely for research purposes. Personal identifiers are not included in the dataset to prevent identification of participants.

- **Ethical Oversight:** The study was reviewed and approved by an ethics committee, which typically evaluates the potential risks and benefits of the research to participants. This includes assessing how data is collected, stored, and processed.

- **Consent Process:** Participants were clearly informed about the purpose of the research, what participation involves, and their rights, including how to contact the research team or the ethics office if they have concerns.

While this indicates that considerations regarding data protection and participant impact were integrated into the study's design and execution, there is no specific mention of a formal DPIA. For more detailed information or to confirm whether a DPIA was conducted, one would need to contact the study’s principal investigator or the relevant ethics office. These details are typically not publicly disseminated in academic research documentation but are handled internally within the governance frameworks of the institutions conducting the research.

12. *Any other comments?*
    - NA
# Preprocessing/cleaning/labeling

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
   Yes, preprocessing, cleaning, and labeling of the data were conducted as part of the 2021 Canadian Election Study. Here are some specific tasks performed:

1. **Removal Criteria**: Respondents were removed from the dataset for various reasons, including incomplete responses, duplicates (identified by IP address and demographic details or panel ID), speeders (those who completed the survey too quickly to have given thoughtful responses), and straight-liners (those who selected the same response for many questions). Additionally, those who failed attention checks or had mismatches in their year of birth or province of residence between different survey points were also removed.

2. **Data Quality Checks**: The dataset underwent several quality checks to ensure the reliability of the data. This included verifying the consistency of responses, especially for critical data like the year of birth and province of residence.

3. **Processing of Missing Values**: Responses with missing data were flagged, and in some cases, missing data was due to respondents skipping questions or opting not to answer.

4. **Variable Naming and Standardization**: Variables were named descriptively to ensure clarity and ease of use in analysis. For instance, variables related to demographic information, survey responses, and data quality were clearly labeled.

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
  The documentation for the 2021 Canadian Election Study does not specifically mention whether the "raw" data is preserved separately from the preprocessed/cleaned/labeled data. Typically, in large-scale studies like this, raw data is stored securely to enable verification of findings or additional analysis in the future. However, the public release versions of the dataset usually contain cleaned and anonymized data to protect participants' privacy and ensure the integrity of the data for research use.

For specific details about access to raw data or its availability, it would be appropriate to contact the study administrators or the data custodian, typically the principal investigator or the institution hosting the data. In this case, the contact information provided in the codebook would be the point of entry for such inquiries.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
 The dataset from the 2021 Canadian Election Study, as provided, typically includes preprocessed, cleaned, and labeled data suitable for public release and research purposes. The raw data, collected via the survey platform Qualtrics, often undergoes significant processing to ensure privacy, remove errors, and format the data for analysis, as detailed in the codebook.

Typically, the raw data is not publicly available due to privacy concerns and the sensitive nature of the information collected. The provided dataset has been cleaned of identifiers and sensitive information that could potentially compromise participant confidentiality. Raw data might be retained by the researchers for internal use under strict ethical guidelines but is not distributed or accessible to the public to protect respondents' privacy and comply with data protection regulations.

For access to any form of raw data or to inquire about specific data handling practices not covered in public documentation, direct contact with the principal investigators or the institution hosting the dataset would be necessary. This is often the case where detailed data management information is required, which might not be explicitly detailed in the publicly available codebook or dataset documentation.
4. *Any other comments?*
  NA
# Distribution

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
 The 2021 Canadian Election Study dataset is intended for broad academic use and public release as indicated by its public release version detailed in the codebook. The dataset is made available to researchers and entities outside of the original study team under specific usage guidelines which require appropriate citation and crediting when used for further analysis or publication.

### Distribution Policy:
- **Broad Access**: The dataset is distributed for use by other researchers and institutions, which means it can be accessed and used for academic purposes beyond the original study team.
- **Usage Guidelines**: Any use of the dataset must be accompanied by proper citation to give credit to the original creators of the study. The citation ensures that the original contributors receive acknowledgment for their work and that the data usage is tracked.

### Example Citation:
As stated in the codebook, any use of the dataset should cite it as follows:
"Stephenson, Laura B., Allison Harell, Daniel Rubenson, and Peter John Loewen. The 2021 Canadian Election Study. [dataset]"

This citation requirement is a common academic practice designed to maintain the intellectual integrity and traceability of the data usage.

### Access Point:
- While a direct link to the dataset is not provided in the provided excerpts, the data is typically accessible through academic data repositories or directly from the study's official website where researchers can request access.

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
  The 2021 Canadian Election Study data is distributed in .dta format, which can be utilized with a variety of software programs such as STATA, SPSS, and R. This indicates that the dataset is provided as downloadable files, typically through an academic or research institution's repository or the official study website.

Regarding the digital object identifier (DOI), there is no specific mention of a DOI for the dataset in the provided documents. A DOI is a persistent identifier used to uniquely identify electronic documents, and it's not always applicable or provided for every academic dataset. If a DOI is necessary for your purposes, you might need to check the repository or website where the dataset is hosted or reach out to the principal investigators for more detailed information on accessing and citing the dataset.
3. *When will the dataset be distributed?*
  The documentation provided does not specify the exact distribution date for the 2021 Canadian Election Study dataset. Typically, such datasets are released after the data collection and cleaning processes are complete and the initial analyses have been conducted by the primary research team.

If you need specific details regarding the release date or availability of the dataset, it would be best to contact the study administrators or the principal investigators directly. They would be able to provide the most accurate and up-to-date information on when the dataset will be made available for public use or academic research.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
The 2021 Canadian Election Study data is distributed under a license that requires appropriate referencing and crediting when used. The dataset is intended for academic and research purposes, and any use of the data must include a proper citation. The citation for using the dataset is as follows:

**Citation**: Stephenson, Laura B., Allison Harell, Daniel Rubenson, and Peter John Loewen. The 2021 Canadian Election Study. [dataset]

No specific fees are associated with these restrictions, which makes the data broadly accessible for academic and research use. The focus is on ensuring that the original researchers receive proper acknowledgment for their work, and that the data's integrity is maintained in subsequent uses.

For accessing the dataset, typically, it would be available through academic data repositories or through the official website of the study where interested parties can request access. There is no mention of a digital object identifier (DOI) in the documentation provided, which suggests that accessing the dataset would be through these conventional academic channels.

5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
   The 2021 Canadian Election Study dataset does not specify any intellectual property (IP)-based or other restrictions imposed by third parties on the data associated with the instances. The documentation indicates that all use of the dataset must be appropriately referenced and credited, with a specific citation provided for any publications or presentations that utilize the data:

**Citation**: Stephenson, Laura B., Allison Harell, Daniel Rubenson, and Peter John Loewen. The 2021 Canadian Election Study. [dataset]

There are no explicit IP restrictions or fees associated with the use of the data mentioned in the documentation. The dataset is intended for academic and research purposes, and its use is conditioned upon proper citation to acknowledge the contributions of the original researchers. This approach facilitates the ethical and responsible use of the data within the academic community. If there were any third-party restrictions, these would typically be detailed in the license or terms of use associated with the dataset, none of which are specified in the provided documents.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
The documentation for the 2021 Canadian Election Study does not explicitly state any export controls or regulatory restrictions applied to the dataset or to individual instances. The data collected through this survey typically adheres to local laws and regulations concerning data privacy, research ethics, and data protection, as governed by the institution hosting the research and the jurisdictions in which the data is collected and used.

The lack of mention of specific regulatory restrictions or export controls suggests that the primary considerations for using the dataset revolve around ethical research practices, participant consent, and privacy protections, which are standard for academic research involving human subjects.

For more specific details regarding any potential regulatory restrictions or to confirm the absence of such, direct communication with the research team or the ethics board that reviewed the study would be necessary. They would be able to provide detailed guidance on any restrictions or compliance requirements that might not be explicitly documented in the public release of the dataset.
7. *Any other comments?*
 NA
# Maintenance

1. *Who will be supporting/hosting/maintaining the dataset?*
The entity supporting, hosting, and maintaining the 2021 Canadian Election Study dataset is typically the academic or research institution affiliated with the principal investigators and research team responsible for the study. This institution serves as the custodian of the dataset, ensuring its accessibility, integrity, and long-term preservation for academic and research use.

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
Contact information for the owner, curator, or manager of the 2021 Canadian Election Study dataset is typically provided through the dataset documentation or associated publications. In academic research, the principal investigators or project leads are usually the primary points of contact for inquiries related to the dataset.

Based on the information provided in the documentation, you can contact the principal investigators of the study for further assistance or inquiries regarding the dataset. Here are the contact details for the principal investigators:

1. **Dr. Laura Stephenson**
   - Department of Political Science, University of Western Ontario
   - Email: laura.stephenson@uwo.ca

2. **Dr. Allison Harell**
   - Department of Political Science, Université de Québec à Montréal

3. **Dr. Daniel Rubenson**
   - Department of Politics and Public Administration, Ryerson University

4. **Dr. Peter John Loewen**
   - Munk School of Global Affairs, University of Toronto

You can reach out to them via email with any questions or inquiries you may have regarding the dataset, its usage, availability, or any other related matters. They should be able to provide further guidance or direct you to the appropriate resources for assistance.

3. *Is there an erratum? If so, please provide a link or other access point.*
There is no specific mention of an erratum related to the 2021 Canadian Election Study dataset in the provided documentation. An erratum typically refers to a correction or update issued after the initial publication of a dataset or associated documentation to rectify errors or provide additional information.

If you suspect that there may be errors or updates related to the dataset, it is advisable to review any accompanying documentation, such as codebooks or data release notes, for any relevant announcements or corrections. Additionally, contacting the principal investigators or project leads of the study directly can provide clarification or updates on any issues related to the dataset. They would be able to inform you of any errata or corrections that have been issued for the dataset and provide guidance on how to access them.

4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*

The provided documentation does not specify whether updates will be made to the 2021 Canadian Election Study dataset. However, it is common practice in academic research to periodically update datasets to correct errors, add new instances, or improve data quality based on feedback or new research findings.

If updates are planned for the dataset, the frequency, process, and communication methods for these updates would typically be determined by the dataset's custodians or the research team responsible for its maintenance. Here are some general considerations:

1. **Frequency**: Updates may occur on an as-needed basis or periodically, depending on the nature and extent of changes required. For example, updates might be released annually, after each election cycle, or in response to identified errors or improvements.

2. **Responsibility**: The responsibility for updating the dataset lies with the custodians or managers of the dataset, typically the principal investigators or the institution hosting the research.

3. **Communication**: Updates to the dataset can be communicated to dataset consumers through various channels, such as email notifications, announcements on the dataset's website or repository, mailing lists, or social media platforms. Academic repositories like GitHub or institutional data repositories may also provide versioning and change logs to track updates and revisions.

5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
The documentation for the 2021 Canadian Election Study dataset does not explicitly mention any limits on the retention of data associated with the instances. However, in academic research involving human subjects, data retention practices typically adhere to ethical guidelines and data protection regulations to ensure the privacy and confidentiality of participants.

Common practices for data retention in academic research include:

1. **Informed Consent**: Participants are typically informed about how their data will be used and retained during the consent process. If specific limits on data retention are in place, participants would be informed accordingly.

2. **Data Protection Regulations**: Data retention practices may be guided by local data protection regulations, which often specify retention periods or conditions for data storage and deletion.

3. **Ethical Oversight**: Academic research studies, especially those involving human subjects, are often subject to ethical review by institutional review boards (IRBs) or ethics committees. These bodies may provide guidance or set requirements for data retention and deletion.

4. **Research Protocols**: The research team may establish protocols for data management, including data retention and deletion procedures, to ensure compliance with ethical standards and regulatory requirements.

6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
The documentation does not specify whether older versions of the 2021 Canadian Election Study dataset will continue to be supported, hosted, and maintained. However, in academic research, it is common for datasets to be preserved and maintained for long-term access, especially if they are considered valuable for ongoing research or historical reference.

Here are possible scenarios for how older versions of the dataset might be handled:

1. **Continued Hosting and Maintenance**: Older versions of the dataset may continue to be hosted and maintained alongside newer versions, ensuring ongoing access to historical data. This allows researchers to access and compare data from different time periods for longitudinal studies or trend analysis.

2. **Archiving**: If older versions of the dataset are no longer actively supported or maintained, they may be archived in repositories or data archives to ensure long-term preservation. Archived versions would remain accessible for reference purposes but may not receive updates or technical support.

3. **Communication of Obsolescence**: If older versions of the dataset are no longer supported or maintained, this information would typically be communicated to dataset consumers through announcements on the dataset's website, repository, or other communication channels. Consumers may be advised to migrate to newer versions of the dataset or alternative data sources for updated information.

7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
The documentation does not explicitly mention a mechanism for others to extend, augment, build on, or contribute to the 2021 Canadian Election Study dataset. However, academic research datasets are often considered valuable resources for further analysis and research, and contributions from other researchers may be welcomed under certain conditions.

Here are potential considerations regarding contributions to the dataset:

1. **Mechanism for Contributions**: If contributions to the dataset are welcomed, researchers may be invited to submit their additions or modifications through a designated process, such as contacting the dataset's custodians or submitting proposed changes through a repository's contribution mechanism.

2. **Validation/Verification**: Contributions to the dataset may undergo validation and verification processes to ensure data quality, consistency, and adherence to ethical standards. This could involve peer review by experts in the field or validation against existing data sources.

3. **Communication/Distribution of Contributions**: If contributions are accepted and validated, they may be communicated to dataset consumers through updates to the dataset documentation, release notes, or versioning information. Contributions may be distributed alongside the original dataset, either as part of updated versions or as supplementary datasets.

4. **Process for Reviewing Contributions**: A structured process may be established for reviewing and approving contributions to the dataset. This process could involve criteria for assessing the relevance, accuracy, and ethical compliance of proposed contributions.

8. *Any other comments?*
   NA

\newpage

# References

### 2024-04-19 paper/Data sheet.qmd
Add files via upload

@@
 number-sections: true
-bibliography: references.bib
+bibliography: reference.bib
 link-citations: true
 ---
+The questions of the data sheet is from @gebru2021datasheets
 
-# Motivation
+##  Motivation
 
